### 2021-09-13 note-temp/elegantnote-cn-code.tex
Update

%!TEX program = xelatex
%\documentclass[cn,hazy,blue,14pt,screen]{elegantnote}

\documentclass[cn,normal,11pt,blue]{elegantnote}
\usepackage{epsfig,amssymb,amsmath,version}
\usepackage{amssymb,version,graphicx,fancybox,mathrsfs,multirow}
%\usepackage[notcite,notref]{showkeys}
\usepackage{fontspec}
\usepackage{diagbox}
\usetikzlibrary{arrows,shapes}

\usepackage{tocloft}
\renewcommand{\cfttoctitlefont}{\hfill \bfseries \LARGE}
\renewcommand{\contentsname}{\centerline{\color{ecolor}目~~录}}
\renewcommand{\cftaftertoctitle}{\hfill}
\setlength{\cftbeforetoctitleskip}{10ex}
\setlength{\cftaftertoctitleskip}{5ex}
\renewcommand{\cftsecdotsep}{\cftdotsep}  % 设置Section引导点
\renewcommand{\cftbeforesecskip}{3ex}
\renewcommand{\cftbeforesubsecskip}{1ex}
% \renewcommand{\cftsecfont}{\songti}   % 设置Section字体

%%%%%%%%%%%%%%%%%%%%%%%%% Code Style %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Matlab highlight color settings
%\definecolor{mBasic}{RGB}{248,248,242}       % default
\definecolor{mKeyword}{RGB}{0,0,255}          % bule
\definecolor{mString}{RGB}{160,32,240}        % purple
\definecolor{mComment}{RGB}{34,139,34}        % green
\definecolor{mBackground}{RGB}{245,245,245}   % lightgrey
\definecolor{mNumber}{RGB}{128,128,128}       % gray

\lstset{language=matlab,               % choose the language of the code
  xleftmargin=20pt,
  xrightmargin=20pt,
  frame=tlbr,framesep=6pt,framerule=0.5pt, % sets the frame style
  %frame=shadowbox,rulesepcolor=\color{red!20!green!20!blue!20},
  basicstyle=\footnotesize\ttfamily,
  keywordstyle={\color{mKeyword}},     % sets color for keywords
  stringstyle={\color{mString}},       % sets color for strings
  commentstyle={\color{mComment}},     % sets color for comments
  backgroundcolor=\color{gray!5},      %\color{pBackground}, % choose the background color
  rulecolor=\color{gray!50},
  %title=\lstname,                      % \lstname show the filename of files
  keywords={break,case,catch,classdef,continue,else,elseif,end,for,
  function,global,if,otherwise,parfor,persistent,return,spmd,switch,try,while},
  showspaces=false,                    % show spaces adding particular underscores
  showstringspaces=false,              % underline spaces within strings
  showtabs=false,                      % show tabs within strings adding particular underscores
  tabsize=4,                           % sets default tabsize to 2 spaces
  captionpos=t,                        % sets the caption-position to bottom
  breaklines=true,                     % sets automatic line breaking
}

%\lstinputpath{./M-files/}
\newcommand*\lstinputpath[1]{\lstset{inputpath=#1}}
\lstinputpath{{./M-files/}}

% Using: \lstinputlisting{Euler1.m}

\lstset{basicstyle=\footnotesize\fontspec{Consolas}}
%\lstset{basicstyle=\footnotesize\fontspec{Courier New}}

%\renewcommand{\lstlistingname}{\texttt{Listing}}%
%
%\newcommand{\mylisting}[2][]{%
%    \lstinputlisting[style=MyStyle,caption=\texttt{\detokenize{#2}},#1]{#2}%
%}

%\usepackage[numbered,autolinebreaks,useliterate]{mcode} % framed,
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{ElegantNote：一个优美的 \LaTeX{} 笔记模板}

\author{邓东升}
\institute{Elegant\LaTeX{} Program}

\version{2.30}
\date{\zhtoday}

\usepackage{array}

\begin{document}
\maketitle

\pagenumbering{Roman} % 页码为大写罗马数字

%\input{Cover.tex}
%\clearpage

% ----- generate a empty page -----
%\newpage\null\thispagestyle{empty}\newpage \addtocounter{page}{-1}
%\addtocounter{page}{-1}

\vskip -2em
\tableofcontents
\clearpage
\setlist[itemize]{label=$\circ$}

\pagenumbering{arabic}  % 页码为阿拉伯数字

\section{ElegantNote 使用说明}

新版 ElegantNote 是基于标准的 \LaTeX{} 文类 article 重新设计的，格式更加简化的笔记模板！本模板支持两种编译方式，\hologo{pdfLaTeX} 和 \hologo{XeLaTeX}，英文模式下请使用 \hologo{pdfLaTeX} 进行编译，中文模式下推荐使用 \hologo{XeLaTeX}。

新模板有下面几个特性：

\begin{itemize}
  \item 纸张模式：护眼模式（geye）和朦胧模式（hazy）；
  \item 适配不同设备，包括 Pad（默认），Screen（幻灯片），Kindle，PC（双页），通用（A4 纸张）；
  \item 5 套颜色主题，分别是：\textcolor{eblue}{blue}（默认）、\textcolor{egreen}{green}、\textcolor{ecyan}{cyan}、 \textcolor{sakura}{sakura} 和 \textcolor{black}{black}；
  \item 语言支持：中文（默认），英文；
  \item 支持 \hologo{pdfLaTeX} 和 \hologo{XeLaTeX} 编译；
  \item 更加美观的图表标题格式，列表环境，数学字体等；
  \item 全局字体大小支持：8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, 和 20pt；
  \item 支持 \lstinline{newtx} 以及 \lstinline{mtpro2} 数学字体设置；
  \item 中文字体支持方正字体或者自定义字体；
  \item 英文模式通过 \lstinline{bibstyle} 选项（默认为 \lstinline{apalike}）支持参考文献格式修改；
  \item 支持参考格式显示格式修改 \lstinline{cite} 可选为 \lstinline{authoryear}、\lstinline{numbers} （默认）和 \lstinline{super}。
\end{itemize}

本次更新：修复 \TeX{} Live 2020 更新之后因 \lstinline{gbt7714} 宏包更新用法导致模板出错的问题。

\subsection{模板模式}

本模板增加了模式选项，分别有护眼模式（\lstinline{mode=geye}）和朦胧模式（\lstinline{mode=hazy}）。其中护眼模式设置纸张底色为绿豆沙颜色，而朦胧模式为淡蓝色，开启的方法如下：
\begin{lstlisting}[frame=none]
  \documentclass[geye]{elegantnote} % or
  \documentclass[mode=geye]{elegantnote}
  \documentclass[hazy]{elegantnote} % or
  \documentclass[mode=hazy]{elegantnote}
\end{lstlisting}

\begin{remark}
  如果你想为自己的文档添加底色，可以在导言区添加下面设置：
  \begin{lstlisting}
    \definecolor{geyecolor}{RGB}{199,237,204}
    \pagecolor{geyecolor}
  \end{lstlisting}
\end{remark}

\subsection{设备选择}

为了让笔记方便在不同设备上阅读，免去切边，缩放等操作，本模板适配不同的设备，分别为 Pad（默认），Kindle，PC，A4。

\textcolor{red}{\kaishu 新增}：为了方便展示笔记，2.20 版本新增了 \lstinline{device=screen} 设备选项，大小为 MS Powerpoint 的纸张大小，比例为 4:3（2019/12/06）。

不同屏幕的选择为
\begin{lstlisting}[frame=none]
  \documentclass[device=pad]{elegantnote}    % ipad screen size
  \documentclass[device=kindle]{elegantnote} % kindle screen size
  \documentclass[device=pc]{elegantnote}     % double pages for pc
  \documentclass[device=normal]{elegantnote} % a4 normal page
  \documentclass[device=screen]{elegantnote} % 4:3 PPT size
\end{lstlisting}
\begin{note}
也可以采取直接赋值的方法选择屏幕，比如：
\end{note}
\begin{lstlisting}[frame=none]
  \documentclass[pad]{elegantnote}
  \documentclass[kindle]{elegantnote}
  \documentclass[pc]{elegantnote}
  \documentclass[normal]{elegantnote}
  \documentclass[screen]{elegantnote}
\end{lstlisting}

\begin{note}
  如果想要正常的 A4 大小的 PDF，需要选择 \lstinline{device=normal}。
\end{note}

\subsection{数学字体选项}

本模板定义了一个数学字体选项（\lstinline{math}），可选项有三个：
\begin{enumerate}
  \item \lstinline{math=cm}（默认），使用 \LaTeX{} 默认数学字体（推荐，无需声明）；
  \item \lstinline{math=newtx}，使用 \lstinline{newtxmath} 设置数学字体（潜在问题比较多）。
  \item \lstinline{math=mtpro2}，使用 \lstinline{mtpro2} 宏包设置数学字体，要求用户已经成功安装此宏包。
\end{enumerate}

\subsection{中文字体选项}
模板提供中文字体选项 \lstinline{chinesefont}，可选项有
\begin{enumerate}
\item \lstinline{ctexfont}：默认选项，使用 \lstinline{ctex} 宏包根据系统自行选择字体，可能存在字体缺失的问题，更多内容参考 \lstinline{ctex} 宏包\href{https://ctan.org/pkg/ctex}{官方文档}\footnote{可以使用命令提示符，输入 \lstinline{texdoc ctex} 调出本地 \lstinline{ctex} 宏包文档}。
\item \lstinline{founder}：方正字体选项，调用 \lstinline{ctex} 宏包并且使用 \lstinline{fontset=none} 选项，然后设置字体为方正四款免费字体，方正字体下载注意事项见后文。
\item \lstinline{nofont}：调用 \lstinline{ctex} 宏包并且使用 \lstinline{fontset=none} 选项，不设定中文字体，用户可以自行设置中文字体，具体见后文。
\end{enumerate}

\noindent \textbf{注意：} 使用 \lstinline{founder} 选项或者 \lstinline{nofont} 时，必须使用 \hologo{XeLaTeX} 进行编译。

\subsubsection{方正字体选项}
由于使用 \lstinline{ctex} 宏包默认调用系统已有的字体，部分系统字体缺失严重，因此，用户希望能够使用其它字体，我们推荐使用方正字体。方正的{\songti 方正书宋}、{\heiti 方正黑体}、{\kaishu 方正楷体}、{\fangsong 方正仿宋}四款字体均可免费试用，且可用于商业用途。用户可以自行从\href{http://www.foundertype.com/}{方正字体官网}下载此四款字体，在下载的时候请\textbf{务必}注意选择 GBK 字符集，也可以使用 \href{https://www.latexstudio.net/}{\LaTeX{} 工作室}提供的\href{https://pan.baidu.com/s/1BgbQM7LoinY7m8yeP25Y7Q}{方正字体，提取码为：njy9} 进行安装。安装时，{\kaishu Win 10 用户请右键选择为全部用户安装，否则会找不到字体。}

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\textwidth]{founder.png}
\end{figure}

\subsubsection{其他中文字体}
如果你想完全自定义字体\footnote{这里仍然以方正字体为例。}，你可以选择 \lstinline{chinesefont=nofont}，然后在导言区设置
\begin{lstlisting}
\setCJKmainfont[BoldFont={FZHei-B01},ItalicFont={FZKai-Z03}]{FZShuSong-Z01}
\setCJKsansfont[BoldFont={FZHei-B01},ItalicFont={FZHei-B01}]{FZHei-B01}
\setCJKmonofont[BoldFont={FZHei-B01},ItalicFont={FZHei-B01}]{FZFangSong-Z02}
\setCJKfamilyfont{zhsong}{FZShuSong-Z01}
\setCJKfamilyfont{zhhei}{FZHei-B01}
\setCJKfamilyfont{zhkai}{FZKai-Z03}
\setCJKfamilyfont{zhfs}{FZFangSong-Z02}
\newcommand*{\songti}{\CJKfamily{zhsong}}
\newcommand*{\heiti}{\CJKfamily{zhhei}}
\newcommand*{\kaishu}{\CJKfamily{zhkai}}
\newcommand*{\fangsong}{\CJKfamily{zhfs}}
\end{lstlisting}

\subsection[颜色主题]{颜色主题\footnote{测试章节脚注。}}

本模板内置 5 套颜色主题，分别是 \textcolor{eblue}{blue}（默认），\textcolor{egreen}{green}， \textcolor{ecyan}{cyan}， \textcolor{sakura}{sakura} 和 \textcolor{black}{black}。如果不需要颜色，可以选择黑色（black）主题。颜色主题的设置方法：
\begin{lstlisting}[frame=none]
  \documentclass[green]{elegantnote}
  \documentclass[color=green]{elegantnote}
  ...
  \documentclass[black]{elegantnote}
  \documentclass[color=black]{elegantnote}
\end{lstlisting}

\subsection{语言模式}

本模板内含两套语言环境，改变语言环境会改变图表标题的引导词（图，表），文章结构词（比如目录，参考文献等），以及定理环境中的引导词（比如定理，引理等）。不同语言模式的启用如下：
\begin{lstlisting}[frame=none]
  \documentclass[cn]{elegantnote}
  \documentclass[lang=cn]{elegantnote}
  \documentclass[en]{elegantnote}
  \documentclass[lang=en]{elegantnote}
\end{lstlisting}

\begin{note}
只有中文模式才可输入中文，如果需要在英文模式下输入中文，可以自行添加 \lstinline{ctex} 宏包\footnote{需要使用 \lstinline{scheme=plain} 选项才不会把标题改为中文。}或者使用 \lstinline{xeCJK} 宏包设置字体。另外如果在笔记中使用了抄录环境（\lstinline{lstlisting}），并且里面有中文字符，请务必使用 \hologo{XeLaTeX} 编译。
\end{note}

\subsection{定理类环境}

此模板采用了 \lstinline{amsthm} 中的定理样式，使用了 4 类定理样式，所包含的环境分别为
\begin{itemize}
  \item \textbf{定理类}：theorem，lemma，proposition，corollary；
  \item \textbf{定义类}：definition，conjecture，example；
  \item \textbf{备注类}：remark，note，case；
  \item \textbf{证明类}：proof。
\end{itemize}

\begin{remark}
在选用 \lstinline{lang=cn} 时，定理类环境的引导词全部会改为中文。
\end{remark}

\section{写作示例}

我们将通过三个步骤定义可测函数的积分。首先定义非负简单函数的积分。以下设 $E$ 是 $\mathcal{R}^n$ 中的可测集。

\begin{definition}[可积性]
设 $ f(x)=\sum\limits_{i=1}^{k} a_i \chi_{A_i}(x)$ 是 $E$ 上的非负简单函数，其中 $\{A_1,A_2,\ldots$, $A_k\}$ 是 $E$ 上的一个可测分割，$a_1,a_2,\ldots,a_k$ 是非负实数。定义 $f$ 在 $E$ 上的积分为 1. 3
\begin{equation}
   \label{inter}
   \int_{E} f dx = \sum_{i=1}^k a_i m(A_i).
\end{equation}
一般情况下 $0 \leq \int_{E} f dx \leq \infty$。若 $\int_{E} f dx < \infty$，则称 $f$ 在 $E$ 上可积。
\end{definition}

一个自然的问题是，Lebesgue 积分与我们所熟悉的 Riemann 积分有什么联系和区别？之后我们将详细讨论 Riemann 积分与 Lebesgue 积分的关系。这里只看一个简单的例子。设 $D(x)$ 是区间 $[0,1]$ 上的 Dirichlet 函数。即 $D(x)=\chi_{Q_0}(x)$，其中 $Q_0$ 表示 $[0,1]$ 中的有理数的全体。根据非负简单函数积分的定义，$D(x)$ 在 $[0,1]$ 上的 Lebesgue 积分为
\begin{equation}\label{inter2}
  \int_0^1 D(x)dx = \int_0^1 \chi_{Q_0} (x) dx = m(Q_0) = 0
\end{equation}
即 $D(x)$ 在 $[0,1]$ 上是 Lebesgue 可积的并且积分值为零。但 $D(x)$ 在 $[0,1]$ 上不是 Riemann 可积的。

\begin{table}[htbp]
  \centering
  \small
  \caption{燃油效率与汽车价格}
    \begin{tabular}{lcc}
    \toprule
                  &       (1)         &        (2)      \\
    \midrule
    燃油效率      &   -238.90***      &      -49.51     \\
                  &    (53.08)        &      (86.16)    \\
    汽车重量      &                   &        1.75***  \\
                  &                   &       (0.641)   \\
    常数项        &  11253.00***      &    1946.00      \\
                  &  (1171.00)        &   (3597.00)     \\
    观测数        &     74            &      74         \\
    $R^2$         &      0.220        &       0.293     \\
    \bottomrule
    \end{tabular}%
  \label{tab:reg}%
\end{table}%

\begin{theorem}[Fubini 定理]\label{thm:fubi}
若 $f(x,y)$ 是 $\mathcal{R}^p\times\mathcal{R}^q$ 上的非负可测函数，则对几乎处处的 $x\in \mathcal{R}^p$，$f(x,y)$ 作为 $y$ 的函数是 $\mathcal{R}^q$ 上的非负可测函数，$g(x)=\int_{\mathcal{R}^q}f(x,y) dy$ 是 $\mathcal{R}^p$ 上的非负可测函数。并且
\begin{equation}\label{eq:461}
  \int_{\mathcal{R}^p\times\mathcal{R}^q} f(x,y) dxdy=\int_{\mathcal{R}^p}\left(\int_{\mathcal{R}^q}f(x,y)dy\right)dx.
\end{equation}
\end{theorem}

\begin{proof}
Let $z$ be some element of $xH \cap yH$.  Then $z = xa$ for some $a \in H$, and $z = yb$ for some $b \in H$. If $h$ is any element of $H$ then $ah \in H$ and $a^{-1}h \in H$, since $H$ is a subgroup of $G$. But $zh = x(ah)$ and $xh = z(a^{-1}h)$ for all $h \in H$. Therefore $zH \subset xH$ and $xH \subset zH$, and thus $xH = zH$.  Similarly $yH = zH$, and thus $xH = yH$, as required.
\end{proof}

回归分析（regression analysis) 是确定两种或两种以上变量间相互依赖的定量关系的一种统计分析方法。根据定理~\ref{thm:fubi}，其运用十分广泛，回归分析按照涉及的变量的多少，分为一元回归和多元回归分析；按照因变量的多少，可分为简单回归分析和多重回归分析；按照自变量和因变量之间的关系类型，可分为线性回归分析和非线性回归分析。

\section{协作人员招募}

招募 Elegant\LaTeX{} 的协作人员，没有工资。工作内容：翻译 Elegant\LaTeX{} 系列模板相关的文稿（中翻英），维护模板的 wiki（主要涉及 Markdown），如果有公众号文稿写作经历的话，也可以帮忙写微信稿。本公告长期有效。

目前 ElegantLaTeX 共有 4 名协作人员，分别是
\begin{itemize}
  \item 官方文档翻译: \href{https://github.com/peggy2006xzyz}{YPY};
  \item GitHub 维基维护: \href{https://github.com/izinngo}{Ingo Zinngo}、\href{https://github.com/xiaohao890809}{追寻原风景};
  \item QQ 群管理员: \href{https://github.com/sikouhjw}{Sikouhjw}.
\end{itemize}

在此感谢他们无私的奉献！

\section{致谢}

截止到 2020 年 04 月 12 日，ElegantNote 2.30 版本发布，ElegantNote 模板在 GitHub 上的收藏数（star）达到了 263。在此特别感谢 China\TeX{} 以及 \href{http://www.latexstudio.net/}{\LaTeX{} 工作室}对于本系列模板的大力宣传与推广。如果你喜欢我们的模板，你可以在 GitHub 上收藏（Star）我们的模板。

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{star.png}
  \caption{一键三连求赞}
\end{figure}

\section{MATLAB代码}

\begin{lstlisting}
% Euler1.m
% Euler method for the ODE model
% u'(t)=t^2+t-u, t \in [0,1]
% Initial condition : u(0)=0 ;
% Exact solution : u(t)=-exp(-t)+t^2-t+1.
clear all
h=0.1;
x=0:h:1;                       % function interval
n=length(x)-1;
u(1)=0;                        % initial value
fun=@(t,u) t.^2+t-u;           % RHS
for i=1:n
    u(i+1)=u(i)+h.*fun(x(i),u(i));
end
ue=-exp(-x)+x.^2-x+1;          % exact solution
plot(x,ue,'b-',x,u,'r+','LineWidth',1.5)
xlabel('x','fontsize', 16), ylabel('y','fontsize',16,'Rotation',0)
legend('Exact ','Numerical','location','North')
title('Euler Method','fontsize',14)
set(gca,'fontsize',14)
\end{lstlisting}

\section{捐赠}

如果您非常喜爱我们的模板，你还可以选择捐赠以表达您对我们模板和我的支持！

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.4\textwidth]{donate.jpg}
\end{figure}

\textbf{赞赏费用的使用解释权归 Elegant\LaTeX{} 所有，并且不接受监督，请自愿理性打赏}。10 元以上的赞赏，我们将列入捐赠榜，并且发放捐赠纪念证（全部），谢谢各位金主！

\begin{table}[htbp]
  \scriptsize
  \centering
  \caption{Elegant\LaTeX{} 系列模板捐赠榜}
    \begin{tabular}{*{8}{>{\scriptsize}c}}
    \toprule
    \textbf{捐赠者} & \textbf{金额} & \textbf{时间} & \textbf{渠道} & \textbf{捐赠者} & \textbf{金额} & \textbf{时间} & \textbf{渠道} \\
    \midrule
    Lerh  & 10 RMB & 2019/05/15 & 微信    & 越过地平线 & 10 RMB & 2019/05/15 & 微信 \\
    银桑    & 20 RMB & 2019/05/27 & 微信    & *空    & 10 RMB & 2019/05/30 & 微信 \\
    latexstudio.net & 666 RMB & 2019/06/05 & 支付宝   & A*n   & 40 RMB & 2019/06/15 & 微信 \\
    * 夏   & 22 RMB & 2019/06/15 & 微信    & * 倩   & 21 RMB  & 2019/06/15 & 微信 \\
    Cassis & 11 RMB & 2019/06/30 & 微信    & *君    & 10 RMB & 2019/07/23 & 微信 \\
    P*u   & 50 RMB & 2019/07/30 & 微信    & *萌    & 19 RMB & 2019/08/28 & 微信 \\
    曲豆豆   & 10 RMB & 2019/08/28 & 微信    & 李博    & 100 RMB & 2019/10/06 & 微信 \\
    Njustsll & 10 RMB & 2019/10/11 & 微信    & 刘志阔   & 99.99 RMB & 2019/10/15 & 支付宝 \\
    * 韬   & 16 RMB & 2019/10/17 & 微信    & 赤霓    & 12 RMB & 2019/10/17 & 支付宝 \\
    追寻原风景 & 10 RMB & 2019/10/28 & 微信    & 郭德良   & 88 RMB & 2019/11/03 & 微信 \\
    自强不息  & 20 RMB & 2019/11/04 & 支付宝   & 读书之虫  & 20 RMB & 2019/11/18 & 微信 \\
    *等    & 10 RMB & 2019/11/18 & 微信    & *哲    & 20 RMB & 2019/11/18 & 微信 \\
    佚名    & 10 RMB & 2019/11/24 & 微信    & Jiye Qian & 66 RMB & 2019/12/04 & 微信 \\
    * 阳   & 20 RMB & 2019/12/05 & 微信    & Catcher & 11 RMB & 2019/12/08 & 支付宝 \\
    希尔波特门徒 & 10 RMB & 2019/12/09 & 支付宝   & * 伟   & 10 RMB & 2019/12/09 & 微信 \\
    Simon & 20 RMB & 2019/12/11 & 支付宝   & 流殇丶浅忆 & 66.60 RMB & 2019/12/18 & 支付宝 \\
    羽     & 10 RMB & 2019/12/20 & 支付宝   & * 琛   & 15 RMB & 2019/12/20 & 微信 \\
    随风    & 20 RMB & 2019/12/27 & 支付宝   & Ws    & 23.30 RMB & 2019/12/28 & 微信 \\
    初八    & 100 RMB  & 2020/01/02 & 支付宝   & p*e   & 20 RMB & 2020/01/03 & 微信 \\
    Shunmx & 100 RMB & 2020/01/03 & 微信    & hj    & 10 RMB & 2020/01/03 & 微信 \\
    F*5   & 10 RMB & 2020/01/03 & 微信    & S*m   & 20.20 RMB & 2020/01/03 & 微信 \\
    二代青雉  & 13 RMB & 2020/01/14 & 支付宝   & *?    & 66 RMB & 2020/01/15 & 微信 \\
    Mr. Xiong & 20 RMB & 2020/01/17 & 微信    & *博    & 15 RMB & 2020/01/18 & 微信 \\
    * 者  & 10 RMB & 2020/02/02 & 微信    & Jackie  &  88.80 RMB  &  2020/02/09 & 微信 \\
    Henry\_Sun、 & 50 RMB & 2020/02/14 & 支付宝 & * 桥  & 50 RMB & 2020/02/21 & 微信 \\
    昀琏 & 10 RMB & 2020/03/02 & 支付宝 & S*y  &  10 RMB  &  2020/03/15 & 微信 \\
    * 哥  & 66.66 RMB & 2020/03/17 & 微信    &   K*e & 30 RMB & 2020/03/30 & 微信\\
    * 阳  &  20 RMB  &  2020/04/02 & 微信 & 士*n  & 30 RMB & 2020/04/11 & 微信 \\
    \bottomrule
    \end{tabular}%
  \label{tab:donation}%
\end{table}%

\section{常见问题 FAQ}

\begin{enumerate}[label=\arabic*).]
  \item \textit{如何删除版本信息？}\\
    导言区不写 \lstinline|\version{x.xx}| 即可。
  \item \textit{如何删除日期？}\\
    与版本 \lstinline{\version} 不同的是，导言区不写或注释 \lstinline{\date} 的话，仍然会打印出当日日期，原因是 \lstinline{\date} 有默认参数。如果不需要日期的话，日期可以留空即可，也即 \lstinline|\date{}|。
  \item \textit{如何获得中文日期？}\\
    为了获得中文日期，必须在中文模式下，使用 \lstinline|\date{\zhdate{2019/12/09}}|，如果需要当天的汉化日期，可以使用 \lstinline|\date{\zhtoday}|，这两个命令都来源于 \href{https://ctan.org/pkg/zhnumber}{\lstinline{zhnumber}} 宏包。
  \item \textit{如何添加多个作者？}\\
    在 \lstinline{\author} 里面使用 \lstinline{\and}，作者单位可以用 \lstinline{\\} 换行。
    \begin{lstlisting}
      \author{author 1\\ org. 1 \and author 2 \\ org. 2 }
    \end{lstlisting}
\end{enumerate}

\end{document}

### 2021-09-13 note-temp/elegantnote-cn.tex
Update

--- 2021-09-13 note-temp/elegantnote-cn-code.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%% Code Style %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Matlab highlight color settings
-%\definecolor{mBasic}{RGB}{248,248,242}       % default
-\definecolor{mKeyword}{RGB}{0,0,255}          % bule
-\definecolor{mString}{RGB}{160,32,240}        % purple
-\definecolor{mComment}{RGB}{34,139,34}        % green
-\definecolor{mBackground}{RGB}{245,245,245}   % lightgrey
-\definecolor{mNumber}{RGB}{128,128,128}       % gray
-
-\lstset{language=matlab,               % choose the language of the code
-  xleftmargin=20pt,
-  xrightmargin=20pt,
-  frame=tlbr,framesep=6pt,framerule=0.5pt, % sets the frame style
-  %frame=shadowbox,rulesepcolor=\color{red!20!green!20!blue!20},
-  basicstyle=\footnotesize\ttfamily,
-  keywordstyle={\color{mKeyword}},     % sets color for keywords
-  stringstyle={\color{mString}},       % sets color for strings
-  commentstyle={\color{mComment}},     % sets color for comments
-  backgroundcolor=\color{gray!5},      %\color{pBackground}, % choose the background color
-  rulecolor=\color{gray!50},
-  %title=\lstname,                      % \lstname show the filename of files
-  keywords={break,case,catch,classdef,continue,else,elseif,end,for,
-  function,global,if,otherwise,parfor,persistent,return,spmd,switch,try,while},
-  showspaces=false,                    % show spaces adding particular underscores
-  showstringspaces=false,              % underline spaces within strings
-  showtabs=false,                      % show tabs within strings adding particular underscores
-  tabsize=4,                           % sets default tabsize to 2 spaces
-  captionpos=t,                        % sets the caption-position to bottom
-  breaklines=true,                     % sets automatic line breaking
-}
-
-%\lstinputpath{./M-files/}
-\newcommand*\lstinputpath[1]{\lstset{inputpath=#1}}
-\lstinputpath{{./M-files/}}
-
-% Using: \lstinputlisting{Euler1.m}
-
-\lstset{basicstyle=\footnotesize\fontspec{Consolas}}
-%\lstset{basicstyle=\footnotesize\fontspec{Courier New}}
-
-%\renewcommand{\lstlistingname}{\texttt{Listing}}%
-%
-%\newcommand{\mylisting}[2][]{%
-%    \lstinputlisting[style=MyStyle,caption=\texttt{\detokenize{#2}},#1]{#2}%
-%}
-
-%\usepackage[numbered,autolinebreaks,useliterate]{mcode} % framed,
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\usepackage{fancyhdr}
+%\fancyhf{}
+%\cfoot{\thepage}
 
@@
 
-\section{MATLAB代码}
-
-\begin{lstlisting}
-% Euler1.m
-% Euler method for the ODE model
-% u'(t)=t^2+t-u, t \in [0,1]
-% Initial condition : u(0)=0 ;
-% Exact solution : u(t)=-exp(-t)+t^2-t+1.
-clear all
-h=0.1;
-x=0:h:1;                       % function interval
-n=length(x)-1;
-u(1)=0;                        % initial value
-fun=@(t,u) t.^2+t-u;           % RHS
-for i=1:n
-    u(i+1)=u(i)+h.*fun(x(i),u(i));
-end
-ue=-exp(-x)+x.^2-x+1;          % exact solution
-plot(x,ue,'b-',x,u,'r+','LineWidth',1.5)
-xlabel('x','fontsize', 16), ylabel('y','fontsize',16,'Rotation',0)
-legend('Exact ','Numerical','location','North')
-title('Euler Method','fontsize',14)
-set(gca,'fontsize',14)
-\end{lstlisting}
-
 \section{捐赠}

### 2021-09-13 note-temp/elegantnote-en.tex
Update

%\documentclass[en,hazy,screen,blue,14pt]{elegantnote}

\documentclass[en,normal,11pt,blue]{elegantnote}
\usepackage{epsfig,amssymb,amsmath,version}
\usepackage{amssymb,version,graphicx,fancybox,mathrsfs,multirow}
%\usepackage[notcite,notref]{showkeys}
\usepackage{diagbox}
\usetikzlibrary{arrows,shapes}

\usepackage{tocloft}
\renewcommand{\cfttoctitlefont}{\hfill \bfseries \LARGE}
\renewcommand{\contentsname}{\centerline{\color{ecolor}Contents}}
\renewcommand{\cftaftertoctitle}{\hfill}
\setlength{\cftbeforetoctitleskip}{10ex}
\setlength{\cftaftertoctitleskip}{5ex}
\renewcommand{\cftsecdotsep}{\cftdotsep} 
\renewcommand{\cftbeforesecskip}{3ex}
\renewcommand{\cftbeforesubsecskip}{1ex}

\title{ElegantNote: An Elegant \LaTeX{} Template for Notes}

\author{Dongsheng Deng}
\institute{Elegant\LaTeX{} Program}

\version{2.30}
\date{\today}

\begin{document}
\maketitle

\pagenumbering{Roman}

%\input{Cover.tex}
%\clearpage

% ----- generate a empty page -----
%\newpage\null\thispagestyle{empty}\newpage \addtocounter{page}{-1}
%\addtocounter{page}{-1}

\vskip -2em
\tableofcontents
\clearpage

\pagenumbering{arabic}  % 页码为阿拉伯数字

\section{ElegantNote Instructions}
\thispagestyle{empty}
The brand new ElegantNote is redesigned on the basis of \LaTeX{} article, a more elegant note template! You can use either \hologo{pdfLaTeX} or \hologo{XeLaTeX} to compile\footnote{The test environment is Win10 + \TeX{} Live 2019.}. It is recommended that \hologo{pdfLaTeX} be used for notes in English while \hologo{XeLaTeX} be used for notes in Chinese.

The new template has the following features:
\begin{itemize}
  \item two modes: good for eye mode (geye) and hazy mode;
  \item different devices: Pad (default), Screen(beamer size), Kindle, PC (double-page) and normal (A4);
  \item 5 color themes: \textcolor{eblue}{blue} (default),  \textcolor{egreen}{green}, \textcolor{ecyan}{cyan}, \textcolor{sakura}{sakura} and \textcolor{black}{black};
  \item languages support: Chinese (default), English;
  \item support \hologo{pdfLaTeX} and \hologo{XeLaTeX};
  \item prettier captions, list environments, and unified fonts;
  \item custmized global font size: 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt and 20pt;
  \item support for math font options for \lstinline{newtx} and \lstinline{mtpro2};
  \item with the option of \lstinline{bibstyle} (default: apalike) for changing style of bibliography;
  \item change the citation style with \lstinline{cite} option: \lstinline{authoryear}, \lstinline{numbers} and \lstinline{super}.
\end{itemize}

This update is to resolve \TeX{} Live 2020 compilation errors caused by \lstinline{gbt7714} compatibility issues.

\subsection{Optional Modes}

This template provides optional modes: good for eye mode (geye) and hazy mode, while the paper color is green for the former and light blue for the latter. you can use the following code to activate the desired mode:
\begin{lstlisting}[frame=none]
  \documentclass[geye]{elegantnote} % or
  \documentclass[mode=geye]{elegantnote}
  \documentclass[hazy]{elegantnote} % or
  \documentclass[mode=hazy]{elegantnote}
\end{lstlisting}

\begin{remark}
  If you are expected to customize background, use:
  \begin{lstlisting}
    \definecolor{geyecolor}{RGB}{199,237,204}
    \pagecolor{geyecolor}
  \end{lstlisting}
\end{remark}

\subsection{Device Options}

To make the notes more comfortable to read, we designed four output options (of different sizes) that correspond to different reading devices: Pad (default), Kindle, PC and A4paper.

\textcolor{red}{New}: For the convenience of notes presentation, version 2.20 offers a new option for device, i.e. \lstinline{device=screen}, which is similar to the size of MS Powerpoint with ratio aspect of 4:3 (2019/12/06).

The options of output for different devices are
\begin{lstlisting}[frame=none]
  \documentclass[device=pad]{elegantnote}    % ipad screen size
  \documentclass[device=kindle]{elegantnote} % kindle screen size
  \documentclass[device=pc]{elegantnote}     % double pages for pc
  \documentclass[device=normal]{elegantnote} % a4 normal page
  \documentclass[device=screen]{elegantnote} % 4:3 PPT size
\end{lstlisting}

\begin{note}
You can also select the device by using a direct assignment method, such as:
\end{note}

\begin{lstlisting}[frame=none]
  \documentclass[pad]{elegantnote}
  \documentclass[kindle]{elegantnote}
  \documentclass[pc]{elegantnote}
  \documentclass[normal]{elegantnote}
  \documentclass[screen]{elegantnote}
\end{lstlisting}

\begin{note}
To get a normal A4paper size PDF, please select \lstinline{device=normal}.
\end{note}

\subsection{Math Fonts}

This template defines a new option (\lstinline{math}), with three options:

\begin{enumerate}
  \item \lstinline{math=cm} (default), use \LaTeX{} default math font (recommended).
  \item \lstinline{math=newtx}, use \lstinline{newtxmath} math font (may bring about bugs).
  \item \lstinline{math=mtpro2}, use \lstinline{mtpro2} package to set math font.
\end{enumerate}

\subsection[Color Themes]{Color Themes\footnote{Test for chapter footnote.}}

This template contains 5 color themes, \textcolor{egreen}{green}, \textcolor{ecyan}{cyan}, \textcolor{eblue}{blue}(default), \textcolor{sakura}{sakura} and \textcolor{black}{black}. If you don't need color, you can choose black theme. The color theme is enabled in the same way as before:
\begin{lstlisting}[frame=none]
  \documentclass[green]{elegantnote}
  \documentclass[color=green]{elegantnote}
  ....
  \documentclass[black]{elegantnote}
  \documentclass[color=black]{elegantnote}
\end{lstlisting}

\subsection{Languages}

This template contains two sets of language environments, changing the language environment will change the title of table/figure (figure, table), article structure words (such as the table of contents, references, etc.), and the environment Introductory words (such as Theorem, Lemma, etc.). The different language modes are enabled as follows:
\begin{lstlisting}[frame=none]
  \documentclass[cn]{elegantnote}
  \documentclass[lang=cn]{elegantnote}
  \documentclass[en]{elegantnote}
  \documentclass[lang=en]{elegantnote}
\end{lstlisting}

\begin{note}
Chinese characters are allowed in Chinese mode only. To type in Chinese characters in English mode, please include \lstinline{ctex}\footnote{Please use \lstinline{scheme=plain} to retain headlines in English.} or \lstinline{xeCJK} package.
\end{note}

\subsection{Theorem Class Environments}

This template used the \lstinline{amsthm} to create theorems, there are 4 types of theorem environments
\begin{itemize}
  \item \textbf{Theorem-Class}: theorem, lemma, proposition, corollary;
  \item \textbf{Definition-Class}: definition, conjecture, example;
  \item \textbf{Remark-Class}: remark, note, case;
  \item \textbf{Proof-Class}: proof.
\end{itemize}

\begin{remark}
With the option \lstinline{lang=cn} , the introductory words of the theorem class environments will be changed to Chinese.
\end{remark}

\section{Writing Sample}

We will define the integral of a measurable function in three steps. First, we define the integral of a nonnegative simple function. Let $E$ be the measurable set in $\mathcal{R}^N$.

% source: https://www.maths.tcd.ie/~dwilkins/LaTeXPrimer/Theorems.html

\begin{definition}[Left Coset]
Let $H$ be a subgroup of a group~$G$.  A \emph{left coset} of $H$ in $G$ is a subset of $G$ that is of the form $xH$, where $x \in G$ and $xH = \{ xh : h \in H \}$. Similarly a \emph{right coset} of $H$ in $G$ is a subset of $G$ that is of the form $Hx$, where $Hx = \{ hx : h \in H \}$
\end{definition}

Note that a subgroup~$H$ of a group $G$ is itself a left coset of $H$ in $G$.

\begin{lemma}[Size Of Left Coset]
Let $H$ be a finite subgroup of a group $G$.  Then each left
coset of $H$ in $G$ has the same number of elements as $H$.
\end{lemma}

\begin{theorem}[Lagrange's Theorem]
Let $G$ be a finite group, and let $H$ be a subgroup
of $G$.  Then the order of $H$ divides the order of $G$.
\end{theorem}

\begin{proof}
Let $z$ be some element of $xH \cap yH$.  Then $z = xa$ for some $a \in H$, and $z = yb$ for some $b \in H$. If $h$ is any element of $H$ then $ah \in H$ and $a^{-1}h \in H$, since $H$ is a subgroup of $G$. But $zh = x(ah)$ and $xh = z(a^{-1}h)$ for all $h \in H$. Therefore $zH \subset xH$ and $xH \subset zH$, and thus $xH = zH$.  Similarly $yH = zH$, and thus $xH = yH$, as required.
\end{proof}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.6\textwidth]{scatter.pdf}
	\caption{Matplotlib: Scatter Plot Example\label{fig:mpg}}
\end{figure}

Regression analysis is a powerful statistical method that allows you to examine the relationship between two or more variables of interest. While there are many types of regression analysis, at their core they all examine the influence of one or more independent variables on a dependent variable. The process of performing a regression allows you to confidently determine which factors matter most, which factors can be ignored, and how these factors influence each other.

Let's continue using our application training example. In this case, we'd want to measure the historical levels of satisfaction with the events from the past three years or so, as well as any information possible in regards to the independent variables.

\begin{table}[htbp]
  \small
  \centering
  \caption{Auto MPG and Price \label{tab:reg}}
    \begin{tabular}{lcc}
    \toprule
                    &       (1)         &        (2)      \\
    \midrule
    mpg             &    -238.90***     &      -49.51     \\
                    &     (53.08)       &      (86.16)    \\
    weight          &                   &      1.75***    \\
                    &                   &      (0.641)    \\
    constant        &     11,253***     &       1,946     \\
                    &     (1,171)       &      (3,597)   \\
    obs             &        74         &         74     \\
    $R^2$           &      0.220        &       0.293    \\
    \bottomrule
    \multicolumn{3}{l}{\scriptsize Standard errors in parentheses} \\
    \multicolumn{3}{l}{\scriptsize *** p<0.01, ** p<0.05, * p<0.1} \\
    \end{tabular}%
\end{table}%

\begin{itemize}[noitemsep]
  \item Routing and resource discovery;
    \begin{itemize}
      \item Language Models
      \item Vector Space Models
    \end{itemize}
  \item Resilient and scalable computer networks;
  \item Distributed storage and search.
\end{itemize}

\section{Recruit Support Members}

Recruit support members for Elegant\LaTeX{} to translate template official guide, maintain wiki entries, update Wechat articles. No deadline for this recruitment.

So far, Elegant\LaTeX{} has four support members:
\begin{itemize}
	\item OG Translator: \href{https://github.com/peggy2006xzyz}{YPY};
	\item Wiki Maintainer: \href{https://github.com/izinngo}{Ingo Zinngo}, \href{https://github.com/xiaohao890809}{Xiaohao890809};
	\item QQ Group Manager: \href{https://github.com/sikouhjw}{Sikouhjw}.
\end{itemize}

Thank them all!!!

\section{Acknowledgement}
The number of stars on GitHub for ElegantPaper reached 176 on April 12, 2020 at the release of ElegantNote v2.20.
Thank China\TeX{} and \href{http://www.latexstudio.net/}{\LaTeX{} studio} for their promotion.

If you like our templates, star on GitHub.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{star.png}
	\caption{Twinkle, Twinkle, Little Star}
\end{figure}

\section{Donation}
To express your love for our templates and/or our developers, please do not hesitate to tip us.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.4\textwidth]{donate.jpg}
\end{figure}

\textbf{The explanation right of the tip usage belongs to Elegant\LaTeX{} with no supervision. Feel free to tip us.} Those who donate more than 10 RMB will be recorded in the donation list and will receive a donation certificate. Thank all the tippers!

\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Donation List}
    \begin{tabular}{cccccccc}
    \toprule
    \textbf{Tipper} & \textbf{Amount} & \textbf{Date} & \textbf{Channel} & \textbf{Tipper} & \textbf{Amount} & \textbf{Date} & \textbf{Channel} \\
    \midrule
    Lerh  & 10 RMB & 2019/05/15 & Wechat    & yueguodipingxian & 10 RMB & 2019/05/15 & Wechat \\
	  yinsang    & 20 RMB & 2019/05/27 & Wechat    & *kong    & 10 RMB & 2019/05/30 & Wechat \\
	  latexstudio.net & 666 RMB & 2019/06/05 & Alipay   & A*n   & 40 RMB & 2019/06/15 & Wechat \\
	  * xia   & 22 RMB & 2019/06/15 & Wechat    & * qian  & 21 RMB  & 2019/06/15 & Wechat \\
	  Cassis & 11 RMB & 2019/06/30 & Wechat    & * jun    & 10 RMB & 2019/07/23 & Wechat \\
	  P*u   & 50 RMB & 2019/07/30 & Wechat    & * meng    & 19 RMB & 2019/08/28 & Wechat \\
	  Qu Doudou   & 10 RMB & 2019/08/28 & Wechat    & Li Bo    & 100 RMB & 2019/10/06 & Wechat \\
	  Njustsll & 10 RMB & 2019/10/11 & Wechat    & Liu Zhikuo   & 99.99 RMB & 2019/10/15 & Alipay \\
	  * tao   & 16 RMB & 2019/10/17 & Wechat    & Chini    & 12 RMB & 2019/10/17 & Alipay \\
	  yuanfengjing & 10 RMB & 2019/10/28 & Wechat    & Guo Deliang   & 88 RMB & 2019/11/03 & Wechat \\
	  ziqiangbuxi  & 20 RMB & 2019/11/04 & Alipay   & dushuzhichong  & 20 RMB & 2019/11/18 & Wechat \\
	  * deng    & 10 RMB & 2019/11/18 & Wechat    & * zhe   & 20 RMB & 2019/11/18 & Wechat \\
	  anonymous    & 10 RMB & 2019/11/24 & Wechat    & Jiye Qian & 66 RMB & 2019/12/04 & Wechat \\
	  * yang   & 20 RMB & 2019/12/05 & Wechat    & Catcher & 11 RMB & 2019/12/08 & Alipay \\
	  xierbotementu & 10 RMB & 2019/12/09 & Alipay   & * wei   & 10 RMB & 2019/12/09 & Wechat \\
	  Simon & 20 RMB & 2019/12/11 & Alipay   & liushangqianyi & 66.60 RMB & 2019/12/18 & Alipay \\
	  yu     & 10 RMB & 2019/12/20 & Alipay   & *chen   & 15 RMB & 2019/12/20 & Wechat \\
	  suifeng   & 20 RMB & 2019/12/27 & Alipay   & Ws    & 23.30 RMB & 2019/12/28 & Wechat \\
	  chuba    & 100 RMB  & 2020/01/02 & Alipay   & p*e   & 20 RMB & 2020/01/03 & Wechat \\
	  Shunmx & 100 RMB & 2020/01/03 & Wechat    & hj    & 10 RMB & 2020/01/03 & Wechat \\
	  F*5   & 10 RMB & 2020/01/03 & Wechat    & S*m   & 20.20 RMB & 2020/01/03 & Wechat \\
	  erdaiqingzhi  & 13 RMB & 2020/01/14 & Alipay   & *?    & 66 RMB & 2020/01/15 & Wechat \\
	  Mr. Xiong & 20 RMB & 2020/01/17 & Wechat    & *bo    & 15 RMB & 2020/01/18 & Wechat \\
	  *Zhe    & 10 RMB & 2020/02/02 & Wechat    &  Jackie &  88.80 RMB  &  2020/02/09 & Wechat \\
	  Henry\_Sun & 50 RMB & 2020/02/14 & Alipay & * Qiao  & 50 RMB & 2020/02/21 & Wechat \\
	  YunLian & 10 RMB & 2020/03/02 & Alipay & S*y  &  10 RMB  &  2020/03/15 & Wechat \\
	  * Ge  & 66.66 RMB & 2020/03/17 & Wechat    &   K*e & 30 RMB & 2020/03/30 & Wechat\\
	  * Yang  &  20 RMB  &  2020/04/02 & Wechat & Shi*n  & 30 RMB & 2020/04/11 & Wechat \\
\bottomrule
\end{tabular}%
  \label{tab:donation}%
\end{table}%

\section{FAQ}

\begin{enumerate}[label=\arabic*).]
	\item \textit{How to remove the information of version?}\\
    Please comment \lstinline|\version{x.xx}|.
	\item \textit{How to remove the information of date?}\\
	  Please type in \lstinline|\date{}|.
	\item \textit{How to add several authors?}\\
	  Use \lstinline{\and} in \lstinline{\author} and use \lstinline{\\} to start a new line.
    \begin{lstlisting}
      \author{author 1\\ org. 1 \and author 2 \\ org. 2 }
    \end{lstlisting}
\end{enumerate}

\end{document}

### 2021-09-13 note-temp/note-cover.tex
Update

% Note Cover

\begin{titlepage}
\begin{tikzpicture}[remember picture, overlay]
\fill[cyan!20](current page.north west) rectangle (current page.south east);
\fill[hong!90](current page.north west) rectangle ([xshift=0.8cm,yshift=-7cm]current page.north west);
\fill[hong!50]([yshift=-7cm]current page.north west) rectangle ([xshift=0.8cm,yshift=-11cm]current page.north west);
\draw[line width=2pt,huang]([yshift=-7cm]current page.north west)--node[above=20pt]{\color{black}\HUGE \newtitle}([yshift=-7cm]current page.north east);
\node[opacity=0.25,rotate=30] at ([xshift=4.8cm,yshift=-3cm]current page.north west){\LARGE $e^{\mathrm{i}\pi}+1=0$};
\node[circle,fill,inner sep=5pt]at([xshift=10.7cm,yshift=-8.1cm]current page.north west)
{};
\node[dart,fill=white,inner sep=2pt]at([xshift=10.7cm,yshift=-8.1cm]current page.north west){};
\node[right] at ([xshift=11.2cm,yshift=-8.1cm]current page.north west){\Large\fangsong 机构名称 \quad 作者 \quad 编写};
\node[opacity=0.45,right] at ([xshift=3.5cm,yshift=-22cm]current page.north west)
{\includegraphics[scale=1.6]{titlefig01.png}};
\node[opacity=0.45,right] at ([xshift=10.5cm,yshift=-13cm]current page.north west)
{\includegraphics[scale=2.4]{titlefig02.png}};
\end{tikzpicture}
\end{titlepage}

### 2021-09-14 note-temp/note-cover.tex
Update

@@
 \begin{titlepage}
+\pdfbookmark[1]{封~面}{cover}
 \begin{tikzpicture}[remember picture, overlay]
@@
 \node[dart,fill=white,inner sep=2pt]at([xshift=10.7cm,yshift=-8.1cm]current page.north west){};
-\node[right] at ([xshift=11.2cm,yshift=-8.1cm]current page.north west){\Large\fangsong 机构名称 \quad 作者 \quad 编写};
+\node[right] at ([xshift=11.2cm,yshift=-8.1cm]current page.north west){\Large\fangsong 组织名称 \quad \newauthor \quad 编写};
+\node[opacity=0.45,right] at ([xshift=10.5cm,yshift=-13cm]current page.north west)
+{\includegraphics[scale=2.4]{titlefig02.png}};
 \node[opacity=0.45,right] at ([xshift=3.5cm,yshift=-22cm]current page.north west)
 {\includegraphics[scale=1.6]{titlefig01.png}};
-\node[opacity=0.45,right] at ([xshift=10.5cm,yshift=-13cm]current page.north west)
-{\includegraphics[scale=2.4]{titlefig02.png}};
+\node[right] at ([xshift=9.1cm,yshift=-27.6cm]current page.north west){\Large \citshape Version 1.00};
 \end{tikzpicture}

### 2021-12-03 book-en/book-cover-en.tex
Update

% !Tex Program = pdflatex

\documentclass[openany,twoside,12pt]{book}
%\documentclass[twoside,12pt]{book}

%----- usepackage for tempalate -----
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{mathrsfs,bm}
%\usepackage[notcite,notref]{showkeys}
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=1.7cm,bottom=1.8cm,includehead,includefoot}
%\geometry{left=1in,right=1in,top=1in,bottom=1in}
%\geometry{left=2.5cm,right=2.1cm,top=1.7cm,bottom=2cm,includehead,includefoot}
%\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
\usepackage{url,hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black} % 去掉目录红框
\usepackage[english]{babel}
\usepackage{imakeidx}
\usepackage{color,xcolor}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{tabularx,array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{fancybox}
\usepackage{makecell}
\usepackage{xstring}
%\usepackage[english]{babel}
\usepackage{listings}
\usepackage{titletoc}
\usepackage{titlesec}
\usepackage{mathtools}
\usepackage{float}
\usepackage{bookmark}
\usepackage[numbers]{natbib}

%\usepackage{indentfirst}
\usepackage[perpage,symbol]{footmisc}   % footnote control

%\usepackage{appendix}

\makeindex
%\bibliographystyle{plain}

%---- header and footer position -----
\addtolength{\headsep}{-0.1cm}
\addtolength{\footskip}{-0.1cm}
%---- Contents Setting -----
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}

%\newcommand{\makeheadrule}{%
%    \makebox[-3pt][l]{\rule[.7\baselineskip]{\headwidth}{0.4pt}}
%    \rule[0.85\baselineskip]{\headwidth}{1.5pt}\vskip-.8\baselineskip}
%
%\makeatletter
%\renewcommand{\headrule}{%
%    {\if@fancyplain\let\headrulewidth\plainheadrulewidth\fi
%     \makeheadrule}}
%\pagestyle{fancyplain}

\usepackage[cleardoublepage=plain]{scrextend}

\usepackage{fancyhdr,fancyref}
\pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{\thechapter ~ #1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection ~ #1}{}}
\fancyhf{}  % remove the original style
\fancyhead[RO,LE]{~\thepage~}
\fancyhead[LO]{\rmfamily \rightmark}
\fancyhead[RE]{\rmfamily \leftmark}

%\setlength{\parskip}{3pt plus1pt minus1pt}

\renewcommand{\baselinestretch}{1.2}

%----- theorem setting -----
\theoremstyle{plain}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{example}{Example}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\newtheorem{remark}{Remarks}[chapter]
\newtheorem{exercise}{Exercise}[chapter]
\newtheorem{assumption}{Assumption}[chapter]
\newtheorem{axiom}{Axiom}[chapter]
\newtheorem{property}{Property}[chapter]
\newtheorem{conjecture}{Conjecture}[chapter]
%\renewcommand{\proofname}{Proof}

% number of equation, figure and table
\numberwithin{equation}{chapter}
\numberwithin{figure}{chapter}
\numberwithin{table}{chapter}

% define new command
\newcommand{\CC}{\ensuremath{\mathbb{C}}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\ii}{\bm{\mathrm{i}}\,}  % imaginary part
\newcommand{\md}{\mathrm{d}\,}
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\red}[1]{\textcolor{red}{#1}}

\newcommand{\plogo}{\fbox{$\mathcal{PL}$}} % Generic dummy publisher logo

\graphicspath{{./figure/}{./figures/}{./image/}{./images/}}

%----- book information -----

\title{THE BOOK \\[8pt] \LaTeX ~TEMPLATES}
\author{John Smith}
\date{\today}

\begin{document}

%\maketitle

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage} % Suppresses headers and footers on the title page

    \pdfbookmark[0]{Cover}{cover} % book cover

	\centering % Centre everything on the title page

	\scshape % Use small caps for all text on the title page

	\vspace*{2\baselineskip} % White space at the top of the page

	%------------------------------------------------
	%	Title
	%------------------------------------------------

	\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt} % Thick horizontal rule
	\rule{\textwidth}{0.4pt} % Thin horizontal rule

	\vspace{0.75\baselineskip} % Whitespace above the title

    \makeatletter

	{\LARGE\bfseries \@title \\} % Title

	\vspace{0.75\baselineskip} % Whitespace below the title

	\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt} % Thin horizontal rule
	\rule{\textwidth}{1.6pt} % Thick horizontal rule

	\vspace{2\baselineskip} % Whitespace after the title block

	%------------------------------------------------
	%	Subtitle
	%------------------------------------------------

	% A Number of Fascinating and Life-changing Templates Presented in a Clear and Concise Way

	\vspace*{3\baselineskip} % Whitespace under the subtitle

	%------------------------------------------------
	%	Editor(s)
	%------------------------------------------------

	Edited By

	\vspace{0.5\baselineskip} % Whitespace before the editors

	{\scshape\Large \@author \\} % Editor list

	\vspace{0.5\baselineskip} % Whitespace below the editor list

	\textit{The University Name} % Editor affiliation

	\vfill % Whitespace between editor names and publisher logo

    \makeatletter

	%------------------------------------------------
	%	Publisher
	%------------------------------------------------

	\plogo % Publisher logo

	\vspace{0.3\baselineskip} % Whitespace under the publisher logo

	2021 % Publication year

	{\large publisher} % Publisher

\end{titlepage}

\thispagestyle{empty}

\frontmatter

\chapter{Preface}

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

%\clearpage
\cleardoublepage
\phantomsection
\pdfbookmark[chapter]{\contentsname}{toc}
\tableofcontents

\mainmatter

\chapter{The first chapter}

\section{The first section}\label{my label}
LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation. LaTeX is the de facto standard for the communication and publication of scientific documents.

\subsection{A sub section}
LaTeX is not a word processor! Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content. For example consider this document:
\begin{equation}\label{eqn:trifun}
\sin^2{\theta}+\cos^2{\theta}=1.
\end{equation}

LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
$ \Rightarrow $
\begin{align}
a & = b + c \\
& = d + e.
\end{align}

Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.

An example of the \verb|\cite| command to cite within the book:

This statement requires citation \cite{Adams2003} and \cite{Shen1994,Tadmor2012,TreWei2014}

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\section{The second section}
LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation. LaTeX is the de facto standard for the communication and publication of scientific documents.

\subsection{A sub section}
LaTeX is not a word processor! Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content. For example consider this document:

LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
$ \Rightarrow $

Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.

\begin{definition}
This is a definition environment.
\end{definition}

\begin{lemma}
This is a lemma environment.
\end{lemma}

\begin{theorem}
This is a theorem environment.
\end{theorem}

\begin{proposition}
This is a proposition environment.
\end{proposition}

\begin{theorem}[Mass--energy]
This is a theorem environment.
\end{theorem}
\begin{proof}
  This is a proof environment.
\end{proof}

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\section{The third section}
LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation. LaTeX is the de facto standard for the communication and publication of scientific documents.

\subsection{A sub section}
LaTeX is not a word processor! Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content. For example consider this document:

LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
$ \Rightarrow $

Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\chapter{The second chapter}

\section{The first section}
LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation. LaTeX is the de facto standard for the communication and publication of scientific documents.

\subsection{A sub section}
LaTeX is not a word processor! Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content. For example consider this document:

LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
$ \Rightarrow $

\begin{equation}\label{eqn:1}
\left\{\begin{aligned}
  &-\frac{\mathrm{d}^{2} u}{\mathrm{d} x^{2}}+\frac{\mathrm{d} u}{\mathrm{d} x}=\pi^{2} \sin (\pi x)+\pi \cos (\pi x),\quad x \in [0,1], \\
  &u(0)=0,\quad u(1)=0.
\end{aligned} \right.
\end{equation}

Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\section{The second section}
LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation. \index{LaTeX} is the de facto standard for the communication and publication of scientific documents.

\subsection{A sub section}
LaTeX is not a word processor! Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content. For example consider this document:

LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
$ \Rightarrow $

Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\appendix

\chapter{This is the first appendix}
\section{A sub section}

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. Thequick brown \index{fox} jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\section{A sub section}

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\chapter{This is the second appendix}
\section{A sub section}

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\section{A sub section}

The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

\backmatter

\renewcommand{\bibname}{References}

% add References to contents
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{\bibname}

\bibliographystyle{plain}
\bibliography{mybib}

%\begin{thebibliography}{99}
%\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces[M]. Elsevier, 2003.
%
%\bibitem{Shen1994} Shen~J. Efficient spectral-Galerkin method I. Direct solvers of second- and fourth-order equations using Legendre polynomials[J]. SIAM J. Sci. Comput., 1994, 15(6): 1489-1505.
%
%\bibitem{Tadmor2012} Tadmor~E. A review of numerical methods for nonlinear partial differential
%  equations[J]. Bull. Amer. Math. Soc., 2012, 49(4): 507-554.
%
%\bibitem{TreWei2014} Trefethen~L~N, Weideman~J~A~C. The exponentially convergent trapezoidal rule[J]. SIAM Rev., 2014, 56(3): 385-458.
%
%\end{thebibliography}

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{\indexname}
\printindex

\end{document}

### 2021-12-03 book-en/compile-pdflatex-bibtex.sh
Update

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+#-> Get source filename
+find . -name "*.tex"|while read FileName;
+do 
+#--- Process FileName.tex ---
+echo "$FileName"
+echo "${FileName%.tex}"
+#-> Compile the main file
+pdflatex --synctex=-1 "$FileName"
+bibtex "${FileName%.tex}"
+pdflatex --synctex=-1 "$FileName"
+pdflatex --synctex=-1 "$FileName"
+#clear aux files
+rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
+done
+

### 2021-12-04 book-en/book-en.tex
Update

--- 2021-12-03 book-en/book-cover-en.tex
@@
 
-%----- usepackage for tempalate -----
+%----- Packages for template -----
 \usepackage{amsmath,amsthm,amssymb,amsfonts}
@@
 \usepackage{url,hyperref}
-\hypersetup{colorlinks=true,linkcolor=black,citecolor=black} % 去掉目录红框
+\hypersetup{colorlinks=true,linkcolor=black,citecolor=black}
 \usepackage[english]{babel}
@@
 %\usepackage{indentfirst}
-\usepackage[perpage,symbol]{footmisc}   % footnote control
+\usepackage[perpage,symbol]{footmisc}   % footnote setting
 
@@
 
-\title{THE BOOK \\[8pt] \LaTeX ~TEMPLATES}
-\author{John Smith}
+\title{\bfseries LaTeX Book Sample}
+\author{Edited by John Smith}
 \date{\today}
@@
 
-%\maketitle
-
-%----------------------------------------------------------------------------------------
-%	TITLE PAGE
-%----------------------------------------------------------------------------------------
-
-\begin{titlepage} % Suppresses headers and footers on the title page
-
-    \pdfbookmark[0]{Cover}{cover} % book cover
-
-	\centering % Centre everything on the title page
-
-	\scshape % Use small caps for all text on the title page
-
-	\vspace*{2\baselineskip} % White space at the top of the page
-
-	%------------------------------------------------
-	%	Title
-	%------------------------------------------------
-
-	\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt} % Thick horizontal rule
-	\rule{\textwidth}{0.4pt} % Thin horizontal rule
-
-	\vspace{0.75\baselineskip} % Whitespace above the title
-
-    \makeatletter
-
-	{\LARGE\bfseries \@title \\} % Title
-
-	\vspace{0.75\baselineskip} % Whitespace below the title
-
-	\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt} % Thin horizontal rule
-	\rule{\textwidth}{1.6pt} % Thick horizontal rule
-
-	\vspace{2\baselineskip} % Whitespace after the title block
-
-	%------------------------------------------------
-	%	Subtitle
-	%------------------------------------------------
-
-	% A Number of Fascinating and Life-changing Templates Presented in a Clear and Concise Way
-
-	\vspace*{3\baselineskip} % Whitespace under the subtitle
-
-	%------------------------------------------------
-	%	Editor(s)
-	%------------------------------------------------
-
-	Edited By
-
-	\vspace{0.5\baselineskip} % Whitespace before the editors
-
-	{\scshape\Large \@author \\} % Editor list
-
-	\vspace{0.5\baselineskip} % Whitespace below the editor list
-
-	\textit{The University Name} % Editor affiliation
-
-	\vfill % Whitespace between editor names and publisher logo
-
-    \makeatletter
-
-	%------------------------------------------------
-	%	Publisher
-	%------------------------------------------------
-
-	\plogo % Publisher logo
-
-	\vspace{0.3\baselineskip} % Whitespace under the publisher logo
-
-	2021 % Publication year
-
-	{\large publisher} % Publisher
-
-\end{titlepage}
+\maketitle
 

### 2022-01-08 paper-cn/compile-xelatex.sh
Update

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+#-> Get source filename
+find . -name "*.tex"|while read FileName;
+do 
+#--- Process FileName.tex ---
+echo "$FileName"
+echo "${FileName%.tex}"
+#-> Compile the main file
+xelatex --synctex=-1 "$FileName"
+xelatex --synctex=-1 "$FileName"
+#clear aux files
+rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
+done
+

### 2022-07-18 zhbook/makefiles.sh
update

@@ -1,17 +1,0 @@
-#!/bin/bash
-
-#-> Get source filename
-find . -name "*.tex"|while read FileName;
-do 
-#--- Process FileName.tex ---
-echo "$FileName"
-echo "${FileName%.tex}"
-#-> Compile the main file
-xelatex --synctex=-1 "$FileName"
-bibtex "${FileName%.tex}"
-xelatex --synctex=-1 "$FileName"
-xelatex --synctex=-1 "$FileName"
-#clear aux files
-rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
-done
-

### 2022-10-27 cover-letter/cover_letter2.tex
update

% LaTeX Cover Letter Template

\documentclass[a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage}
%\usepackage{geometry}
%\geometry{margin=1.25in}
%showframe  % Uncomment to show frames around the margins

% Default font family: sans serif
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}

\pagenumbering{gobble} % No page numbering

\usepackage{amsmath,amsthm,amssymb}
\usepackage{amsfonts,bm,version}
\usepackage{graphicx,fancybox,mathrsfs}
\usepackage{color,xcolor}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{caption}
\allowdisplaybreaks

%\usepackage{charter} % Charter font

\usepackage{fancyhdr}       % Required for customizing headers and footers

\fancypagestyle{main}{%
	\fancyhf{} % Clear default headers/footers
	\renewcommand{\headrulewidth}{0pt} % No header rule
	\renewcommand{\footrulewidth}{0.5pt} % Footer rule thickness
}
%\pagestyle{main}

\setlength{\parindent}{0pt}     % Paragraph indentation
\setlength{\parskip}{1em}       % Vertical space between paragraphs

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	First page header
%----------------------------------------------------------------------------------------

\includegraphics[width=0.5\textwidth]{UnivLogo.png} % Logo

\vspace{-1em}

\rule{\linewidth}{0.5pt} % Horizontal rule

\vskip2.5em

%----------------------------------------------------------------------------------------
%	Your information
%----------------------------------------------------------------------------------------

\hfill
\begin{tabular}{l @{}}
	\textbf{XX research group} \\
    \textbf{Department of Mathematics} \\
    University of XXXX \\
    XX Building, XX Road \\
	City 200123, P. R. China. \\[10pt] % Address
    \textbf{Dr. Who} \\
	Email: xxx@univ.edu.cn \bigskip \\
    \today \\ % Date
\end{tabular}

\bigskip

\bigskip

%Dear Mrs.\ XXX,
Dear Editor,

\bigskip

%----------------------------------------------------------------------------------------
%	Letter body
%----------------------------------------------------------------------------------------

Please find attached the manuscript ``PAPER TITLE" by Author A and Author B for consideration as a Research Article in XX.

Our work builds on the considerable interest of the scientific community in XXX [cite]. This  is more impressing especially since the XX were recently experimentally demonstrated [cite].

Hitherto, XX have increasingly been investigated [cite]. However, the ``missing component" has  been XXX. XXX will enable future XXX.

In this paper, we XXX.

We are convinced that this work will have implications for XXX. As such, the research should  appeal to a broad audience interested in XXX. We thus believe that the manuscript is  appropriate for the readership of XX.

We remain at your disposal for any further questions.

\bigskip %

Sincerely yours,

\includegraphics[height=1.5cm]{signature}

%\vspace{25pt} %

Andy

\end{document}

### 2022-10-29 note-temp/main-en.tex
update

--- 2021-09-13 note-temp/elegantnote-en.tex
@@
-%\documentclass[en,hazy,screen,blue,14pt]{elegantnote}
+%!TEX program = xelatex
+%\documentclass[en,hazy,normal,blue,11pt]{elegantnote}
+\documentclass[en,normal,12pt,blue]{elegantnote}
+\usepackage{amssymb,mathrsfs,multirow}
+%\usepackage[notcite,notref]{showkeys}
+%\usepackage{epsfig}
+%\usepackage{tabularx}
+\usepackage{diagbox}
+%\usepackage{bookmark}
+\usetikzlibrary{arrows,shapes}
+\usepackage{array,makecell}
+%\usepackage{tikz}
+%\usepackage{tikzpagenodes}
+%\usetikzlibrary{shapes.geometric,shapes.symbols,shapes.callouts,decorations.markings,shapes.misc,shapes.arrows}
 
-\documentclass[en,normal,11pt,blue]{elegantnote}
-\usepackage{epsfig,amssymb,amsmath,version}
-\usepackage{amssymb,version,graphicx,fancybox,mathrsfs,multirow}
-%\usepackage[notcite,notref]{showkeys}
-\usepackage{diagbox}
-\usetikzlibrary{arrows,shapes}
+\usepackage[numbers,sort&compress]{natbib}
+\def\bibfont{\small}      % 修改参考文献字体
+\setlength{\bibsep}{8pt}  % 调整参考文献间距
+%\usepackage{subfig}
 
-\usepackage{tocloft}
-\renewcommand{\cfttoctitlefont}{\hfill \bfseries \LARGE}
-\renewcommand{\contentsname}{\centerline{\color{ecolor}Contents}}
-\renewcommand{\cftaftertoctitle}{\hfill}
-\setlength{\cftbeforetoctitleskip}{10ex}
-\setlength{\cftaftertoctitleskip}{5ex}
-\renewcommand{\cftsecdotsep}{\cftdotsep} 
-\renewcommand{\cftbeforesecskip}{3ex}
-\renewcommand{\cftbeforesubsecskip}{1ex}
+% --- 算法宏包及设置 ---
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\floatname{algorithm}{Algorithm}
+\algrenewcommand\algorithmicrequire{\textbf{Input:}}
+\algrenewcommand\algorithmicensure{\textbf{Output:}}
 
-\title{ElegantNote: An Elegant \LaTeX{} Template for Notes}
+% --- 代码高亮 ---
+%\input{matlab-style.tex}
 
-\author{Dongsheng Deng}
-\institute{Elegant\LaTeX{} Program}
+%\definecolor{hong}{RGB}{199,21,133}
+%\definecolor{huang}{RGB}{255,164,0}
 
-\version{2.30}
-\date{\today}
+%\makeatletter
+%\newcommand\HUGE{\@setfontsize\Huge{32}{36}}
+%\makeatother
+
+%\bibliographystyle{thuthesis-numeric}
+\bibliographystyle{plain}
+
+% --- 自定义命令 -----
+\newcommand{\CC}{\ensuremath{\mathbb{C}}}
+\newcommand{\RR}{\ensuremath{\mathbb{R}}}
+\newcommand{\A}{\mathcal{A}}
+\newcommand{\ii}{\bm{\mathrm{i}}\,}  % 虚部
+\newcommand{\bA}{\boldsymbol{A}}
+\newcommand{\red}[1]{\textcolor{red}{#1}}
+\newcommand{\blue}[1]{\textcolor{blue}{#1}}
+\newcommand{\mT}{\mathrm{T}}
+\newcommand{\md}{\mathrm{d}}
+
+%\title{\LaTeX 笔记模板}
+%\author{某某某}
+%\institute{}
+%\version{1.3}
+%\date{\zhtoday}
+%\date{}
 
 \begin{document}
-\maketitle
+%\maketitle
 
-\pagenumbering{Roman}
+\pagenumbering{Roman} % 页码为大写罗马数字
 
-%\input{Cover.tex}
+\input{cover2.tex}
+
+% ----- generate a empty page -----
+%\clearpage%
+%\thispagestyle{empty}%
+%\addtocounter{page}{-1}%
+%\null%
 %\clearpage
 
-% ----- generate a empty page -----
-%\newpage\null\thispagestyle{empty}\newpage \addtocounter{page}{-1}
-%\addtocounter{page}{-1}
-
-\vskip -2em
+\clearpage
+%\phantomsection
+\pdfbookmark[1]{Contents}{toc}
 \tableofcontents
 \clearpage
+\setlist[itemize]{label=$\circ$}
 
 \pagenumbering{arabic}  % 页码为阿拉伯数字
+
+%==========================================%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 正文内容从这里开始  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{itemize}
-
-This update is to resolve \TeX{} Live 2020 compilation errors caused by \lstinline{gbt7714} compatibility issues.
 
@@
 
-\section{Recruit Support Members}
-
-Recruit support members for Elegant\LaTeX{} to translate template official guide, maintain wiki entries, update Wechat articles. No deadline for this recruitment.
-
-So far, Elegant\LaTeX{} has four support members:
-\begin{itemize}
-	\item OG Translator: \href{https://github.com/peggy2006xzyz}{YPY};
-	\item Wiki Maintainer: \href{https://github.com/izinngo}{Ingo Zinngo}, \href{https://github.com/xiaohao890809}{Xiaohao890809};
-	\item QQ Group Manager: \href{https://github.com/sikouhjw}{Sikouhjw}.
-\end{itemize}
-
-Thank them all!!!
+Citation \cite{Tadmor2012} and \cite{Adams2003,TreWei2014}.  Citation \cite{Adams2003,Shen1994}.
 
 \section{Acknowledgement}
-The number of stars on GitHub for ElegantPaper reached 176 on April 12, 2020 at the release of ElegantNote v2.20.
-Thank China\TeX{} and \href{http://www.latexstudio.net/}{\LaTeX{} studio} for their promotion.
 
-If you like our templates, star on GitHub.
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=\textwidth]{star.png}
-	\caption{Twinkle, Twinkle, Little Star}
-\end{figure}
-
-\section{Donation}
-To express your love for our templates and/or our developers, please do not hesitate to tip us.
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.4\textwidth]{donate.jpg}
-\end{figure}
-
-\textbf{The explanation right of the tip usage belongs to Elegant\LaTeX{} with no supervision.
-Feel free to tip us.} Those who donate more than 10 RMB will be recorded in the donation list and will receive a donation certificate.
-Thank all the tippers!
-
-\begin{table}[htbp]
-  \centering
-  \scriptsize
-  \caption{Donation List}
-    \begin{tabular}{cccccccc}
-    \toprule
-    \textbf{Tipper} & \textbf{Amount} & \textbf{Date} & \textbf{Channel} & \textbf{Tipper} & \textbf{Amount} & \textbf{Date} & \textbf{Channel} \\
-    \midrule
-    Lerh  & 10 RMB & 2019/05/15 & Wechat    & yueguodipingxian & 10 RMB & 2019/05/15 & Wechat \\
-	  yinsang    & 20 RMB & 2019/05/27 & Wechat    & *kong    & 10 RMB & 2019/05/30 & Wechat \\
-	  latexstudio.net & 666 RMB & 2019/06/05 & Alipay   & A*n   & 40 RMB & 2019/06/15 & Wechat \\
-	  * xia   & 22 RMB & 2019/06/15 & Wechat    & * qian  & 21 RMB  & 2019/06/15 & Wechat \\
-	  Cassis & 11 RMB & 2019/06/30 & Wechat    & * jun    & 10 RMB & 2019/07/23 & Wechat \\
-	  P*u   & 50 RMB & 2019/07/30 & Wechat    & * meng    & 19 RMB & 2019/08/28 & Wechat \\
-	  Qu Doudou   & 10 RMB & 2019/08/28 & Wechat    & Li Bo    & 100 RMB & 2019/10/06 & Wechat \\
-	  Njustsll & 10 RMB & 2019/10/11 & Wechat    & Liu Zhikuo   & 99.99 RMB & 2019/10/15 & Alipay \\
-	  * tao   & 16 RMB & 2019/10/17 & Wechat    & Chini    & 12 RMB & 2019/10/17 & Alipay \\
-	  yuanfengjing & 10 RMB & 2019/10/28 & Wechat    & Guo Deliang   & 88 RMB & 2019/11/03 & Wechat \\
-	  ziqiangbuxi  & 20 RMB & 2019/11/04 & Alipay   & dushuzhichong  & 20 RMB & 2019/11/18 & Wechat \\
-	  * deng    & 10 RMB & 2019/11/18 & Wechat    & * zhe   & 20 RMB & 2019/11/18 & Wechat \\
-	  anonymous    & 10 RMB & 2019/11/24 & Wechat    & Jiye Qian & 66 RMB & 2019/12/04 & Wechat \\
-	  * yang   & 20 RMB & 2019/12/05 & Wechat    & Catcher & 11 RMB & 2019/12/08 & Alipay \\
-	  xierbotementu & 10 RMB & 2019/12/09 & Alipay   & * wei   & 10 RMB & 2019/12/09 & Wechat \\
-	  Simon & 20 RMB & 2019/12/11 & Alipay   & liushangqianyi & 66.60 RMB & 2019/12/18 & Alipay \\
-	  yu     & 10 RMB & 2019/12/20 & Alipay   & *chen   & 15 RMB & 2019/12/20 & Wechat \\
-	  suifeng   & 20 RMB & 2019/12/27 & Alipay   & Ws    & 23.30 RMB & 2019/12/28 & Wechat \\
-	  chuba    & 100 RMB  & 2020/01/02 & Alipay   & p*e   & 20 RMB & 2020/01/03 & Wechat \\
-	  Shunmx & 100 RMB & 2020/01/03 & Wechat    & hj    & 10 RMB & 2020/01/03 & Wechat \\
-	  F*5   & 10 RMB & 2020/01/03 & Wechat    & S*m   & 20.20 RMB & 2020/01/03 & Wechat \\
-	  erdaiqingzhi  & 13 RMB & 2020/01/14 & Alipay   & *?    & 66 RMB & 2020/01/15 & Wechat \\
-	  Mr. Xiong & 20 RMB & 2020/01/17 & Wechat    & *bo    & 15 RMB & 2020/01/18 & Wechat \\
-	  *Zhe    & 10 RMB & 2020/02/02 & Wechat    &  Jackie &  88.80 RMB  &  2020/02/09 & Wechat \\
-	  Henry\_Sun & 50 RMB & 2020/02/14 & Alipay & * Qiao  & 50 RMB & 2020/02/21 & Wechat \\
-	  YunLian & 10 RMB & 2020/03/02 & Alipay & S*y  &  10 RMB  &  2020/03/15 & Wechat \\
-	  * Ge  & 66.66 RMB & 2020/03/17 & Wechat    &   K*e & 30 RMB & 2020/03/30 & Wechat\\
-	  * Yang  &  20 RMB  &  2020/04/02 & Wechat & Shi*n  & 30 RMB & 2020/04/11 & Wechat \\
-\bottomrule
-\end{tabular}%
-  \label{tab:donation}%
-\end{table}%
+Thank \href{https://github.com/sikouhjw}{sikouhjw} and \href{https://github.com/syvshc}{syvshc} for their quick response to Github issues and continuously support work for ElegantLaTeX.
+Thank ChinaTeX and \href{http://www.latexstudio.net/}{LaTeX Studio} for their promotion.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%% 参考文献 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
+\phantomsection
+\addcontentsline{toc}{section}{References} % 添加  "参考文献 " 到目录
+
+% 生成参考文献, 使用第一种请把第二种全部注释
+
+% 第一种方式, 使用 bib 文件
+
+%\nocite{*}  % 可以暂时显示全部参考文献, 包括未引用的
+
+\bibliography{reference}
+
+% 第二种方式, 按照格式直接写文献信息, 使用第二种请把第一种全部注释
+
+%\begin{thebibliography}{99}
+%\bibitem{Tadmor2012} Tadmor~E. A review of numerical methods for nonlinear partial differential
+%  equations\allowbreak[J]. Bull. Amer. Math. Soc., 2012, 49(4): 507-554.
+%
+%\bibitem{LiLiu1997} 李荣华, 刘播. 微分方程数值解法\allowbreak[M]. 东南大学出版社, 1997.
+%
+%\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces\allowbreak[M]. Elsevier, 2003.
+%
+%\bibitem{TreWei2014}Trefethen~L~N, Weideman~J~A~C. The exponentially convergent trapezoidal rule\allowbreak[J]. SIAM Rev., 2014, 56(3): 385-458.
+%
+%\bibitem{Shen1994} Shen~J.
+Efficient spectral-Galerkin method I.
+Direct solvers of second- and fourth-order equations using Legendre polynomials\allowbreak[J].
+SIAM J.
+Sci.
+Comput., 1994, 15(6): 1489-1505.
+%
+%\end{thebibliography}
+
+%\printbibliography[heading=bibintoc, title=\ebibname]
+
 \end{document}

### 2022-10-29 note-temp/matlab-style.tex
update

--- 2021-09-13 note-temp/elegantnote-cn-code.tex
@@
-%!TEX program = xelatex
-%\documentclass[cn,hazy,blue,14pt,screen]{elegantnote}
-
-\documentclass[cn,normal,11pt,blue]{elegantnote}
-\usepackage{epsfig,amssymb,amsmath,version}
-\usepackage{amssymb,version,graphicx,fancybox,mathrsfs,multirow}
-%\usepackage[notcite,notref]{showkeys}
-\usepackage{fontspec}
-\usepackage{diagbox}
-\usetikzlibrary{arrows,shapes}
-
-\usepackage{tocloft}
-\renewcommand{\cfttoctitlefont}{\hfill \bfseries \LARGE}
-\renewcommand{\contentsname}{\centerline{\color{ecolor}目~~录}}
-\renewcommand{\cftaftertoctitle}{\hfill}
-\setlength{\cftbeforetoctitleskip}{10ex}
-\setlength{\cftaftertoctitleskip}{5ex}
-\renewcommand{\cftsecdotsep}{\cftdotsep}  % 设置Section引导点
-\renewcommand{\cftbeforesecskip}{3ex}
-\renewcommand{\cftbeforesubsecskip}{1ex}
-% \renewcommand{\cftsecfont}{\songti}   % 设置Section字体
-
 %%%%%%%%%%%%%%%%%%%%%%%%% Code Style %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   breaklines=true,                     % sets automatic line breaking
+  numberstyle=\tiny\color{mNumber},
+  numbers=left,                        % where to put the line-numbers
+  stepnumber=1,                        % the step between two line-numbers.
 }
@@
 \lstinputpath{{./M-files/}}
-
-% Using: \lstinputlisting{Euler1.m}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{ElegantNote：一个优美的 \LaTeX{} 笔记模板}
-
-\author{邓东升}
-\institute{Elegant\LaTeX{} Program}
-
-\version{2.30}
-\date{\zhtoday}
-
-\usepackage{array}
-
-\begin{document}
-\maketitle
-
-\pagenumbering{Roman} % 页码为大写罗马数字
-
-%\input{Cover.tex}
-%\clearpage
-
-% ----- generate a empty page -----
-%\newpage\null\thispagestyle{empty}\newpage \addtocounter{page}{-1}
-%\addtocounter{page}{-1}
-
-\vskip -2em
-\tableofcontents
-\clearpage
-\setlist[itemize]{label=$\circ$}
-
-\pagenumbering{arabic}  % 页码为阿拉伯数字
-
-\section{ElegantNote 使用说明}
-
-新版 ElegantNote 是基于标准的 \LaTeX{} 文类 article 重新设计的，格式更加简化的笔记模板！本模板支持两种编译方式，\hologo{pdfLaTeX} 和 \hologo{XeLaTeX}，英文模式下请使用 \hologo{pdfLaTeX} 进行编译，中文模式下推荐使用 \hologo{XeLaTeX}。
-
-新模板有下面几个特性：
-
-\begin{itemize}
-  \item 纸张模式：护眼模式（geye）和朦胧模式（hazy）；
-  \item 适配不同设备，包括 Pad（默认），Screen（幻灯片），Kindle，PC（双页），通用（A4 纸张）；
-  \item 5 套颜色主题，分别是：\textcolor{eblue}{blue}（默认）、\textcolor{egreen}{green}、\textcolor{ecyan}{cyan}、 \textcolor{sakura}{sakura} 和 \textcolor{black}{black}；
-  \item 语言支持：中文（默认），英文；
-  \item 支持 \hologo{pdfLaTeX} 和 \hologo{XeLaTeX} 编译；
-  \item 更加美观的图表标题格式，列表环境，数学字体等；
-  \item 全局字体大小支持：8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, 和 20pt；
-  \item 支持 \lstinline{newtx} 以及 \lstinline{mtpro2} 数学字体设置；
-  \item 中文字体支持方正字体或者自定义字体；
-  \item 英文模式通过 \lstinline{bibstyle} 选项（默认为 \lstinline{apalike}）支持参考文献格式修改；
-  \item 支持参考格式显示格式修改 \lstinline{cite} 可选为 \lstinline{authoryear}、\lstinline{numbers} （默认）和 \lstinline{super}。
-\end{itemize}
-
-本次更新：修复 \TeX{} Live 2020 更新之后因 \lstinline{gbt7714} 宏包更新用法导致模板出错的问题。
-
-\subsection{模板模式}
-
-本模板增加了模式选项，分别有护眼模式（\lstinline{mode=geye}）和朦胧模式（\lstinline{mode=hazy}）。其中护眼模式设置纸张底色为绿豆沙颜色，而朦胧模式为淡蓝色，开启的方法如下：
-\begin{lstlisting}[frame=none]
-  \documentclass[geye]{elegantnote} % or
-  \documentclass[mode=geye]{elegantnote}
-  \documentclass[hazy]{elegantnote} % or
-  \documentclass[mode=hazy]{elegantnote}
-\end{lstlisting}
-
-\begin{remark}
-  如果你想为自己的文档添加底色，可以在导言区添加下面设置：
-  \begin{lstlisting}
-    \definecolor{geyecolor}{RGB}{199,237,204}
-    \pagecolor{geyecolor}
-  \end{lstlisting}
-\end{remark}
-
-\subsection{设备选择}
-
-为了让笔记方便在不同设备上阅读，免去切边，缩放等操作，本模板适配不同的设备，分别为 Pad（默认），Kindle，PC，A4。
-
-\textcolor{red}{\kaishu 新增}：为了方便展示笔记，2.20 版本新增了 \lstinline{device=screen} 设备选项，大小为 MS Powerpoint 的纸张大小，比例为 4:3（2019/12/06）。
-
-不同屏幕的选择为
-\begin{lstlisting}[frame=none]
-  \documentclass[device=pad]{elegantnote}    % ipad screen size
-  \documentclass[device=kindle]{elegantnote} % kindle screen size
-  \documentclass[device=pc]{elegantnote}     % double pages for pc
-  \documentclass[device=normal]{elegantnote} % a4 normal page
-  \documentclass[device=screen]{elegantnote} % 4:3 PPT size
-\end{lstlisting}
-\begin{note}
-也可以采取直接赋值的方法选择屏幕，比如：
-\end{note}
-\begin{lstlisting}[frame=none]
-  \documentclass[pad]{elegantnote}
-  \documentclass[kindle]{elegantnote}
-  \documentclass[pc]{elegantnote}
-  \documentclass[normal]{elegantnote}
-  \documentclass[screen]{elegantnote}
-\end{lstlisting}
-
-\begin{note}
-  如果想要正常的 A4 大小的 PDF，需要选择 \lstinline{device=normal}。
-\end{note}
-
-\subsection{数学字体选项}
-
-本模板定义了一个数学字体选项（\lstinline{math}），可选项有三个：
-\begin{enumerate}
-  \item \lstinline{math=cm}（默认），使用 \LaTeX{} 默认数学字体（推荐，无需声明）；
-  \item \lstinline{math=newtx}，使用 \lstinline{newtxmath} 设置数学字体（潜在问题比较多）。
-  \item \lstinline{math=mtpro2}，使用 \lstinline{mtpro2} 宏包设置数学字体，要求用户已经成功安装此宏包。
-\end{enumerate}
-
-\subsection{中文字体选项}
-模板提供中文字体选项 \lstinline{chinesefont}，可选项有
-\begin{enumerate}
-\item \lstinline{ctexfont}：默认选项，使用 \lstinline{ctex} 宏包根据系统自行选择字体，可能存在字体缺失的问题，更多内容参考 \lstinline{ctex} 宏包\href{https://ctan.org/pkg/ctex}{官方文档}\footnote{可以使用命令提示符，输入 \lstinline{texdoc ctex} 调出本地 \lstinline{ctex} 宏包文档}。
-\item \lstinline{founder}：方正字体选项，调用 \lstinline{ctex} 宏包并且使用 \lstinline{fontset=none} 选项，然后设置字体为方正四款免费字体，方正字体下载注意事项见后文。
-\item \lstinline{nofont}：调用 \lstinline{ctex} 宏包并且使用 \lstinline{fontset=none} 选项，不设定中文字体，用户可以自行设置中文字体，具体见后文。
-\end{enumerate}
-
-\noindent \textbf{注意：} 使用 \lstinline{founder} 选项或者 \lstinline{nofont} 时，必须使用 \hologo{XeLaTeX} 进行编译。
-
-\subsubsection{方正字体选项}
-由于使用 \lstinline{ctex} 宏包默认调用系统已有的字体，部分系统字体缺失严重，因此，用户希望能够使用其它字体，我们推荐使用方正字体。方正的{\songti 方正书宋}、{\heiti 方正黑体}、{\kaishu 方正楷体}、{\fangsong 方正仿宋}四款字体均可免费试用，且可用于商业用途。用户可以自行从\href{http://www.foundertype.com/}{方正字体官网}下载此四款字体，在下载的时候请\textbf{务必}注意选择 GBK 字符集，也可以使用 \href{https://www.latexstudio.net/}{\LaTeX{} 工作室}提供的\href{https://pan.baidu.com/s/1BgbQM7LoinY7m8yeP25Y7Q}{方正字体，提取码为：njy9} 进行安装。安装时，{\kaishu Win 10 用户请右键选择为全部用户安装，否则会找不到字体。}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\textwidth]{founder.png}
-\end{figure}
-
-\subsubsection{其他中文字体}
-如果你想完全自定义字体\footnote{这里仍然以方正字体为例。}，你可以选择 \lstinline{chinesefont=nofont}，然后在导言区设置
-\begin{lstlisting}
-\setCJKmainfont[BoldFont={FZHei-B01},ItalicFont={FZKai-Z03}]{FZShuSong-Z01}
-\setCJKsansfont[BoldFont={FZHei-B01},ItalicFont={FZHei-B01}]{FZHei-B01}
-\setCJKmonofont[BoldFont={FZHei-B01},ItalicFont={FZHei-B01}]{FZFangSong-Z02}
-\setCJKfamilyfont{zhsong}{FZShuSong-Z01}
-\setCJKfamilyfont{zhhei}{FZHei-B01}
-\setCJKfamilyfont{zhkai}{FZKai-Z03}
-\setCJKfamilyfont{zhfs}{FZFangSong-Z02}
-\newcommand*{\songti}{\CJKfamily{zhsong}}
-\newcommand*{\heiti}{\CJKfamily{zhhei}}
-\newcommand*{\kaishu}{\CJKfamily{zhkai}}
-\newcommand*{\fangsong}{\CJKfamily{zhfs}}
-\end{lstlisting}
-
-\subsection[颜色主题]{颜色主题\footnote{测试章节脚注。}}
-
-本模板内置 5 套颜色主题，分别是 \textcolor{eblue}{blue}（默认），\textcolor{egreen}{green}， \textcolor{ecyan}{cyan}， \textcolor{sakura}{sakura} 和 \textcolor{black}{black}。如果不需要颜色，可以选择黑色（black）主题。颜色主题的设置方法：
-\begin{lstlisting}[frame=none]
-  \documentclass[green]{elegantnote}
-  \documentclass[color=green]{elegantnote}
-  ...
-  \documentclass[black]{elegantnote}
-  \documentclass[color=black]{elegantnote}
-\end{lstlisting}
-
-\subsection{语言模式}
-
-本模板内含两套语言环境，改变语言环境会改变图表标题的引导词（图，表），文章结构词（比如目录，参考文献等），以及定理环境中的引导词（比如定理，引理等）。不同语言模式的启用如下：
-\begin{lstlisting}[frame=none]
-  \documentclass[cn]{elegantnote}
-  \documentclass[lang=cn]{elegantnote}
-  \documentclass[en]{elegantnote}
-  \documentclass[lang=en]{elegantnote}
-\end{lstlisting}
-
-\begin{note}
-只有中文模式才可输入中文，如果需要在英文模式下输入中文，可以自行添加 \lstinline{ctex} 宏包\footnote{需要使用 \lstinline{scheme=plain} 选项才不会把标题改为中文。}或者使用 \lstinline{xeCJK} 宏包设置字体。另外如果在笔记中使用了抄录环境（\lstinline{lstlisting}），并且里面有中文字符，请务必使用 \hologo{XeLaTeX} 编译。
-\end{note}
-
-\subsection{定理类环境}
-
-此模板采用了 \lstinline{amsthm} 中的定理样式，使用了 4 类定理样式，所包含的环境分别为
-\begin{itemize}
-  \item \textbf{定理类}：theorem，lemma，proposition，corollary；
-  \item \textbf{定义类}：definition，conjecture，example；
-  \item \textbf{备注类}：remark，note，case；
-  \item \textbf{证明类}：proof。
-\end{itemize}
-
-\begin{remark}
-在选用 \lstinline{lang=cn} 时，定理类环境的引导词全部会改为中文。
-\end{remark}
-
-\section{写作示例}
-
-我们将通过三个步骤定义可测函数的积分。首先定义非负简单函数的积分。以下设 $E$ 是 $\mathcal{R}^n$ 中的可测集。
-
-\begin{definition}[可积性]
-设 $ f(x)=\sum\limits_{i=1}^{k} a_i \chi_{A_i}(x)$ 是 $E$ 上的非负简单函数，其中 $\{A_1,A_2,\ldots$, $A_k\}$ 是 $E$ 上的一个可测分割，$a_1,a_2,\ldots,a_k$ 是非负实数。定义 $f$ 在 $E$ 上的积分为 1. 3
-\begin{equation}
-   \label{inter}
-   \int_{E} f dx = \sum_{i=1}^k a_i m(A_i).
-\end{equation}
-一般情况下 $0 \leq \int_{E} f dx \leq \infty$。若 $\int_{E} f dx < \infty$，则称 $f$ 在 $E$ 上可积。
-\end{definition}
-
-一个自然的问题是，Lebesgue 积分与我们所熟悉的 Riemann 积分有什么联系和区别？之后我们将详细讨论 Riemann 积分与 Lebesgue 积分的关系。这里只看一个简单的例子。设 $D(x)$ 是区间 $[0,1]$ 上的 Dirichlet 函数。即 $D(x)=\chi_{Q_0}(x)$，其中 $Q_0$ 表示 $[0,1]$ 中的有理数的全体。根据非负简单函数积分的定义，$D(x)$ 在 $[0,1]$ 上的 Lebesgue 积分为
-\begin{equation}\label{inter2}
-  \int_0^1 D(x)dx = \int_0^1 \chi_{Q_0} (x) dx = m(Q_0) = 0
-\end{equation}
-即 $D(x)$ 在 $[0,1]$ 上是 Lebesgue 可积的并且积分值为零。但 $D(x)$ 在 $[0,1]$ 上不是 Riemann 可积的。
-
-\begin{table}[htbp]
-  \centering
-  \small
-  \caption{燃油效率与汽车价格}
-    \begin{tabular}{lcc}
-    \toprule
-                  &       (1)         &        (2)      \\
-    \midrule
-    燃油效率      &   -238.90***      &      -49.51     \\
-                  &    (53.08)        &      (86.16)    \\
-    汽车重量      &                   &        1.75***  \\
-                  &                   &       (0.641)   \\
-    常数项        &  11253.00***      &    1946.00      \\
-                  &  (1171.00)        &   (3597.00)     \\
-    观测数        &     74            &      74         \\
-    $R^2$         &      0.220        &       0.293     \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:reg}%
-\end{table}%
-
-\begin{theorem}[Fubini 定理]\label{thm:fubi}
-若 $f(x,y)$ 是 $\mathcal{R}^p\times\mathcal{R}^q$ 上的非负可测函数，则对几乎处处的 $x\in \mathcal{R}^p$，$f(x,y)$ 作为 $y$ 的函数是 $\mathcal{R}^q$ 上的非负可测函数，$g(x)=\int_{\mathcal{R}^q}f(x,y) dy$ 是 $\mathcal{R}^p$ 上的非负可测函数。并且
-\begin{equation}\label{eq:461}
-  \int_{\mathcal{R}^p\times\mathcal{R}^q} f(x,y) dxdy=\int_{\mathcal{R}^p}\left(\int_{\mathcal{R}^q}f(x,y)dy\right)dx.
-\end{equation}
-\end{theorem}
-
-\begin{proof}
-Let $z$ be some element of $xH \cap yH$.
-Then $z = xa$ for some $a \in H$, and $z = yb$ for some $b \in H$.
-If $h$ is any element of $H$ then $ah \in H$ and $a^{-1}h \in H$, since $H$ is a subgroup of $G$.
-But $zh = x(ah)$ and $xh = z(a^{-1}h)$ for all $h \in H$.
-Therefore $zH \subset xH$ and $xH \subset zH$, and thus $xH = zH$.
-Similarly $yH = zH$, and thus $xH = yH$, as required.
-\end{proof}
-
-回归分析（regression analysis) 是确定两种或两种以上变量间相互依赖的定量关系的一种统计分析方法。根据定理~\ref{thm:fubi}，其运用十分广泛，回归分析按照涉及的变量的多少，分为一元回归和多元回归分析；按照因变量的多少，可分为简单回归分析和多重回归分析；按照自变量和因变量之间的关系类型，可分为线性回归分析和非线性回归分析。
-
-\section{协作人员招募}
-
-招募 Elegant\LaTeX{} 的协作人员，没有工资。工作内容：翻译 Elegant\LaTeX{} 系列模板相关的文稿（中翻英），维护模板的 wiki（主要涉及 Markdown），如果有公众号文稿写作经历的话，也可以帮忙写微信稿。本公告长期有效。
-
-目前 ElegantLaTeX 共有 4 名协作人员，分别是
-\begin{itemize}
-  \item 官方文档翻译: \href{https://github.com/peggy2006xzyz}{YPY};
-  \item GitHub 维基维护: \href{https://github.com/izinngo}{Ingo Zinngo}、\href{https://github.com/xiaohao890809}{追寻原风景};
-  \item QQ 群管理员: \href{https://github.com/sikouhjw}{Sikouhjw}.
-\end{itemize}
-
-在此感谢他们无私的奉献！
-
-\section{致谢}
-
-截止到 2020 年 04 月 12 日，ElegantNote 2.30 版本发布，ElegantNote 模板在 GitHub 上的收藏数（star）达到了 263。在此特别感谢 China\TeX{} 以及 \href{http://www.latexstudio.net/}{\LaTeX{} 工作室}对于本系列模板的大力宣传与推广。如果你喜欢我们的模板，你可以在 GitHub 上收藏（Star）我们的模板。
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=\textwidth]{star.png}
-  \caption{一键三连求赞}
-\end{figure}
-
-\section{MATLAB代码}
-
-\begin{lstlisting}
-% Euler1.m
-% Euler method for the ODE model
-% u'(t)=t^2+t-u, t \in [0,1]
-% Initial condition : u(0)=0 ;
-% Exact solution : u(t)=-exp(-t)+t^2-t+1.
-clear all
-h=0.1;
-x=0:h:1;                       % function interval
-n=length(x)-1;
-u(1)=0;                        % initial value
-fun=@(t,u) t.^2+t-u;           % RHS
-for i=1:n
-    u(i+1)=u(i)+h.*fun(x(i),u(i));
-end
-ue=-exp(-x)+x.^2-x+1;          % exact solution
-plot(x,ue,'b-',x,u,'r+','LineWidth',1.5)
-xlabel('x','fontsize', 16), ylabel('y','fontsize',16,'Rotation',0)
-legend('Exact ','Numerical','location','North')
-title('Euler Method','fontsize',14)
-set(gca,'fontsize',14)
-\end{lstlisting}
-
-\section{捐赠}
-
-如果您非常喜爱我们的模板，你还可以选择捐赠以表达您对我们模板和我的支持！
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=0.4\textwidth]{donate.jpg}
-\end{figure}
-
-\textbf{赞赏费用的使用解释权归 Elegant\LaTeX{} 所有，并且不接受监督，请自愿理性打赏}。10 元以上的赞赏，我们将列入捐赠榜，并且发放捐赠纪念证（全部），谢谢各位金主！
-
-\begin{table}[htbp]
-  \scriptsize
-  \centering
-  \caption{Elegant\LaTeX{} 系列模板捐赠榜}
-    \begin{tabular}{*{8}{>{\scriptsize}c}}
-    \toprule
-    \textbf{捐赠者} & \textbf{金额} & \textbf{时间} & \textbf{渠道} & \textbf{捐赠者} & \textbf{金额} & \textbf{时间} & \textbf{渠道} \\
-    \midrule
-    Lerh  & 10 RMB & 2019/05/15 & 微信    & 越过地平线 & 10 RMB & 2019/05/15 & 微信 \\
-    银桑    & 20 RMB & 2019/05/27 & 微信    & *空    & 10 RMB & 2019/05/30 & 微信 \\
-    latexstudio.net & 666 RMB & 2019/06/05 & 支付宝   & A*n   & 40 RMB & 2019/06/15 & 微信 \\
-    * 夏   & 22 RMB & 2019/06/15 & 微信    & * 倩   & 21 RMB  & 2019/06/15 & 微信 \\
-    Cassis & 11 RMB & 2019/06/30 & 微信    & *君    & 10 RMB & 2019/07/23 & 微信 \\
-    P*u   & 50 RMB & 2019/07/30 & 微信    & *萌    & 19 RMB & 2019/08/28 & 微信 \\
-    曲豆豆   & 10 RMB & 2019/08/28 & 微信    & 李博    & 100 RMB & 2019/10/06 & 微信 \\
-    Njustsll & 10 RMB & 2019/10/11 & 微信    & 刘志阔   & 99.99 RMB & 2019/10/15 & 支付宝 \\
-    * 韬   & 16 RMB & 2019/10/17 & 微信    & 赤霓    & 12 RMB & 2019/10/17 & 支付宝 \\
-    追寻原风景 & 10 RMB & 2019/10/28 & 微信    & 郭德良   & 88 RMB & 2019/11/03 & 微信 \\
-    自强不息  & 20 RMB & 2019/11/04 & 支付宝   & 读书之虫  & 20 RMB & 2019/11/18 & 微信 \\
-    *等    & 10 RMB & 2019/11/18 & 微信    & *哲    & 20 RMB & 2019/11/18 & 微信 \\
-    佚名    & 10 RMB & 2019/11/24 & 微信    & Jiye Qian & 66 RMB & 2019/12/04 & 微信 \\
-    * 阳   & 20 RMB & 2019/12/05 & 微信    & Catcher & 11 RMB & 2019/12/08 & 支付宝 \\
-    希尔波特门徒 & 10 RMB & 2019/12/09 & 支付宝   & * 伟   & 10 RMB & 2019/12/09 & 微信 \\
-    Simon & 20 RMB & 2019/12/11 & 支付宝   & 流殇丶浅忆 & 66.60 RMB & 2019/12/18 & 支付宝 \\
-    羽     & 10 RMB & 2019/12/20 & 支付宝   & * 琛   & 15 RMB & 2019/12/20 & 微信 \\
-    随风    & 20 RMB & 2019/12/27 & 支付宝   & Ws    & 23.30 RMB & 2019/12/28 & 微信 \\
-    初八    & 100 RMB  & 2020/01/02 & 支付宝   & p*e   & 20 RMB & 2020/01/03 & 微信 \\
-    Shunmx & 100 RMB & 2020/01/03 & 微信    & hj    & 10 RMB & 2020/01/03 & 微信 \\
-    F*5   & 10 RMB & 2020/01/03 & 微信    & S*m   & 20.20 RMB & 2020/01/03 & 微信 \\
-    二代青雉  & 13 RMB & 2020/01/14 & 支付宝   & *?    & 66 RMB & 2020/01/15 & 微信 \\
-    Mr. Xiong & 20 RMB & 2020/01/17 & 微信    & *博    & 15 RMB & 2020/01/18 & 微信 \\
-    * 者  & 10 RMB & 2020/02/02 & 微信    & Jackie  &  88.80 RMB  &  2020/02/09 & 微信 \\
-    Henry\_Sun、 & 50 RMB & 2020/02/14 & 支付宝 & * 桥  & 50 RMB & 2020/02/21 & 微信 \\
-    昀琏 & 10 RMB & 2020/03/02 & 支付宝 & S*y  &  10 RMB  &  2020/03/15 & 微信 \\
-    * 哥  & 66.66 RMB & 2020/03/17 & 微信    &   K*e & 30 RMB & 2020/03/30 & 微信\\
-    * 阳  &  20 RMB  &  2020/04/02 & 微信 & 士*n  & 30 RMB & 2020/04/11 & 微信 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:donation}%
-\end{table}%
-
-\section{常见问题 FAQ}
-
-\begin{enumerate}[label=\arabic*).]
-  \item \textit{如何删除版本信息？}\\
-    导言区不写 \lstinline|\version{x.xx}| 即可。
-  \item \textit{如何删除日期？}\\
-    与版本 \lstinline{\version} 不同的是，导言区不写或注释 \lstinline{\date} 的话，仍然会打印出当日日期，原因是 \lstinline{\date} 有默认参数。如果不需要日期的话，日期可以留空即可，也即 \lstinline|\date{}|。
-  \item \textit{如何获得中文日期？}\\
-    为了获得中文日期，必须在中文模式下，使用 \lstinline|\date{\zhdate{2019/12/09}}|，如果需要当天的汉化日期，可以使用 \lstinline|\date{\zhtoday}|，这两个命令都来源于 \href{https://ctan.org/pkg/zhnumber}{\lstinline{zhnumber}} 宏包。
-  \item \textit{如何添加多个作者？}\\
-    在 \lstinline{\author} 里面使用 \lstinline{\and}，作者单位可以用 \lstinline{\\} 换行。
-    \begin{lstlisting}
-      \author{author 1\\ org. 1 \and author 2 \\ org. 2 }
-    \end{lstlisting}
-\end{enumerate}
-
-\end{document}

### 2022-10-29 poster/poster-en.tex
update

%======================================================%
%   Poster LaTeX Template
%   compile using PDFLaTeX
%======================================================%

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage[UTF8,indent]{ctex}
%\usepackage{indentfirst}
\renewcommand{\indent}{\hspace*{2em}}

\bibliographystyle{plain}
\usepackage[orientation=portrait,size=a4,scale=2.3]{beamerposter} %1.68

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=1.5cm, text margin right=1.5cm}

\renewcommand{\baselinestretch}{1.15}

%\usetheme{LLT-poster}
%\usecolortheme{ComingClean}
%\footimage{\includegraphics[width=.35\textwidth]{authors}}

% Default font family: sans serif
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

%\setCJKfamilyfont{kai}[AutoFakeBold]{simkai.ttf}
%\newcommand*{\kai}{\CJKfamily{kai}}
%\setCJKfamilyfont{song}[AutoFakeBold]{SimSun}
%\newcommand*{\song}{\CJKfamily{song}}
%
%\newcommand*{\xinwei}{\CJKfamily{STXinwei}}

\makeatletter
\setbeamertemplate{frametitle}{%
  \nointerlineskip%
  \vskip0.4cm%
  \begin{beamercolorbox}[wd=\paperwidth,leftskip=.3cm,rightskip=.3cm plus1fil,vmode]{frametitle}%
  \hspace*{4pt} \includegraphics[height=1.5cm]{\logopic} %Logo.png}
  \begin{center}
    \usebeamerfont{frametitle}
	\insertframetitle
  \end{center}
  \end{beamercolorbox}%
  %\vskip-6pt
  \begin{beamercolorbox}[wd=\paperwidth,leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}
    \parbox[t]{15cm}{\centering \inserttitle}
  \end{beamercolorbox}%
  \vskip6pt
  \begin{beamercolorbox}[wd=\paperwidth,leftskip=.3cm,rightskip=.3cm plus1fil,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertauthor
  \end{beamercolorbox}%
  \vskip-8pt
  \begin{beamercolorbox}[wd=\paperwidth,leftskip=.3cm,rightskip=.3cm plus1fil,center]{author in head/foot}%
    \usebeamerfont{institute in head/foot}\insertinstitute
  \end{beamercolorbox}%
  \begin{beamercolorbox}[colsep=1.5pt,wd=14cm,leftskip=.3cm,rightskip=.3cm]{lower separation line head}
  \end{beamercolorbox}
}
\makeatother

\newlength\columnheight \columnheight=5cm % needed to define \columnheight,
                                          % don't have it here
\def\postercolumn{
    \leavevmode
    \vtop to \columnheight\bgroup
    \hsize.5\textwidth
    \noindent
    \ignorespaces
}

\def\endpostercolumn{
    \egroup
}

\setbeamerfont{frametitle}{family=\rmfamily,size=\LARGE,series=\bfseries}
\setbeamerfont{title in head/foot}{family=\rmfamily,size=\Large}
\setbeamerfont{author in head/foot}{family=\rmfamily,size=\large,series=\bfseries}
\setbeamerfont{institute in head/foot}{family=\rmfamily,size=\large,series=\bfseries}

\setbeamercolor{frametitle}{fg=black}
\setbeamercolor{author in head/foot}{fg=black}

% set block font
\setbeamerfont{block title}{family=\rmfamily,series=\bfseries}
\setbeamerfont{block body}{family=\rmfamily}
\setbeamercolor{block title}{fg=black}
%\setbeamercolor{block body}{size=black}

\setbeamerfont{normal text}{family=\rmfamily}
\AtBeginDocument{\usebeamerfont{normal text}}

\def\logopic{UnivLogo.png}   %logo
\title{This is a LaTeX template of poster}
\author{Professor ~ John Smith}
\institute{Department of Mathematics}

\begin{document}

% only change the spacing of body text
%\setlength{\baselineskip}{16pt}

\begin{frame}
\frametitle{Academic Poster}

\vskip-5em

\begin{columns}[t] %c

\column{0.75\textwidth}

\begin{block}{About the Speaker}
\indent This is a brief introduction to the author. This is a brief introduction to the author.
This is a brief introduction to the author. This is a brief introduction to the author.
This is a brief introduction to the author. This is a brief introduction to the author.
This is a brief introduction to the author.

\end{block}

\column{0.1\textwidth}
\vspace{4ex}
\begin{center}
\hspace{-6ex}\includegraphics[width=1.5\textwidth]{author.jpg}
\end{center}

\end{columns}

%\begin{postercolumn}
%   hello world hello world hello world hello world
%   hello world hello world hello world hello world
%\end{postercolumn}

\vskip1em

\begin{block}{Abstract}
\indent This is abstract. This is abstract. This is abstract. This is abstract. This is abstract. This is abstract. This is abstract. This is abstract. This is abstract. This is abstract. This is abstract. This is abstract.
\end{block}

\vskip1em

{\textbf{\large Date}:} October 28, 2022 (Friday)  \\[5pt]

{\textbf{\large Time}:} 9:00--10:00  \\[5pt]

{\textbf{\large Venue}:} Room 001, Building 3  \\[5pt]

{\textbf{\large Tencent Meeting}:} 111-222-333 \\[5pt]

\vskip1em

\begin{center}
\LARGE\bfseries Welcome!
\end{center}

\vskip2em

\begin{flushright}
Department of Mathematics \\
XX University  \\
October 26, 2022
\end{flushright}

\vskip-2em

\end{frame}

\end{document}

### 2022-10-29 note-temp/compile-pdflatex-en.sh

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+#-> Get source filename
+find . -name "*en.tex"|while read FileName;
+do 
+#--- Process FileName.tex ---
+echo "$FileName"
+echo "${FileName%.tex}"
+#-> Compile the main file
+pdflatex --synctex=-1 "$FileName"
+bibtex "${FileName%.tex}"
+pdflatex --synctex=-1 "$FileName"
+pdflatex --synctex=-1 "$FileName"
+#clear aux files
+rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
+done
+

### 2022-10-29 note-temp/compile-xelatex-cn.sh

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+#-> Get source filename
+find . -name "*cn.tex"|while read FileName;
+do 
+#--- Process FileName.tex ---
+echo "$FileName"
+echo "${FileName%.tex}"
+#-> Compile the main file
+xelatex --synctex=-1 "$FileName"
+bibtex "${FileName%.tex}"
+xelatex --synctex=-1 "$FileName"
+xelatex --synctex=-1 "$FileName"
+#clear aux files
+rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
+done
+

### 2022-10-29 note-temp/makefiles.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+#-> Compile the main file
+xelatex --synctex=-1 main.tex
+bibtex main
+xelatex --synctex=-1 main.tex
+xelatex --synctex=-1 main.tex
+#clear aux files
+rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
+done
+

### 2023-01-23 paper-cn/makefiles.sh
update

@@ -8,6 +8,8 @@ echo "$FileName"
 echo "${FileName%.tex}"
 #-> Compile the main file
 xelatex --synctex=-1 "$FileName"
+bibtex "${FileName%.tex}"
+xelatex --synctex=-1 "$FileName"
 xelatex --synctex=-1 "$FileName"
 #clear aux files
 rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 

### 2023-02-08 cover-letter/cover_letter3.tex
update

% LaTeX Cover Letter Template

\documentclass{article}

\usepackage{charter} % Use the Charter font

\usepackage[
	a4paper,    % Paper size
	top=1in,    % Top margin
	bottom=1in, % Bottom margin
	left=1in,   % Left margin
	right=1in,  % Right margin
	%showframe  % Uncomment to show frames around the margins for debugging purposes
]{geometry}

\setlength{\parindent}{0pt}     % Paragraph indentation
\setlength{\parskip}{1em}       % Vertical space between paragraphs

\usepackage{graphicx}       % Required for including images

\usepackage{fancyhdr}       % Required for customizing headers and footers

\fancypagestyle{firstpage}{%
	\fancyhf{} % Clear default headers/footers
	\renewcommand{\headrulewidth}{0pt} % No header rule
	\renewcommand{\footrulewidth}{1pt} % Footer rule thickness
}

\fancypagestyle{subsequentpages}{%
	\fancyhf{} % Clear default headers/footers
	\renewcommand{\headrulewidth}{1pt} % Header rule thickness
	\renewcommand{\footrulewidth}{1pt} % Footer rule thickness
}

\AtBeginDocument{\thispagestyle{firstpage}} % Use the first page headers/footers style on the first page
\pagestyle{subsequentpages} % Use the subsequent pages headers/footers style on subsequent pages

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	First page header
%----------------------------------------------------------------------------------------

\includegraphics[width=0.5\textwidth]{UnivLogo.png} % Logo

\vspace{-1em} % Pull the rule closer to the logo

\rule{\linewidth}{1pt} % Horizontal rule

\bigskip\bigskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	YOUR NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\hfill
\begin{tabular}{l @{}}
	\today \bigskip\\ % Date
	XXX \\
	Address 1 \\ % Address
	Address 2 \\
	Phone: +86 123-4567 \\
	Email: xxx@univ.edu.cn
\end{tabular}

\bigskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	ADDRESSEE AND GREETING
%----------------------------------------------------------------------------------------

\begin{tabular}{@{} l}
	Mr.\ XXX \\
	Recruitment Officer \\
	The Corporation \\
	123 Pleasant Lane \\
	City, State 12345
\end{tabular}

\bigskip % Vertical whitespace

Dear Mrs.\ XXX,

\bigskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

PARAGRAPH ONE: State the reason for the letter, name the position or type of work you are applying for and identify the source from which you learned of the opening (i.e. career development center, newspaper, employment service, personal contact).

PARAGRAPH TWO: Indicate why you are interested in the position, the company, its products, services - above all, stress what you can do for the employer. If you are a recent graduate, explain how your academic background makes you a qualified candidate for the position. If you have practical work experience, point out specific achievements or unique qualifications. Try not to repeat the same information the reader will find in the resume. Refer the reader to the enclosed resume or application which summarizes your qualifications, training, and experiences. The purpose of this section is to strengthen your resume by providing details which bring your experiences to life.

PARAGRAPH THREE: Request a personal interview and indicate your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example, state that you will be in the city where the company is located on a certain date and would like to set up an interview. Alternatively, state that you will call on a certain date to set up an interview. End the letter by thanking the employer for taking time to consider your credentials.

\bigskip %

Sincerely yours,

\includegraphics[height=1.5cm]{signature}

%\vspace{25pt} %

Andy

\end{document}

### 2023-02-13 amsart-en/amsart-temp.tex
update

% paper template

\documentclass[10pt,reqno,final]{amsart}
%\documentclass[10pt,reqno,draft]{amsart}

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{url,hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm}
\usepackage{algpseudocode}
% package for using box and verbatim
\usepackage{fancybox}

% allow page breaks between multiline formulas
\allowdisplaybreaks

% layout setting
\setlength{\textwidth}{15cm}
\setlength{\textheight}{21.6cm}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}

% command for line spacing
%\renewcommand{\baselinestretch}{1.1}

% command for mark footnotes
%\usepackage[symbol]{footmisc}
%\renewcommand{\thefootnote}{\fnsymbol{footnote}}

% command for equations, theorems and lemmas etc.
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}
\newtheorem{xca}{Exercise}[section]

\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

% caption setting
%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
\captionsetup[table]{position=top,skip={2pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

% number of equation, figure and table
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}

% new command
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\dx}[1][x]{\,{\rm d}#1}
\newcommand{\ddx}[1][x]{\dfrac{\rm d}{{\rm d}#1}}
\newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
\newcommand{\red}[1]{\textcolor{red}{#1}}

% Information for title and author
\title[Short Title]{This is Full Title}

\author[Author A \; \& \; Author B]{Author A${\,}^{1}$ \quad and \quad Author B${\,}^{2,*}$}

\thanks{${}^{*}$ Corresponding author (E-mail: \texttt{xyz@math.univ.edu}). \\
\indent ${}^{1}$ Department of Computer Science, \LaTeX\ University. \\
\indent ${}^{2}$ Department of Mechanical Engineering, \LaTeX\ University \\
\indent This work is supported in part by NSFC grants No. 12345678 and ...
}

\date{\today}

\subjclass[2000]{65L60, 65L05, 65L70}

\keywords{Keyword 1, keyword 2, error analysis}

\begin{document}

\begin{abstract}
  This is an example \LaTeX\ article. This can be used as a
  template for new articles.  Abstracts must be able to stand alone
  and so cannot contain citations to the paper's references,
  equations, etc.  An abstract must consist of a single paragraph and
  be concise. Because of online formatting, abstracts must appear as
  plain as possible. Any equations should be inline.
\end{abstract}

\maketitle

\section{Introduction}
The introduction introduces the context and summarizes the
manuscript. It is importantly to clearly state the contributions of
this piece of work.

In this paper we present a new method for solving the model equation
\begin{equation}\label{eq:mulequ}
\left\{\begin{aligned}
  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{ in } ~\Omega\times\mathcal{T}, \\
  &\, u(x,y,t) = g(t), \quad \text{ on } ~ \partial \Omega, \\
  &\, u(x,y,0)=\varphi(x, y), \quad \text{ on } ~\Omega.
\end{aligned}\right.
\end{equation}
where $\varepsilon$ is a small parameter.

This is an example of quoting an equation \eqref{eq:mulequ}.

The merits of our method are as follows:
\begin{itemize}
  \item item one
  \item item two
  \item item three
\end{itemize}
\begin{enumerate}
  \item item one
  \item item two
  \item item three
\end{enumerate}

The outline is not required, but we show an example here.

The paper is organized as follows. Our main results are in
\ref{sec:main}, our new algorithm is in \ref{sec:alg}, experimental
results are in \ref{sec:experiments}, discussion is in \ref{sec:discussion} and the conclusions follow in
\ref{sec:conclusions}.

\section{Main results}
\label{sec:main}

%\subsection{Subsection name}

We interleave text filler with some example theorems and theorem-like
items.

\begin{definition}
This is a definition environment.
\end{definition}

\begin{lemma}
This is a lemma environment.
\end{lemma}

\begin{theorem}
This is a theorem environment.
\end{theorem}
\begin{proof}
  This is a proof environment.
\end{proof}

\begin{lemma}
This is a lemma environment
\begin{enumerate}[label=\rm (\roman*)]
  \item item A
  \item item B
  \begin{equation}\label{eq:limite}
    \lim_{n\to\infty}\left(1+\frac{1}{n}\right)^n=e.
  \end{equation}
\end{enumerate}
\end{lemma}

This is a citation example \cite{WoZhMeSh2005}.

Here we state our main result as \ref{thm:bigthm}.

\begin{theorem}[$LDL^T$ Factorization \cite{GoVa2013}]\label{thm:bigthm}
  If $A \in \mathbb{R}^{n \times n}$ is symmetric and the principal
  submatrix $A(1:k,1:k)$ is nonsingular for $k=1:n-1$, then there
  exists a unit lower triangular matrix $L$ and a diagonal matrix
  \begin{equation*}
    D = \operatorname{diag}(d_1,\dots,d_n),  %\diag(d_1,\dots,d_n)
  \end{equation*}
  such that $A=LDL^T$. The factorization is unique.
\end{theorem}

LaTeX is a high-quality typesetting system; it includes features designed
for the production of technical and scientific documentation.
LaTeX is the de facto standard for the communication and publication of scientific documents.
LaTeX is based on the idea that it is better to leave document design to
document designers, and to let authors get on with writing documents.

\begin{theorem}[Mean Value Theorem]\label{thm:mvt}
  Suppose $f$ is a function that is continuous on the closed interval
  $[a,b]$.  and differentiable on the open interval $(a,b)$.
  Then there exists a number $c$ such that $a < c < b$ and
  \begin{equation*}
    f'(c) = \frac{f(b)-f(a)}{b-a}.
  \end{equation*}
  In other words,
  \begin{equation*}
    f(b)-f(a) = f'(c)(b-a).
  \end{equation*}
\end{theorem}

\begin{remark}
Observe that \ref{thm:bigthm}, \ref{thm:mvt} correctly mix references
to multiple labels.
\end{remark}

% command cref package cleveref
%Observe that \cref{thm:bigthm,thm:mvt,cor:a} correctly mix references
%to multiple labels.

\begin{corollary}\label{cor:a}
  Let $f(x)$ be continuous and differentiable everywhere. If $f(x)$
  has at least two roots, then $f'(x)$ must have at least one root.
\end{corollary}
\begin{proof}
  Let $a$ and $b$ be two distinct roots of $f$.
  By \ref{thm:mvt}, there exists a number $c$ such that
  \begin{equation*}
    f'(c) = \frac{f(b)-f(a)}{b-a} = \frac{0-0}{b-a} = 0.
  \end{equation*}
\end{proof}

Note that it may require two \LaTeX\ compilations for the proof marks
to show.

Display matrices can be rendered using environments from \texttt{amsmath}:
\begin{equation}\label{eq:matrices}
S=\begin{bmatrix}1&0\\0&0\end{bmatrix}
\quad\text{and}\quad
C=\begin{pmatrix}1&1&0\\1&1&0\\0&0&0\end{pmatrix}.
\end{equation}
Equation \ref{eq:matrices} shows some example matrices.

We calculate the Fr\'{e}chet derivative of $F$ as follows:
\begin{subequations}
\begin{align}
  F'(U,V)(H,K)
  &= \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T} -
  P(H\Sigma V^{T} + U\Sigma K^{T})\rangle \label{eq:aa} \\
  &= \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T}\rangle
  \nonumber \\
  &= \langle R(U,V)V\Sigma^{T},H\rangle +
  \langle \Sigma^{T}U^{T}R(U,V),K^{T}\rangle. \label{eq:bb}
\end{align}
\end{subequations}
\ref{eq:aa} is the first line, and \ref{eq:bb} is the last line.

\clearpage
\section{Algorithm}
\label{sec:alg}

Our analysis leads to the algorithm in \ref{alg:buildtree}.

\begin{algorithm}
\caption{Build tree}
\label{alg:buildtree}
\begin{algorithmic}
  \State {Define $P:=T:=\{ \{1\},\ldots,\{d\}$\}}
  \While{$\#P > 1$}
  \State {Choose $C^\prime\in\mathcal{C}_p(P)$ with $C^\prime := \operatorname{argmin}_{C\in\mathcal{C}_p(P)} \varrho(C)$}
  \State {Find an optimal partition tree $T_{C^\prime}$ }
  \State {Update $P := (P{\setminus} C^\prime) \cup \{ \bigcup_{t\in C^\prime} t \}$}
  \State {Update $T := T \cup \{ \bigcup_{t\in\tau} t : \tau\in T_{C^\prime}{\setminus} \mathcal{L}(T_{C^\prime})\}$}
  \EndWhile
  \Return $T$
\end{algorithmic}
\end{algorithm}

Reduce the width of the algorithm environment
\begin{center}
\vspace{-2ex}
\begin{minipage}{0.9\linewidth}
\begin{algorithm}[H]
\caption{Euclid’s algorithm}
\label{euclid}
\begin{algorithmic} % The number tells where the line numbering should start
    \Procedure{Euclid}{$a,b$} \Comment{The g.c.d. of a and b}
        \State $r\gets a \bmod b$
        \While{$r\not=0$} \Comment{We have the answer if r is 0}
            \State $a \gets b$
            \State $b \gets r$
            \State $r \gets a \bmod b$
        \EndWhile\label{euclidendwhile}
            \State \textbf{return} $b$\Comment{The gcd is b}
    \EndProcedure
\end{algorithmic}
\end{algorithm}
\end{minipage}
\end{center}

\section{Experimental results}
\label{sec:experiments}

LaTeX is a high-quality typesetting system; it includes features designed
for the production of technical and scientific documentation.
LaTeX is the de facto standard for the communication and publication of scientific documents.
LaTeX is based on the idea that it is better to leave document design to
document designers, and to let authors get on with writing documents.

\begin{example}
  This is example environment.
\end{example}

Figure \ref{fig:a} shows some example results.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.48\linewidth]{fig1}
  \caption{Example figure using external image files.}
  \label{fig:a}
\end{figure}

\clearpage
The two figures are placed side by side, sharing the same title.
\begin{figure}[htp!]
  \centering
  \includegraphics[width=0.45\linewidth]{fig1}
  \hfill
  \includegraphics[width=0.45\linewidth]{fig2}
  \caption{Left: Caption 1, Right: Caption 2.}
  \label{fig:b}
\end{figure}

Use \texttt{minipage} package to set up images side-by-side, each with its own title.
\begin{figure}[htp!]
\begin{minipage}[t]{0.48\linewidth}
  \centering
  \includegraphics[width=0.96\linewidth]{fig1}
  \caption{Caption A}
  \label{fig:image1}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
\centering
   \includegraphics[width=0.95\linewidth]{fig2}
   \caption{Caption B}
   \label{fig:image2}
\end{minipage}
\end{figure}

Additional results are available in the supplement in Table \ref{tab:foo}.

\begin{table}[!htp]
\centering
\renewcommand\arraystretch{1.2} % line spacing
\caption{Numerical error}
\label{tab:foo}
\begin{tabular}{c|c|cc|cc|cc}
\hline
degree &  step-size~$h$  & $L^2$-errors  &  order  & $H^1$-errors & order & $L^\infty$-errors  &  order \\
\hline
   &  1/128    & 9.18E-06    &2.02    & 7.70E-03  &1.01       & 6.46E-07    &2.02   \\
1  &  1/256    & 2.29E-06    &2.01    & 1.92E-03  &1.00       & 1.61E-07    &2.01   \\
   &  1/512    & 5.70E-07    &2.00    & 9.56E-04  &1.00       & 4.01E-08    &2.00   \\
\hline  % \cline{1-8}
   &  1/128    & 1.39E-08    &3.01    & 1.15E-05  &2.01       & 3.48E-12   &4.02    \\
2  &  1/256    & 1.73E-09    &3.01    & 2.88E-06  &2.01       & 3.27E-13   &3.94    \\
   &  1/512    & 2.17E-10    &3.00    & 7.24E-06  &2.00       & 6.66E-13   &1.55    \\
\hline  % \cline{1-8}
   &  1/32     & 2.28E-09    &4.05    & 6.92E-07  &3.04       & 1.45E-15   &8.21    \\
3  &  1/64     & 1.42E-10    &4.03    & 8.65E-08  &3.02       & 2.06E-14   &3.85    \\
   &  1/128    & 8.91E-12    &4.01    & 1.08E-08  &3.01       & 3.86E-14   &0.91    \\
\hline
\end{tabular}
\end{table}

\clearpage
Use the \texttt{tabularx} environment to generate tables.
\begin{table}[htp!]
\centering
\newcolumntype{L}{X}
\newcolumntype{C}{>{\centering \arraybackslash}X}
\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
\renewcommand\arraystretch{1.2}
\caption{Table description}
\label{tab:error}
\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
\Xhline{2\arrayrulewidth}
N  & A       & B    & C       & D      & E     \\
\Xhline{2\arrayrulewidth}
2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
\Xhline{2\arrayrulewidth}
\end{tabularx}
\end{table}

\section{Discussion of \texorpdfstring{{\boldmath$Z=X \cup Y$}}{Z = X union Y}}
\label{sec:discussion}

Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.

\section{Conclusions}
\label{sec:conclusions}

Some conclusions here.

\appendix
\section{An example appendix}

The contents of the appendix are here.

\begin{lemma}
Test Lemma.
\end{lemma}

This is a equation in appendix.
\begin{equation}\label{eq:A1}
  a^2+b^2=c^2.
\end{equation}

\section*{Acknowledgments}
We would like to acknowledge the assistance of volunteers in putting
together this example manuscript and supplement.

% References
\bibliographystyle{plain}
%\bibliographystyle{abbrv}

\bibliography{reference}

\end{document}

### 2023-02-13 article-en/article-temp.tex
update

--- 2023-02-13 amsart-en/amsart-temp.tex
@@
 
-\documentclass[10pt,reqno,final]{amsart}
-%\documentclass[10pt,reqno,draft]{amsart}
+\documentclass[10pt,reqno,final]{article}
+%\documentclass[10pt,reqno,draft]{article}
 
@@
 \newtheorem{corollary}{Corollary}[section]
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{corollary}[theorem]{Corollary}
 
@@
 % Information for title and author
-\title[Short Title]{This is Full Title}
+\title{An Example Article\thanks{The work is supported in part by NSF Grant No. 12345678 and ...}}
 
-\author[Author A \; \& \; Author B]{Author A${\,}^{1}$ \quad and \quad Author B${\,}^{2,*}$}
+%\author{Author A, Author B, and J. E. Smith\thanks{Corresponding author (\textit{E-mail address:} \texttt{xyz@math.univ.edu}).} }
 
-\thanks{${}^{*}$ Corresponding author (E-mail: \texttt{xyz@math.univ.edu}). \\
-\indent ${}^{1}$ Department of Computer Science, \LaTeX\ University. \\
-\indent ${}^{2}$ Department of Mechanical Engineering, \LaTeX\ University \\
-\indent This work is supported in part by NSFC grants No. 12345678 and ...
+\author{
+  Author A\thanks{Department of Computer Science, \LaTeX\ University.}
+  \and
+  Author B\thanks{Department of Mathematics, \LaTeX\ University.}
+  %\thanks{Email address: \texttt{xyz@math.univ.edu}}
+  \and
+  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
 }
@@
 
-\subjclass[2000]{65L60, 65L05, 65L70}
+\begin{document}
 
-\keywords{Keyword 1, keyword 2, error analysis}
-
-\begin{document}
+\maketitle
 
@@
   plain as possible. Any equations should be inline.
+
+  \medskip
+  \noindent{\bf Keywords}: Example, \LaTeX, numerical methods
+
+  \medskip
+  \noindent{\bf 2000 Mathematics Subject Classification: } 65L60, 65L05, 65L70.
 \end{abstract}
-
-\maketitle
 
@@
   \item item two
-  \item item three
 \end{itemize}
@@
   \item item two
-  \item item three
 \end{enumerate}
@@
 
-\clearpage
 \section{Algorithm}
@@
 
+\clearpage
 Figure \ref{fig:a} shows some example results.
@@
 
-\clearpage
 The two figures are placed side by side, sharing the same title.
@@
 
-\clearpage
 Use the \texttt{tabularx} environment to generate tables.
+
 \begin{table}[htp!]
@@
 
-% References
 \bibliographystyle{plain}

### 2023-02-13 book-en/book-cover-en.tex
Update
update

@@
 \usepackage{geometry}
-\geometry{left=2.5cm,right=2.5cm,top=1.7cm,bottom=1.8cm,includehead,includefoot}
+\geometry{left=2.5cm,right=2.5cm,top=3.0cm,bottom=3.0cm}
 %\geometry{left=1in,right=1in,top=1in,bottom=1in}
@@
 \usepackage{booktabs}
+\usepackage{enumitem}
 \usepackage{multirow}
@@
 \usepackage{makecell}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{xstring}
@@
 %\usepackage{indentfirst}
-\usepackage[perpage,symbol]{footmisc}   % footnote control
+\usepackage[perpage,symbol]{footmisc}   % footnote setting
 
-%\usepackage{appendix}
+% caption setting
+\usepackage{caption}
+%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
+\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
+\captionsetup[table]{position=top,skip={2pt},name={Table}}
+%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
+%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
+%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
+%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
+%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}
 
@@
 %---- header and footer position -----
-\addtolength{\headsep}{-0.1cm}
-\addtolength{\footskip}{-0.1cm}
+%\setlength{\headheight}{18pt}
+%\setlength{\headsep}{18pt}
+%\setlength{\footskip}{28pt}
+
 %---- Contents Setting -----
@@
 \setcounter{secnumdepth}{3}
-
-%\newcommand{\makeheadrule}{%
-%    \makebox[-3pt][l]{\rule[.7\baselineskip]{\headwidth}{0.4pt}}
-%    \rule[0.85\baselineskip]{\headwidth}{1.5pt}\vskip-.8\baselineskip}
-%
-%\makeatletter
-%\renewcommand{\headrule}{%
-%    {\if@fancyplain\let\headrulewidth\plainheadrulewidth\fi
-%     \makeheadrule}}
-%\pagestyle{fancyplain}
 
@@
 \pagestyle{fancy}
-\renewcommand{\chaptermark}[1]{\markboth{\thechapter ~ #1}{}}
-\renewcommand{\sectionmark}[1]{\markright{\thesection ~ #1}{}}
+%\renewcommand{\chaptermark}[1]{\markboth{\thechapter ~ #1}{}}
+%\renewcommand{\sectionmark}[1]{\markright{\thesection ~ #1}{}}
 \fancyhf{}  % remove the original style
 \fancyhead[RO,LE]{~\thepage~}
-\fancyhead[LO]{\rmfamily \rightmark}
-\fancyhead[RE]{\rmfamily \leftmark}
+\fancyhead[LO]{\rmfamily \nouppercase{\rightmark}}
+\fancyhead[RE]{\rmfamily \nouppercase{\leftmark}}
 
 %\setlength{\parskip}{3pt plus1pt minus1pt}
+
+\usepackage{tocloft,calc}
+\renewcommand{\cftchappresnum}{\chaptername\space}
+\renewcommand{\cftchapaftersnumb}{\hspace{-12pt}}
+\setlength{\cftchapnumwidth}{\widthof{\textbf{Appendix~999~}}}
+\makeatletter
+\g@addto@macro\appendix{%
+  \addtocontents{toc}{%
+    \protect\renewcommand{\protect\cftchappresnum}{\appendixname\space}%
+    \protect\renewcommand{\protect\cftchapaftersnumb}{\hspace{0pt}}
+  }%
+  \renewcommand{\chaptermark}[1]{\markboth{\appendixname~\thechapter. ~ #1}{}}
+}
 
@@
 %\renewcommand{\proofname}{Proof}
+
+% new command for tabularx
+\newcolumntype{L}{X}
+\newcolumntype{C}{>{\centering \arraybackslash}X}
+\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
+\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
 
@@
 \title{THE BOOK \\[8pt] \LaTeX ~TEMPLATES}
-\author{John Smith}
+\author{Edited by Andy}
 \date{\today}
@@
 
-	2021 % Publication year
+	202X % Publication year
 
@@
 
+The unnumbered list
+\begin{itemize}
+  \item item one
+  \item item two
+  \item item three
+\end{itemize}
+
+The numbered list
+\begin{enumerate}
+  \item item one
+  \item item two
+  \item item three
+\end{enumerate}
+
 \subsection{A sub section}
@@
 
-LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
-$ \Rightarrow $
+LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
+
+The \texttt{gather} environment
 \begin{align}
@@
 
-Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.
+Use command \verb|\notag| or \verb|\nonumber| to remove number of equation.
+\begin{align}
+a ={} & b + c \\
+={} & d + e + f + g + h + i + j \notag \\
+& + m + n + o \\
+={} & p + q + r + s.
+\end{align}
+
+The \texttt{gather} environment
+\begin{gather}
+a = b + c \\
+d = e + f + g \notag \\
+h + i = j \\
+l + m = n
+\end{gather}
 
@@
 This statement requires citation \cite{Adams2003} and \cite{Shen1994,Tadmor2012,TreWei2014}
+
+we present a new method for solving the model equation
+\begin{equation}\label{eq:mulequ}
+\left\{\begin{aligned}
+  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{ in } ~\Omega\times\mathcal{T}, \\
+  &\, u(x,y,t) = g(t), \quad \text{ on } ~ \partial \Omega, \\
+  &\, u(x,y,0)=\varphi(x, y), \quad \text{ on } ~\Omega.
+\end{aligned}\right.
+\end{equation}
+where $\varepsilon$ is a small parameter.
 
@@
 The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
 
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
 The quick brown fox jumps over the lazy dog.
@@
 
+\begin{lemma}
+This is a lemma environment
+\begin{enumerate}[label=\rm (\roman*)]
+  \item item A
+  \item item B
+  \begin{equation}\label{eq:limite}
+    \lim_{n\to\infty}\left(1+\frac{1}{n}\right)^n=e.
+  \end{equation}
+\end{enumerate}
+\end{lemma}
+
 \begin{theorem}[Mass--energy]
@@
 \end{proof}
+
+\begin{remark}
+  This is a remark environment.
+\end{remark}
+
+\begin{example}
+  This is example environment.
+\end{example}
 
@@
 
-\subsection{A sub section}
-LaTeX is not a word processor!
-Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content.
-For example consider this document:
+Here we state our main result as \ref{thm:bigthm}.
 
-LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
-$ \Rightarrow $
+\begin{theorem}[$LDL^T$ Factorization \cite{Adams2003}]\label{thm:bigthm}
+  If $A \in \mathbb{R}^{n \times n}$ is symmetric and the principal
+  submatrix $A(1:k,1:k)$ is nonsingular for $k=1:n-1$, then there
+  exists a unit lower triangular matrix $L$ and a diagonal matrix
+  \begin{equation*}
+    D = \operatorname{diag}(d_1,\dots,d_n),  %\diag(d_1,\dots,d_n)
+  \end{equation*}
+  such that $A=LDL^T$. The factorization is unique.
+\end{theorem}
 
-Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.
+LaTeX is a high-quality typesetting system; it includes features designed
+for the production of technical and scientific documentation.
+LaTeX is the de facto standard for the communication and publication of scientific documents.
+LaTeX is based on the idea that it is better to leave document design to
+document designers, and to let authors get on with writing documents.
+
+\begin{theorem}[Mean Value Theorem]\label{thm:mvt}
+  Suppose $f$ is a function that is continuous on the closed interval
+  $[a,b]$.  and differentiable on the open interval $(a,b)$.
+  Then there exists a number $c$ such that $a < c < b$ and
+  \begin{equation*}
+    f'(c) = \frac{f(b)-f(a)}{b-a}.
+  \end{equation*}
+  In other words,
+  \begin{equation*}
+    f(b)-f(a) = f'(c)(b-a).
+  \end{equation*}
+\end{theorem}
+
+\begin{remark}
+Observe that \ref{thm:bigthm}, \ref{thm:mvt} correctly mix references
+to multiple labels.
+\end{remark}
+
+% command cref package cleveref
+%Observe that \cref{thm:bigthm,thm:mvt,cor:a} correctly mix references
+%to multiple labels.
+
+\begin{corollary}\label{cor:a}
+  Let $f(x)$ be continuous and differentiable everywhere. If $f(x)$
+  has at least two roots, then $f'(x)$ must have at least one root.
+\end{corollary}
+\begin{proof}
+  Let $a$ and $b$ be two distinct roots of $f$.
+  By \ref{thm:mvt}, there exists a number $c$ such that
+  \begin{equation*}
+    f'(c) = \frac{f(b)-f(a)}{b-a} = \frac{0-0}{b-a} = 0.
+  \end{equation*}
+\end{proof}
+
+Note that it may require two \LaTeX\ compilations for the proof marks
+to show.
+
+Display matrices can be rendered using environments from \texttt{amsmath}:
+\begin{equation}\label{eq:matrices}
+S=\begin{bmatrix}1&0\\0&0\end{bmatrix}
+\quad\text{and}\quad
+C=\begin{pmatrix}1&1&0\\1&1&0\\0&0&0\end{pmatrix}.
+\end{equation}
+Equation \ref{eq:matrices} shows some example matrices.
+
+We calculate the Fr\'{e}chet derivative of $F$ as follows:
+\begin{subequations}
+\begin{align}
+  F'(U,V)(H,K)
+  &= \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T} -
+  P(H\Sigma V^{T} + U\Sigma K^{T})\rangle \label{eq:aa} \\
+  &= \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T}\rangle
+  \nonumber \\
+  &= \langle R(U,V)V\Sigma^{T},H\rangle +
+  \langle \Sigma^{T}U^{T}R(U,V),K^{T}\rangle. \label{eq:bb}
+\end{align}
+\end{subequations}
+\ref{eq:aa} is the first line, and \ref{eq:bb} is the last line.
+
+\section{Algorithm}
+\label{sec:alg}
+
+Our analysis leads to the algorithm in \ref{alg:buildtree}.
+
+\begin{algorithm}
+\caption{Build tree}
+\label{alg:buildtree}
+\begin{algorithmic}
+  \State {Define $P:=T:=\{ \{1\},\ldots,\{d\}$\}}
+  \While{$\#P > 1$}
+  \State {Choose $C^\prime\in\mathcal{C}_p(P)$ with $C^\prime := \operatorname{argmin}_{C\in\mathcal{C}_p(P)} \varrho(C)$}
+  \State {Find an optimal partition tree $T_{C^\prime}$ }
+  \State {Update $P := (P{\setminus} C^\prime) \cup \{ \bigcup_{t\in C^\prime} t \}$}
+  \State {Update $T := T \cup \{ \bigcup_{t\in\tau} t : \tau\in T_{C^\prime}{\setminus} \mathcal{L}(T_{C^\prime})\}$}
+  \EndWhile
+  \Return $T$
+\end{algorithmic}
+\end{algorithm}
+
+\clearpage
+Reduce the width of the algorithm environment
+\begin{center}
+\vspace{-2ex}
+\begin{minipage}{0.9\linewidth}
+\begin{algorithm}[H]
+\caption{Euclid’s algorithm}
+\label{euclid}
+\begin{algorithmic} % The number tells where the line numbering should start
+    \Procedure{Euclid}{$a,b$} \Comment{The g.c.d. of a and b}
+        \State $r\gets a \bmod b$
+        \While{$r\not=0$} \Comment{We have the answer if r is 0}
+            \State $a \gets b$
+            \State $b \gets r$
+            \State $r \gets a \bmod b$
+        \EndWhile\label{euclidendwhile}
+            \State \textbf{return} $b$\Comment{The gcd is b}
+    \EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\end{minipage}
+\end{center}
 
@@
 The quick brown fox jumps over the lazy dog.
-
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
 The quick brown fox jumps over the lazy dog.
@@
 
-\section{The first section}
-LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
+LaTeX is a high-quality typesetting system; it includes features designed
+for the production of technical and scientific documentation.
 LaTeX is the de facto standard for the communication and publication of scientific documents.
+LaTeX is based on the idea that it is better to leave document design to
+document designers, and to let authors get on with writing documents.
+
+\section{Table Environment}
+
+Additional results are available in the supplement in Table \ref{tab:foo}.
+
+\begin{table}[!htp]
+\centering
+\renewcommand\arraystretch{1.2} % line spacing
+\caption{Numerical error}
+\label{tab:foo}
+\begin{tabular}{c|c|cc|cc|cc}
+\hline
+degree &  step-size~$h$  & $L^2$-errors  &  order  & $H^1$-errors & order & $L^\infty$-errors  &  order \\
+\hline
+   &  1/128    & 9.18E-06    &2.02    & 7.70E-03  &1.01       & 6.46E-07    &2.02   \\
+1  &  1/256    & 2.29E-06    &2.01    & 1.92E-03  &1.00       & 1.61E-07    &2.01   \\
+   &  1/512    & 5.70E-07    &2.00    & 9.56E-04  &1.00       & 4.01E-08    &2.00   \\
+\hline  % \cline{1-8}
+   &  1/128    & 1.39E-08    &3.01    & 1.15E-05  &2.01       & 3.48E-12   &4.02    \\
+2  &  1/256    & 1.73E-09    &3.01    & 2.88E-06  &2.01       & 3.27E-13   &3.94    \\
+   &  1/512    & 2.17E-10    &3.00    & 7.24E-06  &2.00       & 6.66E-13   &1.55    \\
+\hline  % \cline{1-8}
+   &  1/32     & 2.28E-09    &4.05    & 6.92E-07  &3.04       & 1.45E-15   &8.21    \\
+3  &  1/64     & 1.42E-10    &4.03    & 8.65E-08  &3.02       & 2.06E-14   &3.85    \\
+   &  1/128    & 8.91E-12    &4.01    & 1.08E-08  &3.01       & 3.86E-14   &0.91    \\
+\hline
+\end{tabular}
+\end{table}
+
+\clearpage
+Use the \texttt{tabularx} environment to generate tables.
+
+\begin{table}[htp!]
+\centering
+\renewcommand\arraystretch{1.2}
+\caption{Table description}
+\label{tab:error}
+\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
+\Xhline{2\arrayrulewidth}
+N  & A       & B    & C       & D      & E     \\
+\Xhline{2\arrayrulewidth}
+2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
+4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
+6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
+8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
+10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
+12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
+\Xhline{2\arrayrulewidth}
+\end{tabularx}
+\end{table}
+
+LaTeX is a high-quality typesetting system; it includes features designed
+for the production of technical and scientific documentation.
+LaTeX is the de facto standard for the communication and publication of scientific documents.
+LaTeX is based on the idea that it is better to leave document design to
+document designers, and to let authors get on with writing documents.
+
+%LaTeX is a high-quality typesetting system; it includes features designed
+%for the production of technical and scientific documentation.
+%LaTeX is the de facto standard for the communication and publication of scientific documents.
+%LaTeX is based on the idea that it is better to leave document design to
+%document designers, and to let authors get on with writing documents.
+
+\section{Figure Environment}
+
+Figure \ref{fig:a} shows some example results.
+\begin{figure}[htp!]
+  \centering
+  \includegraphics[width=0.48\linewidth]{image1}
+  \caption{Example figure using external image files.}
+  \label{fig:a}
+\end{figure}
+
+\clearpage
+The two figures are placed side by side, sharing the same title.
+\begin{figure}[htp!]
+  \centering
+  \includegraphics[width=0.45\linewidth]{image1}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{image2}
+  \caption{Left: Caption 1, Right: Caption 2.}
+  \label{fig:b}
+\end{figure}
+
+Use \texttt{minipage} package to set up images side-by-side, each with its own title.
+\begin{figure}[htp!]
+\begin{minipage}[t]{0.48\linewidth}
+  \centering
+  \includegraphics[width=0.96\linewidth]{image1}
+  \caption{Caption A}
+  \label{fig:image1}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.48\linewidth}
+\centering
+   \includegraphics[width=0.95\linewidth]{image2}
+   \caption{Caption B}
+   \label{fig:image2}
+\end{minipage}
+\end{figure}
+
+\section{Discussion of \texorpdfstring{{\boldmath$Z=X \cup Y$}}{Z = X union Y}}
+\label{sec:discussion}
+
+Some discussions here. Some discussions here. Some discussions here.
 
@@
 For example consider this document:
-
-LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
-$ \Rightarrow $
-
-\begin{equation}\label{eqn:1}
-\left\{\begin{aligned}
-  &-\frac{\mathrm{d}^{2} u}{\mathrm{d} x^{2}}+\frac{\mathrm{d} u}{\mathrm{d} x}=\pi^{2} \sin (\pi x)+\pi \cos (\pi x),\quad x \in [0,1], \\
-  &u(0)=0,\quad u(1)=0.
-\end{aligned} \right.
-\end{equation}
-
-Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.
 
@@
 \subsection{A sub section}
-LaTeX is not a word processor!
-Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content.
-For example consider this document:
-
-LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
-$ \Rightarrow $
-
-Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.
+LaTeX is not a word processor! Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content.
 
@@
 \chapter{This is the first appendix}
+
+LaTeX is a high-quality typesetting system; it includes features designed
+for the production of technical and scientific documentation.
+LaTeX is the de facto standard for the communication and publication of scientific documents.
+LaTeX is based on the idea that it is better to leave document design to
+document designers, and to let authors get on with writing documents.
+
 \section{A sub section}
 
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
+\begin{equation}\label{eq:abc}
+  a^2+b^2=c^2.
+\end{equation}
 
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
-The quick brown fox jumps over the lazy dog.
+\begin{lemma}
+This is a lemma environment.
+\end{lemma}
+
+This is Figure \ref{fig:aa}.
+\begin{figure}[htp!]
+  \centering
+  \includegraphics[width=0.48\linewidth]{image1}
+  \caption{Example figure using external image files.}
+  \label{fig:aa}
+\end{figure}
+
+The following table: Table~\ref{tab2:heightweight}. Use \verb|autoref|: \autoref{tab2:heightweight}.
+\begin{table}[!htp]
+\centering
+\renewcommand\arraystretch{1.05}
+\caption{A sample of the height and weight of students.}
+\label{tab2:heightweight}
+% PLCR is defined in the preamble
+\begin{tabularx}{0.8\textwidth}{lCCC}
+   \toprule %\Xhline{2\arrayrulewidth}
+	Number &  Age & Height & Weight\\
+	\midrule
+	1&14&156&42\\
+	2&16&158&45\\
+	3&14&162&48\\
+	4&15&163&50\\
+    \cmidrule{2-4}
+	Mean &15&159.75&46.25\\
+	\bottomrule
+\end{tabularx}
+\end{table}
 

### 2023-02-13 book-en/book-en.tex
Update
update

@@
 
-%\usepackage{appendix}
+% caption setting
+\usepackage{caption}
+%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
+\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
+\captionsetup[table]{position=top,skip={2pt},name={Table}}
+%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
+%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
+%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
+%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
+%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}
 
@@
 \pagestyle{fancy}
-\renewcommand{\chaptermark}[1]{\markboth{\thechapter ~ #1}{}}
-\renewcommand{\sectionmark}[1]{\markright{\thesection ~ #1}{}}
+%\renewcommand{\chaptermark}[1]{\markboth{\thechapter ~ #1}{}}
+%\renewcommand{\sectionmark}[1]{\markright{\thesection ~ #1}{}}
 \fancyhf{}  % remove the original style
@@
 
+% new command for tabularx
+\newcolumntype{L}{X}
+\newcolumntype{C}{>{\centering \arraybackslash}X}
+\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
+\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
+
 % number of equation, figure and table
@@
 \title{\bfseries LaTeX Book Sample}
-\author{Edited by John Smith}
+\author{Edited by Andy}
 \date{\today}

### 2023-02-18 amsart-en/amsart-temp.tex
update

@@
 % package for algorithm
-\usepackage{algorithm}
+\usepackage{algorithm,algorithmicx}
 \usepackage{algpseudocode}
@@
 \usepackage{fancybox}
+
+% package for bibliography support
+\usepackage[numbers,sort&compress]{natbib}
 
@@
 \newcommand{\abs}[1]{\lvert#1\rvert}
-\newcommand{\dx}[1][x]{\,{\rm d}#1}
-\newcommand{\ddx}[1][x]{\dfrac{\rm d}{{\rm d}#1}}
+\newcommand{\dx}[1][x]{\,\mathrm{d}#1}
+\newcommand{\ddx}[1][x]{\dfrac{\mathrm{d}}{\mathrm{d}#1}}
 \newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
@@
 
-This is a citation example \cite{WoZhMeSh2005}.
+This is a citation example \cite{Adams2003}. This statement requires citation \cite{Shen1994,Tadmor2012,TreWei2014}.
 
@@
   \EndWhile
-  \Return $T$
+  \State \Return $T$
 \end{algorithmic}
@@
 
-Reduce the width of the algorithm environment
+Adjust the width of the algorithm environment
 \begin{center}
@@
 \caption{Euclid’s algorithm}
-\label{euclid}
-\begin{algorithmic} % The number tells where the line numbering should start
-    \Procedure{Euclid}{$a,b$} \Comment{The g.c.d. of a and b}
-        \State $r\gets a \bmod b$
-        \While{$r\not=0$} \Comment{We have the answer if r is 0}
+\label{alg:euclid}
+\begin{algorithmic}[1] % line numbering
+\Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
+  \State $r \gets a \bmod b$
+  \While{$r\not=0$}\Comment{We have the answer if r is 0}
     \State $a \gets b$
@@
 
-\section{Discussion of \texorpdfstring{{\boldmath$Z=X \cup Y$}}{Z = X union Y}}
+\section{Discussion of \texorpdfstring{{$Z=X \cup Y$}}{Z = X union Y}}
 \label{sec:discussion}

### 2023-02-18 amsart-en/amsart-temp2.tex
update

--- 2023-02-18 amsart-en/amsart-temp.tex
@@
 \usepackage{fancybox}
+\usepackage[foot]{amsaddr}
 
@@
 % command for line spacing
-%\renewcommand{\baselinestretch}{1.1}
+\renewcommand{\baselinestretch}{1.1}
 
@@
 %\usepackage[symbol]{footmisc}
-%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
 
@@
 
-\author[Author A \; \& \; Author B]{Author A${\,}^{1}$ \quad and \quad Author B${\,}^{2,*}$}
+\author{author A$^1$ and author B$^{1,*}$}
+\address{$^1$common address of authors A and B}
 
-\thanks{${}^{*}$ Corresponding author (E-mail: \texttt{xyz@math.univ.edu}). \\
-\indent ${}^{1}$ Department of Computer Science, \LaTeX\ University. \\
-\indent ${}^{2}$ Department of Mechanical Engineering, \LaTeX\ University \\
-\indent This work is supported in part by NSFC grants No. 12345678 and ...
-}
+\author{author C$^{2}$}
+\address{$^2$author C address}
+
+\email{list of emails}
+
+\thanks{${}^{*}$Corresponding author.}
+\thanks{The first author was supported in part by NSF Grant \#000000.}
+\thanks{Support information for the second author.}
+\thanks{Support information for the third author.}
+
+\subjclass[2000]{65L60, 65L05, 65L70}
 
 \date{\today}
-
-\subjclass[2000]{65L60, 65L05, 65L70}
 
@@
 for the production of technical and scientific documentation.
-LaTeX is the de facto standard for the communication and publication of scientific documents.
-LaTeX is based on the idea that it is better to leave document design to
-document designers, and to let authors get on with writing documents.
+%LaTeX is the de facto standard for the communication and publication of scientific documents.
+%LaTeX is based on the idea that it is better to leave document design to
+%document designers, and to let authors get on with writing documents.
 
@@
 
-\clearpage
 Use the \texttt{tabularx} environment to generate tables.

### 2023-02-18 article-en/article-temp2.tex
update

--- 2023-02-13 article-en/article-temp.tex
@@
 % package for algorithm
-\usepackage{algorithm}
+\usepackage{algorithm,algorithmicx}
 \usepackage{algpseudocode}
+% package for author and affiliation style
+\usepackage[affil-it]{authblk}
 % package for using box and verbatim
 \usepackage{fancybox}
+
+% package for bibliography support
+\usepackage[numbers,sort&compress]{natbib}
 
@@
 
-\author{
-  Author A\thanks{Department of Computer Science, \LaTeX\ University.}
-  \and
-  Author B\thanks{Department of Mathematics, \LaTeX\ University.}
-  %\thanks{Email address: \texttt{xyz@math.univ.edu}}
-  \and
-  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
-}
+\author{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
+\affil{Department of Computer Science, \LaTeX\ University.}
+
+\author{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
+\affil{Department of Mathematics, \LaTeX\ University.}
+
+\author{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
+\affil{Department of Mechanical Engineering, \LaTeX\ University}
 

### 2023-02-18 article-en/article-temp3.tex
update

--- 2023-02-13 article-en/article-temp.tex
@@
 
-\documentclass[10pt,reqno,final]{article}
+\documentclass[10pt,reqno,twoside,final]{article}
 %\documentclass[10pt,reqno,draft]{article}
@@
 % package for algorithm
-\usepackage{algorithm}
+\usepackage{algorithm,algorithmicx}
 \usepackage{algpseudocode}
+% package for author and affiliation style
+\usepackage[affil-it]{authblk}
 % package for using box and verbatim
 \usepackage{fancybox}
+% package for page headers and footers
+\usepackage{fancyhdr}
+
+% package for bibliography support
+\usepackage[numbers,sort&compress]{natbib}
 
@@
 \setlength{\evensidemargin}{0.5cm}
+
+% headers and footers setting
+\pagestyle{fancy}
+\fancyhf{}
+\fancyhead[CO]{\uppercase{Title of Paper}}
+\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
+\fancyfoot[C]{\thepage}
+\renewcommand{\headrulewidth}{0pt}
+
+%\fancyhead[C]{\uppercase{Title of Paper}}
+%\fancyfoot[C]{\thepage}
+%\renewcommand{\headrulewidth}{0pt}
+
+%\fancyhead[LE,RO]{$\cdot$\:\thepage\:$\cdot$}
+%\fancyhead[LO,RE]{\nouppercase{\leftmark}}
+%\renewcommand{\headrulewidth}{0.5pt}
+
+%\fancyhead[LE,RO]{$\cdot$\:\thepage\:$\cdot$}
+%\fancyhead[RE]{\nouppercase{\leftmark}}
+%\fancyhead[LO]{\nouppercase{\rightmark}}
+%\renewcommand{\headrulewidth}{0.5pt}
 
@@
 \theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
+\newtheorem{remark}[theorem]{Remark}
 
@@
 % Information for title and author
-\title{An Example Article\thanks{The work is supported in part by NSF Grant No. 12345678 and ...}}
+\title{An Example Article\thanks{The work is supported in part by NSF Grant No. 12345678 and ...} }
 
-%\author{Author A, Author B, and J. E. Smith\thanks{Corresponding author (\textit{E-mail address:} \texttt{xyz@math.univ.edu}).} }
+\author[1]{Author A}
+\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
+\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
+%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
+\affil[1]{Department of Computer Science, \LaTeX\ University}
+\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
 
-\author{
-  Author A\thanks{Department of Computer Science, \LaTeX\ University.}
-  \and
-  Author B\thanks{Department of Mathematics, \LaTeX\ University.}
-  %\thanks{Email address: \texttt{xyz@math.univ.edu}}
-  \and
-  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
-}
-
-\date{\today}
+\date{Date: \today}
 

### 2023-02-18 book-en/book-cover-en.tex
update

@@
 %----- Packages for template -----
-\usepackage{amsmath,amsthm,amssymb,amsfonts}
+\usepackage{amsmath,amsthm,amssymb}
 \usepackage{mathrsfs,bm}
@@
 %\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
-\usepackage{url,hyperref}
-\hypersetup{colorlinks=true,linkcolor=black,citecolor=black}
+
 \usepackage[english]{babel}
@@
 \usepackage{algorithm}
+\usepackage{algorithmicx}
 \usepackage{algpseudocode}
@@
 \usepackage{bookmark}
-\usepackage[numbers]{natbib}
+
+% package for bibliography support
+\usepackage[numbers,sort&compress]{natbib}
 
@@
 \usepackage[perpage,symbol]{footmisc}   % footnote setting
+
+\usepackage{url,hyperref}
+\hypersetup{
+  colorlinks = true,
+  linkcolor = black,
+  citecolor = blue,
+  filecolor = blue,
+  urlcolor =blue,
+}
 
@@
 
+\setlength{\headheight}{15pt}
 %\setlength{\parskip}{3pt plus1pt minus1pt}
@@
 
-%----- book information -----
+%----- Book information -----
 
@@
 
-The \texttt{gather} environment
+The \texttt{align} environment
 \begin{align}
@@
 Instead, LaTeX encourages authors not to worry too much about the appearance of their documents but to concentrate on getting the right content.
-For example consider this document:
+LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
+LaTeX is the de facto standard for the communication and publication of scientific documents.
 
-LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents. So, in LaTeX you would input this document as:
-$ \Rightarrow $
-
-Assuming that the disturbance errors of $f$ and $u_{N,0}$ are $\tilde{f}$ and $\tilde{u}_{N,0}$ respectively, the error of the numerical solution $u_N$ is $\tilde{u}_N$.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
 
@@
 
-\begin{theorem}[$LDL^T$ Factorization \cite{Adams2003}]\label{thm:bigthm}
+\begin{theorem}[$LDL^T$ Factorization \cite{GoVa2013}]\label{thm:bigthm}
   If $A \in \mathbb{R}^{n \times n}$ is symmetric and the principal
@@
 \clearpage
-Reduce the width of the algorithm environment
+Adjust the width of the algorithm environment
 \begin{center}
@@
 \bibliographystyle{plain}
-\bibliography{mybib}
+\bibliography{reference}
 
@@
 %\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces[M]. Elsevier, 2003.
+%
+%\bibitem{GoVa2013} Gene~H. Golub and Charles~F. Van~Loan. Matrix computations. The Johns Hopkins University Press, Baltimore, 4th edition, 2013.
 %

### 2023-02-18 book-en/book-en.tex
update

@@
 \usepackage[perpage,symbol]{footmisc}   % footnote setting
+
+\usepackage{url,hyperref}
+\hypersetup{
+  colorlinks = true,
+  linkcolor = black,
+  citecolor = black,
+  filecolor = blue,
+  urlcolor =blue,
+}
 

### 2023-03-24 book-en/book-cover-en.tex
update

@@
 \usepackage{float}
-\usepackage{bookmark}
+\usepackage[numbered]{bookmark}
+\usepackage{anyfontsize}
 
@@
 \usepackage[numbers,sort&compress]{natbib}
+%\def\bibfont{\small}      % bib font size
+%\setlength{\bibsep}{8pt}  % vertical space of bib
 
 %\usepackage{indentfirst}
-\usepackage[perpage,symbol]{footmisc}   % footnote setting
 
-\usepackage{url,hyperref}
+% footnote setting
+%\usepackage[perpage,symbol]{footmisc}
+
+% hyperlink setting
+\usepackage{hyperref}
 \hypersetup{
@@
   filecolor = blue,
-  urlcolor =blue,
+  urlcolor = blue,
 }
@@
 \newcommand{\RR}{\ensuremath{\mathbb{R}}}
-\newcommand{\A}{\mathcal{A}}
-\newcommand{\ii}{\bm{\mathrm{i}}\,}  % imaginary part
-\newcommand{\md}{\mathrm{d}\,}
-\newcommand{\bA}{\boldsymbol{A}}
+% new command
+\newcommand{\abs}[1]{\lvert#1\rvert}
+\newcommand{\norm}[1]{\lVert#1\rVert}
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
+\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
+\newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
 \newcommand{\red}[1]{\textcolor{red}{#1}}
@@
 
-\clearpage
-Use the \texttt{tabularx} environment to generate tables.
+Use the \texttt{tabularx} environment to generate \autoref{tab:error}.
 
@@
 LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
-\index{LaTeX} is the de facto standard for the communication and publication of scientific documents.
+LaTeX\index{LaTeX} is the de facto standard for the communication and publication of scientific documents.
 
@@
 The following table: Table~\ref{tab2:heightweight}. Use \verb|autoref|: \autoref{tab2:heightweight}.
+
 \begin{table}[!htp]
@@
 The quick brown fox jumps over the lazy dog.
-Thequick brown \index{fox} jumps over the lazy dog.
+The quick brown fox\index{fox} jumps over the lazy dog.
 The quick brown fox jumps over the lazy dog.

### 2023-03-24 book-en/book-en.tex
update

@@
 %\usepackage{indentfirst}
-\usepackage[perpage,symbol]{footmisc}   % footnote setting
 
-\usepackage{url,hyperref}
+% footnote setting
+%\usepackage[perpage,symbol]{footmisc}
+
+% hyperlink setting
+\usepackage{hyperref}
 \hypersetup{
@@
 \newcommand{\RR}{\ensuremath{\mathbb{R}}}
-\newcommand{\A}{\mathcal{A}}
-\newcommand{\ii}{\bm{\mathrm{i}}\,}  % imaginary part
-\newcommand{\md}{\mathrm{d}\,}
-\newcommand{\bA}{\boldsymbol{A}}
+\newcommand{\abs}[1]{\lvert#1\rvert}
+\newcommand{\norm}[1]{\lVert#1\rVert}
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
+\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
+\newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
 \newcommand{\red}[1]{\textcolor{red}{#1}}
@@
 \author{Edited by Andy}
-\date{\today}
+\date{February 2023}
 

### 2023-04-02 note-temp/main-en.tex
update

@@
 \usepackage[numbers,sort&compress]{natbib}
-\def\bibfont{\small}      % 修改参考文献字体
-\setlength{\bibsep}{8pt}  % 调整参考文献间距
-%\usepackage{subfig}
+%\def\bibfont{\small}      % bib font size
+%\setlength{\bibsep}{8pt}  % vertical space of bib
 
-% --- 算法宏包及设置 ---
+%----- package for algorithm -----
 \usepackage{algorithm}
@@
 
-% --- 代码高亮 ---
-%\input{matlab-style.tex}
+%----- code highlight -----
+%\lstset{basicstyle=\footnotesize\fontspec{Consolas}}
+%\lstset{basicstyle=\footnotesize\fontspec{Courier New}}
+%\newcommand*\lstinputpath[1]{\lstset{inputpath=#1}}
+%\lstinputpath{{./M-files/}}
 
@@
 
-% --- 自定义命令 -----
+%----- define new command -----
 \newcommand{\CC}{\ensuremath{\mathbb{C}}}
@@
 
-%\title{\LaTeX 笔记模板}
-%\author{某某某}
+%\title{\LaTeX note template}
+%\author{Author}
 %\institute{}
@@
 
-\pagenumbering{Roman} % 页码为大写罗马数字
-
 \input{cover2.tex}
 
-% ----- generate a empty page -----
+%----- generate a empty page -----
 %\clearpage%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\pagenumbering{Roman} % page is Roman numerals
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage
@@
 \clearpage
+
 \setlist[itemize]{label=$\circ$}
 
-\pagenumbering{arabic}  % 页码为阿拉伯数字
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%==========================================%
+\pagenumbering{arabic}  % page is arabic numerals
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 正文内容从这里开始  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%% Body Here %%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%% 参考文献 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{code highlight}
+
+MATLAB code
+
+\begin{lstlisting}[style=matlab,title={MATLAB code}]
+% Euler method for the ODE model
+% u'(x)=x^2+x-u, x in [0,1]
+% Initial condition: u(0)=0 ;
+% Exact solution: u(x)=-exp(-x)+x^2-x+1.
+clear all;  clf
+h=0.1;
+x=0:h:1;
+N=length(x)-1;
+u(1)=0;                        % initial value
+fun=@(t,u) t.^2+t-u;           % RHS
+
+for n=1:N
+    u(n+1)=u(n)+h.*fun(x(n),u(n));
+end
+
+ue=-exp(-x)+x.^2-x+1;          % exact solution
+plot(x,ue,'b-',x,u,'r+','LineWidth',1)
+legend('Exact','Numerical','location','North')
+%title('Euler method','fontsize',12)
+set(gca,'fontsize',12)
+xlabel('x','fontsize',16), ylabel('u','fontsize',16,'Rotation',0)
+\end{lstlisting}
+
+Python code
+
+\begin{lstlisting}[style=python,title={Python code}]
+#PythonDraw.py
+import turtle as t
+t.setup(650, 350, 200, 200)
+t.penup()
+t.fd(-250)
+t.pendown()
+t.pensize(25)
+t.pencolor("purple color")
+t.seth(-40)
+for i in range(4):
+    t.circle(40, 80)
+    t.circle(-40, 80)
+t.circle(40, 80/2)
+t.fd(40)
+t.circle(16, 180)
+t.fd(40 * 2/3)
+t.done()
+\end{lstlisting}
+
+%%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \phantomsection
-\addcontentsline{toc}{section}{References} % 添加  "参考文献 " 到目录
+\addcontentsline{toc}{section}{References}
 
-% 生成参考文献, 使用第一种请把第二种全部注释
-
-% 第一种方式, 使用 bib 文件
-
-%\nocite{*}  % 可以暂时显示全部参考文献, 包括未引用的
-
+%\nocite{*}
 \bibliography{reference}
 
-% 第二种方式, 按照格式直接写文献信息, 使用第二种请把第一种全部注释
-
 %\begin{thebibliography}{99}
+%\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces[M]. Elsevier, 2003.
+%
+%\bibitem{GoVa2013} Gene~H. Golub and Charles~F. Van~Loan. Matrix computations. The Johns Hopkins University Press, Baltimore, 4th edition, 2013.
+%
+%\bibitem{Shen1994} Shen~J. Efficient spectral-Galerkin method I. Direct solvers of second- and fourth-order equations using Legendre polynomials[J]. SIAM J. Sci. Comput., 1994, 15(6): 1489-1505.
+%
 %\bibitem{Tadmor2012} Tadmor~E. A review of numerical methods for nonlinear partial differential
-%  equations\allowbreak[J]. Bull. Amer. Math. Soc., 2012, 49(4): 507-554.
+%  equations[J]. Bull. Amer. Math. Soc., 2012, 49(4): 507-554.
 %
-%\bibitem{LiLiu1997} 李荣华, 刘播. 微分方程数值解法\allowbreak[M]. 东南大学出版社, 1997.
-%
-%\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces\allowbreak[M]. Elsevier, 2003.
-%
-%\bibitem{TreWei2014}Trefethen~L~N, Weideman~J~A~C. The exponentially convergent trapezoidal rule\allowbreak[J]. SIAM Rev., 2014, 56(3): 385-458.
-%
-%\bibitem{Shen1994} Shen~J.
-Efficient spectral-Galerkin method I.
-Direct solvers of second- and fourth-order equations using Legendre polynomials\allowbreak[J].
-SIAM J.
-Sci.
-Comput., 1994, 15(6): 1489-1505.
+%\bibitem{TreWei2014} Trefethen~L~N, Weideman~J~A~C. The exponentially convergent trapezoidal rule[J]. SIAM Rev., 2014, 56(3): 385-458.
 %

### 2023-04-14 amsart-en/amsart-temp.tex
update

@@
 % package for hyperlink
-\usepackage{url,hyperref}
+\usepackage{hyperref}
 % package for layout of list
@@
 %\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
-\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
-\captionsetup[table]{position=top,skip={2pt},name={Table}}
+\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
+\captionsetup[table]{position=top,skip={4pt},name={Table}}
 %\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
@@
 
+% graphic path
+\graphicspath{{./figures/}}
+
+% blankbox for figure
+\newcommand{\blankbox}[2]{%
+\parbox{\columnwidth}{\centering
+\setlength{\fboxsep}{0pt}%
+\fbox{\raisebox{0pt}[#2]{\hspace{#1}}}}%
+}
+
+% differential operator
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+
 % new command
 \newcommand{\abs}[1]{\lvert#1\rvert}
-\newcommand{\dx}[1][x]{\,\mathrm{d}#1}
-\newcommand{\ddx}[1][x]{\dfrac{\mathrm{d}}{\mathrm{d}#1}}
+\newcommand{\norm}[1]{\lVert#1\rVert}
+\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
+\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
 \newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
@@
 \section{Introduction}
-The introduction introduces the context and summarizes the
-manuscript. It is importantly to clearly state the contributions of
-this piece of work.
+The introduction introduces the context and summarizes the manuscript. 
+It is importantly to clearly state the contributions of this piece of work.
 
@@
 \left\{\begin{aligned}
-  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{ in } ~\Omega\times\mathcal{T}, \\
-  &\, u(x,y,t) = g(t), \quad \text{ on } ~ \partial \Omega, \\
-  &\, u(x,y,0)=\varphi(x, y), \quad \text{ on } ~\Omega.
+  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
+  &\, u(x,y,t) = g(t), \quad \text{on } ~ \partial \Omega, \\
+  &\, u(x,y,0)=\varphi(x, y), \quad \text{on } ~\Omega.
 \end{aligned}\right.
@@
 \ref{sec:main}, our new algorithm is in \ref{sec:alg}, experimental
-results are in \ref{sec:experiments}, discussion is in \ref{sec:discussion} and the conclusions follow in
-\ref{sec:conclusions}.
+results are in \ref{sec:experiments}, discussion is in \ref{sec:discussion} 
+and the conclusions follow in \ref{sec:conclusions}.
+
+\section{Preliminaries}
+\label{sec:preliminaries}
+
+\subsection{This is subsection}
+
+\subsubsection{This is subsubsection}
 
@@
 
-%\subsection{Subsection name}
-
-We interleave text filler with some example theorems and theorem-like
-items.
+We interleave text filler with some example theorems and theorem-like items.
 
@@
 
-This is a citation example \cite{Adams2003}. This statement requires citation \cite{Shen1994,Tadmor2012,TreWei2014}.
+This is a citation example \cite{Adams2003}. This statement requires 
+citation \cite{Shen1994,Tadmor2012,TreWei2014}.
 
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed
-for the production of technical and scientific documentation.
-LaTeX is the de facto standard for the communication and publication of scientific documents.
-LaTeX is based on the idea that it is better to leave document design to
-document designers, and to let authors get on with writing documents.
+%LaTeX is a high-quality typesetting system; it includes features designed
+%for the production of technical and scientific documentation.
 
@@
 \begin{remark}
-Observe that \ref{thm:bigthm}, \ref{thm:mvt} correctly mix references
-to multiple labels.
+Observe that \ref{thm:bigthm}, \ref{thm:mvt} correctly mix references to multiple labels.
 \end{remark}
@@
 
-Note that it may require two \LaTeX\ compilations for the proof marks
-to show.
+Note that it may require two \LaTeX\ compilations for the proof marks to show.
 
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed
-for the production of technical and scientific documentation.
-LaTeX is the de facto standard for the communication and publication of scientific documents.
-LaTeX is based on the idea that it is better to leave document design to
-document designers, and to let authors get on with writing documents.
+Some experimental results here.
 
@@
 
-Figure \ref{fig:a} shows some example results.
+\begin{figure}[htp!]
+\blankbox{.6\columnwidth}{10pc}
+\caption{This is an example of a figure caption with text.}
+\label{fig:blackbox}
+\end{figure}
+
+\textbf{Some figures and tables here.}
+
+Figure~\ref{fig:foo} shows some example results.
 \begin{figure}[htp!]
@@
   \caption{Example figure using external image files.}
-  \label{fig:a}
+  \label{fig:foo}
 \end{figure}
 
-\clearpage
-The two figures are placed side by side, sharing the same title.
+The two figures are placed side by side, sharing one title, as shown in \autoref{fig:twofigs}.
 \begin{figure}[htp!]
@@
   \caption{Left: Caption 1, Right: Caption 2.}
-  \label{fig:b}
+  \label{fig:twofigs}
 \end{figure}
 
-Use \texttt{minipage} package to set up images side-by-side, each with its own title.
+Use the \texttt{tabularx} environment to generate \autoref{tab:error}.
+
+\begin{table}[htp!]
+\centering
+\newcolumntype{L}{X}
+\newcolumntype{C}{>{\centering \arraybackslash}X}
+\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
+\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
+\renewcommand\arraystretch{1.2}
+\caption{Table description}
+\label{tab:error}
+\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
+\Xhline{2\arrayrulewidth}
+N  & A       & B    & C       & D      & E     \\
+\Xhline{2\arrayrulewidth}
+2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
+4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
+6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
+8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
+10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
+12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
+14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
+%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
+\Xhline{2\arrayrulewidth}
+\end{tabularx}
+\end{table}
+
+Use \texttt{minipage} package to set images side-by-side, each with its own title, 
+as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
 \begin{figure}[htp!]
@@
   \caption{Caption A}
-  \label{fig:image1}
+  \label{fig:A}
 \end{minipage}
@@
 \centering
-   \includegraphics[width=0.95\linewidth]{fig2}
+   \includegraphics[width=0.96\linewidth]{fig2}
    \caption{Caption B}
-   \label{fig:image2}
+   \label{fig:B}
 \end{minipage}
@@
 
-Additional results are available in the supplement in Table \ref{tab:foo}.
+Additional results are available in the supplement in Table~\ref{tab:foo}.
 
@@
 
-\clearpage
-Use the \texttt{tabularx} environment to generate tables.
-\begin{table}[htp!]
-\centering
-\newcolumntype{L}{X}
-\newcolumntype{C}{>{\centering \arraybackslash}X}
-\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
-\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
-\renewcommand\arraystretch{1.2}
-\caption{Table description}
-\label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
-\Xhline{2\arrayrulewidth}
-N  & A       & B    & C       & D      & E     \\
-\Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
-\end{table}
-
 \section{Discussion of \texorpdfstring{{$Z=X \cup Y$}}{Z = X union Y}}
@@
 
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here.
 
-\section{Conclusions}
-\label{sec:conclusions}
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here.
 
+\section{Conclusions}\label{sec:conclusions}
+
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here. 
 Some conclusions here.
+
+Some conclusions here. Some conclusions here. Some conclusions here. 
+Some conclusions here. Some conclusions here. Some conclusions here. 
+Some conclusions here. Some conclusions here.
 
@@
 This is a equation in appendix.
-\begin{equation}\label{eq:A1}
+\begin{equation}\label{eq:abc}
   a^2+b^2=c^2.

### 2023-04-14 amsart-en/amsart-temp2.tex
update

@@
 \usepackage{fancybox}
+% package for address
 \usepackage[foot]{amsaddr}
@@
 % layout setting
-\setlength{\textwidth}{15cm}
-\setlength{\textheight}{21.6cm}
-\setlength{\oddsidemargin}{0.5cm}
-\setlength{\evensidemargin}{0.5cm}
+\usepackage{geometry}
+\geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}
+%\setlength{\textwidth}{15cm}
+%\setlength{\textheight}{21.6cm}
+%\setlength{\oddsidemargin}{0.5cm}
+%\setlength{\evensidemargin}{0.5cm}
 
@@
 %\usepackage[symbol]{footmisc}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
 
@@
 \newtheorem{corollary}{Corollary}[section]
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newtheorem{corollary}[theorem]{Corollary}
 
@@
 \section{Introduction}
-The introduction introduces the context and summarizes the
-manuscript. It is importantly to clearly state the contributions of
-this piece of work.
+The introduction introduces the context and summarizes the manuscript.
+It is importantly to clearly state the contributions of this piece of work.
 
@@
   \item item two
+  %\item item three
 \end{itemize}
@@
   \item item two
+  %\item item three
 \end{enumerate}
@@
 \ref{sec:main}, our new algorithm is in \ref{sec:alg}, experimental
-results are in \ref{sec:experiments}, discussion is in \ref{sec:discussion} and the conclusions follow in
-\ref{sec:conclusions}.
+results are in \ref{sec:experiments}, discussion is in \ref{sec:discussion}
+and the conclusions follow in \ref{sec:conclusions}.
+
+\section{Preliminaries}
+\label{sec:preliminaries}
+
+\subsection{This is subsection}
+
+\subsubsection{This is subsubsection}
 
@@
 
-This is a citation example \cite{Adams2003}. This statement requires citation \cite{Shen1994,Tadmor2012,TreWei2014}.
+This is a citation example \cite{Adams2003}. This statement requires
+citation \cite{Shen1994,Tadmor2012,TreWei2014}.
 
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed
-for the production of technical and scientific documentation.
-%LaTeX is the de facto standard for the communication and publication of scientific documents.
-%LaTeX is based on the idea that it is better to leave document design to
-%document designers, and to let authors get on with writing documents.
+%LaTeX is a high-quality typesetting system; it includes features designed
+%for the production of technical and scientific documentation.
 
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed
-for the production of technical and scientific documentation.
-%LaTeX is the de facto standard for the communication and publication of scientific documents.
-%LaTeX is based on the idea that it is better to leave document design to
-%document designers, and to let authors get on with writing documents.
+Some experimental results here.
 
@@
   \caption{Left: Caption 1, Right: Caption 2.}
-  \label{fig:b}
+  \label{fig:twofigs}
 \end{figure}
 
-Use \texttt{minipage} package to set up images side-by-side, each with its own title.
+Use the \texttt{tabularx} environment to generate \autoref{tab:error}.
+
+\begin{table}[htp!]
+\centering
+\newcolumntype{L}{X}
+\newcolumntype{C}{>{\centering \arraybackslash}X}
+\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
+\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
+\renewcommand\arraystretch{1.2}
+\caption{Table description}
+\label{tab:error}
+\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
+\Xhline{2\arrayrulewidth}
+N  & A       & B    & C       & D      & E     \\
+\Xhline{2\arrayrulewidth}
+2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
+4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
+6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
+8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
+10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
+12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
+14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
+%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
+\Xhline{2\arrayrulewidth}
+\end{tabularx}
+\end{table}
+
+Use \texttt{minipage} package to set images side-by-side, each with its own title,
+as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
 \begin{figure}[htp!]
@@
 
-Use the \texttt{tabularx} environment to generate tables.
-\begin{table}[htp!]
-\centering
-\newcolumntype{L}{X}
-\newcolumntype{C}{>{\centering \arraybackslash}X}
-\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
-\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
-\renewcommand\arraystretch{1.2}
-\caption{Table description}
-\label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
-\Xhline{2\arrayrulewidth}
-N  & A       & B    & C       & D      & E     \\
-\Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
-\end{table}
-
 \section{Discussion of \texorpdfstring{{$Z=X \cup Y$}}{Z = X union Y}}
@@
 
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here.
 
-\section{Conclusions}
-\label{sec:conclusions}
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here.
 
+\section{Conclusions}\label{sec:conclusions}
+
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
 Some conclusions here.
+
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here.
 

### 2023-04-14 article-en/article-temp.tex
update

@@
 % layout setting
-\setlength{\textwidth}{15cm}
-\setlength{\textheight}{21.6cm}
-\setlength{\oddsidemargin}{0.5cm}
-\setlength{\evensidemargin}{0.5cm}
+\usepackage{geometry}
+\geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}
+%\setlength{\textwidth}{15cm}
+%\setlength{\textheight}{21.6cm}
+%\setlength{\oddsidemargin}{0.5cm}
+%\setlength{\evensidemargin}{0.5cm}
 
 % command for line spacing
-%\renewcommand{\baselinestretch}{1.1}
+\renewcommand{\baselinestretch}{1.1}
 
@@
 %\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+% command for listsep
+\setlist{nolistsep}
 
@@
 
+% graphic path
+\graphicspath{{./figures/}}
+
+% differential operator
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+
 % new command
 \newcommand{\abs}[1]{\lvert#1\rvert}
-\newcommand{\dx}[1][x]{\,\mathrm{d}#1}
-\newcommand{\ddx}[1][x]{\dfrac{\mathrm{d}}{\mathrm{d}#1}}
+\newcommand{\norm}[1]{\lVert#1\rVert}
+\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
+\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
 \newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
@@
 \left\{\begin{aligned}
-  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{ in } ~\Omega\times\mathcal{T}, \\
-  &\, u(x,y,t) = g(t), \quad \text{ on } ~ \partial \Omega, \\
-  &\, u(x,y,0)=\varphi(x, y), \quad \text{ on } ~\Omega.
+  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
+  &\, u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega, \\
+  &\, u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega.
 \end{aligned}\right.
@@
   \item item two
+  \item item three
 \end{itemize}
@@
   \item item two
+  \item item three
 \end{enumerate}
@@
 
+\section{Preliminaries}
+\label{sec:preliminaries}
+
+\subsection{This is subsection}
+
+\subsubsection{This is subsubsection}
+
 \section{Main results}
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed
-for the production of technical and scientific documentation.
-LaTeX is the de facto standard for the communication and publication of scientific documents.
-LaTeX is based on the idea that it is better to leave document design to
-document designers, and to let authors get on with writing documents.
+LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
+LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
 
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed
-for the production of technical and scientific documentation.
-LaTeX is the de facto standard for the communication and publication of scientific documents.
-LaTeX is based on the idea that it is better to leave document design to
-document designers, and to let authors get on with writing documents.
+Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here.Some experimental results here.
 
@@
 
-\clearpage
-Figure \ref{fig:a} shows some example results.
+Figure~\ref{fig:foo} shows some example results.
 \begin{figure}[htp!]
@@
   \caption{Example figure using external image files.}
-  \label{fig:a}
+  \label{fig:foo}
 \end{figure}
 
-The two figures are placed side by side, sharing the same title.
+The two figures are placed side by side, sharing the same title, as shown in \autoref{fig:twofigs}.
 \begin{figure}[htp!]
@@
   \caption{Left: Caption 1, Right: Caption 2.}
-  \label{fig:b}
+  \label{fig:twofigs}
 \end{figure}
 
-Use \texttt{minipage} package to set up images side-by-side, each with its own title.
+Use the \texttt{tabularx} environment to generate \autoref{tab:error}.
+
+\begin{table}[htp!]
+\centering
+\newcolumntype{L}{X}
+\newcolumntype{C}{>{\centering \arraybackslash}X}
+\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
+\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
+\renewcommand\arraystretch{1.2}
+\caption{Table description}
+\label{tab:error}
+\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
+\Xhline{2\arrayrulewidth}
+N  & A       & B    & C       & D      & E     \\
+\Xhline{2\arrayrulewidth}
+2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
+4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
+6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
+8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
+10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
+12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
+%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
+%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
+\Xhline{2\arrayrulewidth}
+\end{tabularx}
+\end{table}
+
+Use \texttt{minipage} package to set images side-by-side, each with its own title, as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
 \begin{figure}[htp!]
@@
 
-Use the \texttt{tabularx} environment to generate tables.
-
-\begin{table}[htp!]
-\centering
-\newcolumntype{L}{X}
-\newcolumntype{C}{>{\centering \arraybackslash}X}
-\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
-\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
-\renewcommand\arraystretch{1.2}
-\caption{Table description}
-\label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
-\Xhline{2\arrayrulewidth}
-N  & A       & B    & C       & D      & E     \\
-\Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
-\end{table}
-
 \section{Discussion of \texorpdfstring{{\boldmath$Z=X \cup Y$}}{Z = X union Y}}
@@
 
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here.
+
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here. Some discussions here. 
+Some discussions here. Some discussions here.
 
@@
 
+Some conclusions here. Some conclusions here. Some conclusions here. 
+Some conclusions here. Some conclusions here. Some conclusions here. 
 Some conclusions here.
+
+Some conclusions here. Some conclusions here. Some conclusions here. 
+Some conclusions here. Some conclusions here. Some conclusions here. 
+Some conclusions here. Some conclusions here.
 

### 2023-04-14 article-en/article-temp2.tex
update

@@
 \usepackage{fancybox}
+% package for page headers and footers
+\usepackage{fancyhdr}
+
+% package for section etc.
+\usepackage{titlesec}
+\titleformat{\section}{\large\bfseries}{\thesection.}{1.2ex}{}
+\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
+\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}
 
@@
 % layout setting
-\setlength{\textwidth}{15cm}
-\setlength{\textheight}{21.6cm}
-\setlength{\oddsidemargin}{0.5cm}
-\setlength{\evensidemargin}{0.5cm}
+\usepackage{geometry}
+\geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}
+%\setlength{\textwidth}{15cm}
+%\setlength{\textheight}{21.6cm}
+%\setlength{\oddsidemargin}{0.5cm}
+%\setlength{\evensidemargin}{0.5cm}
+
+% headers and footers setting
+%\pagestyle{fancy}
+%\fancyhf{}
+%\fancyhead[CO]{\uppercase{Title of Paper}}
+%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
+%\fancyfoot[C]{\thepage}
+%\renewcommand{\headrulewidth}{0pt}
+
+%\fancyhead[C]{\uppercase{Title of Paper}}
+%\fancyfoot[C]{\thepage}
+%\renewcommand{\headrulewidth}{0pt}
+
+%\fancyhead[CO]{\uppercase{Title of Paper}}
+%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
+%\fancyhead[RO]{\thepage}
+%\fancyhead[LE]{\thepage}
 
 % command for line spacing
-%\renewcommand{\baselinestretch}{1.1}
+\renewcommand{\baselinestretch}{1.1}
 
@@
 \theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
+\newtheorem{remark}[theorem]{Remark}
 
 % caption setting
-%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
+%\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
+\captionsetup{font={small},labelformat={default},labelsep=period}
 \captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
@@
 
+% redefine abstract environment
+\makeatletter
+\renewenvironment{abstract}{%
+    \if@twocolumn
+      \section*{\abstractname}%
+    \else %% <- here removed \small
+      \begin{center}%
+        {\bfseries \large\abstractname\vspace{\z@}} %% <- here added \large
+      \end{center}%
+      \quotation
+    \fi}
+    {\if@twocolumn\else\endquotation\fi}
+\makeatother
+
+% graphic path
+\graphicspath{{./figures/}}
+
+% differential operator
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+
 % new command
 \newcommand{\abs}[1]{\lvert#1\rvert}
-\newcommand{\dx}[1][x]{\,\mathrm{d}#1}
-\newcommand{\ddx}[1][x]{\dfrac{\mathrm{d}}{\mathrm{d}#1}}
+\newcommand{\norm}[1]{\lVert#1\rVert}
+\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
+\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
 \newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
@@
 % Information for title and author
-\title{An Example Article\thanks{The work is supported in part by NSF Grant No. 12345678 and ...}}
+\title{An Example Article}
 
-%\author{Author A, Author B, and J. E. Smith\thanks{Corresponding author (\textit{E-mail address:} \texttt{xyz@math.univ.edu}).} }
+\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
+\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
+\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
+%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
+\affil[1]{Department of Mathematics, \LaTeX\ University.}
+\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
 
-\author{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
-\affil{Department of Computer Science, \LaTeX\ University.}
-
-\author{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
-\affil{Department of Mathematics, \LaTeX\ University.}
-
-\author{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
-\affil{Department of Mechanical Engineering, \LaTeX\ University}
-
-\date{\today}
+\date{Date: \today}
 
@@
 
+\section{Preliminaries}
+\label{sec:preliminaries}
+
+\subsection{This is subsection}
+
+\subsubsection{This is subsubsection}
+
 \section{Main results}
 \label{sec:main}
-
-%\subsection{Subsection name}
 
@@
 
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
+Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
+
+Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
 
@@
 
-Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
+
+Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
 

### 2023-04-14 book-en/book-cover-en.tex
update

@@
 
-% define new command
+% differential operator
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+
+% new command
 \newcommand{\CC}{\ensuremath{\mathbb{C}}}
 \newcommand{\RR}{\ensuremath{\mathbb{R}}}
-% new command
 \newcommand{\abs}[1]{\lvert#1\rvert}
 \newcommand{\norm}[1]{\lVert#1\rVert}
-\newcommand{\dif}{\mathop{}\!\mathrm{d}}
 \newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
@@
 
-%----------------------------------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % TITLE PAGE
-%----------------------------------------------------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-	\vspace{2\baselineskip} % Whitespace after the title block
-
-	%------------------------------------------------
-	%	Subtitle
-	%------------------------------------------------
-
-	% A Number of Fascinating and Life-changing Templates Presented in a Clear and Concise Way
-
-	\vspace*{3\baselineskip} % Whitespace under the subtitle
+	\vspace{5\baselineskip} % Whitespace after the title block
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \thispagestyle{empty}
@@
 \frontmatter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\clearpage
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \mainmatter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Figure \ref{fig:a} shows some example results.
+Figure \ref{fig:sinx} shows some example results.
 \begin{figure}[htp!]
@@
   \caption{Example figure using external image files.}
-  \label{fig:a}
+  \label{fig:sinx}
 \end{figure}
@@
 \clearpage
-The two figures are placed side by side, sharing the same title.
+The two figures are placed side by side, sharing the one title, as shown in Figure~\ref{fig:twofigs}.
 \begin{figure}[htp!]
@@
   \includegraphics[width=0.45\linewidth]{image2}
-  \caption{Left: Caption 1, Right: Caption 2.}
-  \label{fig:b}
+  \caption{Left: Caption 1, ~ Right: Caption 2.}
+  \label{fig:twofigs}
 \end{figure}
 
-Use \texttt{minipage} package to set up images side-by-side, each with its own title.
+Use \texttt{minipage} package to set images side-by-side, each with its own title, as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
 \begin{figure}[htp!]
@@
    \caption{Caption B}
-   \label{fig:image2}
+   \label{fig:B}
 \end{minipage}
@@
 
-This is Figure \ref{fig:aa}.
+This is Figure~\ref{fig:sinx2}.
 \begin{figure}[htp!]
@@
   \caption{Example figure using external image files.}
-  \label{fig:aa}
+  \label{fig:sinx2}
 \end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \backmatter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2023-04-14 book-en/book-en.tex
update

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \frontmatter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%LaTeX is a high-quality typesetting system; it includes features designed
-%for the production of technical and scientific documentation.
-%LaTeX is the de facto standard for the communication and publication of scientific documents.
-%LaTeX is based on the idea that it is better to leave document design to
-%document designers, and to let authors get on with writing documents.
-
 \section{Figure Environment}
 
-Figure \ref{fig:a} shows some example results.
+Figure \ref{fig:sinx} shows some example results.
 \begin{figure}[htp!]
@@
 The quick brown fox jumps over the lazy dog.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-04-14 note-temp/main-en.tex
update

@@
 
+%----- header and footer -----
+\fancypagestyle{plain}{%
+	\fancyhf{}
+	\fancyhead[C]{\color{ecolor}\nouppercase{\leftmark}}
+	\fancyfoot[C]{\color{gray}\thepage}
+    \renewcommand{\headrulewidth}{0.5pt}
+}
+
+\pagestyle{plain}
+
 %----- package for algorithm -----
@@
 \algrenewcommand\algorithmicensure{\textbf{Output:}}
+
+%----- maketitle -----
+\makeatletter
+\renewcommand*{\maketitle}{
+\begin{titlepage}
+    \pdfbookmark[1]{Cover}{cover}
+    \centering
+    %\scshape
+    \vspace*{5\baselineskip}
+    \color{ecolor}
+
+    %-------- title ---------
+    \rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
+    \rule{\textwidth}{0.4pt}
+
+    \vspace{0.75\baselineskip}
+
+    {\LARGE\bfseries \@title}
+
+	\vspace{0.75\baselineskip}
+
+	\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt}
+	\rule{\textwidth}{1.6pt}
+
+	\vspace{4\baselineskip}
+
+    %----- Author -----
+    {\Large \@author}
+
+    \vspace{0.35\baselineskip}
+
+    {\Large \@date}
+	\vfill
+\end{titlepage}
+\thispagestyle{empty}
+}
+\makeatother
 
@@
 
+% bibliography style
 %\bibliographystyle{thuthesis-numeric}
@@
 
-%\title{\LaTeX note template}
-%\author{Author}
+\title{Title of Note Template ElegantNote \\[20pt]
+\Large Subtitle of notes
+}
+\author{Author}
 %\institute{}
@@
 %\date{\zhtoday}
-%\date{}
+\date{June, 2022}
 
 \begin{document}
-%\maketitle
 
-\input{cover2.tex}
+\maketitle
 
@@
 
-\section{code highlight}
+\section{Code highlight}
 
@@
 % Initial condition: u(0)=0 ;
-% Exact solution: u(x)=-exp(-x)+x^2-x+1.
 clear all;  clf
@@
 fun=@(t,u) t.^2+t-u;           % RHS
-
 for n=1:N
@@
 end
-
 ue=-exp(-x)+x.^2-x+1;          % exact solution
@@
 legend('Exact','Numerical','location','North')
-%title('Euler method','fontsize',12)
 set(gca,'fontsize',12)
-xlabel('x','fontsize',16), ylabel('u','fontsize',16,'Rotation',0)
+xlabel('x','fontsize',16), ylabel('u','fontsize',16)
 \end{lstlisting}

### 2023-04-14 book-cn/makefiles.sh

@@ -1,9 +1,8 @@
 #!/bin/bash
 
-#-> Get source filename
-find . -name "*.tex"|while read FileName;
-do 
-#--- Process FileName.tex ---
+#-> Get source FileName
+find . -maxdepth 1 -type f -name "*.tex" | while read FileName; do 
+#--- Process file.tex ---
 echo "$FileName"
 echo "${FileName%.tex}"
 #-> Compile the main file
@@ -11,7 +10,6 @@ xelatex --synctex=-1 "$FileName"
 bibtex "${FileName%.tex}"
 xelatex --synctex=-1 "$FileName"
 xelatex --synctex=-1 "$FileName"
-#clear aux files
+#-> Clear aux files
 rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
 done
-

### 2023-04-14 book-en/compile-pdflatex-bibtex.sh

@@ -1,8 +1,7 @@
 #!/bin/bash
 
 #-> Get source filename
-find . -name "*.tex"|while read FileName;
-do 
+find . -maxdepth 1 -type f -name "*.tex" | while read FileName; do 
 #--- Process FileName.tex ---
 echo "$FileName"
 echo "${FileName%.tex}"
@@ -14,4 +13,3 @@ pdflatex --synctex=-1 "$FileName"
 #clear aux files
 rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
 done
-

### 2023-04-14 note-temp/compile-pdflatex-en.sh

@@ -1,8 +1,7 @@
 #!/bin/bash
 
 #-> Get source filename
-find . -name "*en.tex"|while read FileName;
-do 
+find . -maxdepth 1 -type f -name "*en.tex" | while read FileName; do 
 #--- Process FileName.tex ---
 echo "$FileName"
 echo "${FileName%.tex}"
@@ -11,7 +10,7 @@ pdflatex --synctex=-1 "$FileName"
 bibtex "${FileName%.tex}"
 pdflatex --synctex=-1 "$FileName"
 pdflatex --synctex=-1 "$FileName"
-#clear aux files
+#-> Clear aux files
 rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
 done
 

### 2023-04-14 note-temp/compile-xelatex-cn.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 
 #-> Get source filename
-find . -name "*cn.tex"|while read FileName;
+find . -maxdepth 1 -type f -name "*cn.tex" | while read FileName;
 do 
 #--- Process FileName.tex ---
 echo "$FileName"
@@ -11,7 +11,7 @@ xelatex --synctex=-1 "$FileName"
 bibtex "${FileName%.tex}"
 xelatex --synctex=-1 "$FileName"
 xelatex --synctex=-1 "$FileName"
-#clear aux files
+#-> Clear aux files
 rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
 done
 

### 2023-04-14 note-temp/makefiles.sh

@@ -1,10 +1,15 @@
 #!/bin/bash
+
+#-> Get source FileName
+find . -maxdepth 1 -type f -name "*.tex" | while read FileName; do 
+#--- Process file.tex ---
+echo "$FileName"
+echo "${FileName%.tex}"
 #-> Compile the main file
-xelatex --synctex=-1 main.tex
-bibtex main
-xelatex --synctex=-1 main.tex
-xelatex --synctex=-1 main.tex
-#clear aux files
+xelatex --synctex=-1 "$FileName"
+bibtex "${FileName%.tex}"
+xelatex --synctex=-1 "$FileName"
+xelatex --synctex=-1 "$FileName"
+#-> Clear aux files
 rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
 done
-

### 2023-04-25 amsart-en/amsart-temp.tex
update

@@
 
-% blankbox for figure
+% blank box for figure
 \newcommand{\blankbox}[2]{%
@@
 
-\author[Author A \; \& \; Author B]{Author A${\,}^{1}$ \quad and \quad Author B${\,}^{2,*}$}
+\author[Author A and Author B]{Author A${}^{1}$ and Author B${}^{2,*}$}
 
-\thanks{${}^{*}$ Corresponding author (E-mail: \texttt{xyz@math.univ.edu}). \\
-\indent ${}^{1}$ Department of Computer Science, \LaTeX\ University. \\
-\indent ${}^{2}$ Department of Mechanical Engineering, \LaTeX\ University \\
-\indent This work is supported in part by NSFC grants No. 12345678 and ...
-}
+\thanks{${}^{*}$Corresponding author (E-mail: \texttt{xyz@math.univ.edu})}
+\thanks{${}^{1}$Department of Computer Science, \LaTeX\ University}
+\thanks{${}^{2}$Department of Mechanical Engineering, \LaTeX\ University}
+\thanks{This work is supported in part by NSFC grants No. 12345678 and ...}
 

### 2023-04-25 article-en/article-temp.tex
update

@@
 \author{
-  Author A\thanks{Department of Computer Science, \LaTeX\ University.}
-  \and
-  Author B\thanks{Department of Mathematics, \LaTeX\ University.}
-  %\thanks{Email address: \texttt{xyz@math.univ.edu}}
-  \and
+  Author A\thanks{Department of Computer Science, \LaTeX\ University}~,
+  Author B\thanks{Department of Mathematics, \LaTeX\ University}~,
+  and
   Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}

### 2023-04-25 article-en/article-temp3.tex
update

--- 2023-02-13 article-en/article-temp.tex
@@
 
+% graphic path
+\graphicspath{{./figures/}}
+
+% differential operator
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+
 % new command
 \newcommand{\abs}[1]{\lvert#1\rvert}
-\newcommand{\dx}[1][x]{\,{\rm d}#1}
-\newcommand{\ddx}[1][x]{\dfrac{\rm d}{{\rm d}#1}}
+\newcommand{\norm}[1]{\lVert#1\rVert}
+\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
+\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
 \newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
@@
 % Information for title and author
-\title{An Example Article\thanks{The work is supported in part by NSF Grant No. 12345678 and ...}}
+\title{An Example Article}
 
@@
 \author{
-  Author A\thanks{Department of Computer Science, \LaTeX\ University.}
+  Author A \\
+  {\itshape Department of Computer Science, \LaTeX\ University} \\
   \and
-  Author B\thanks{Department of Mathematics, \LaTeX\ University.}
-  %\thanks{Email address: \texttt{xyz@math.univ.edu}}
+  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
+  {\itshape Department of Mathematics, \LaTeX\ University} \\
   \and
-  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
+  Author C\thanks{This author was supported in part by NSF Grant No. 12345678.} \\
+  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
 }
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed
-for the production of technical and scientific documentation.
-LaTeX is the de facto standard for the communication and publication of scientific documents.
-LaTeX is based on the idea that it is better to leave document design to
-document designers, and to let authors get on with writing documents.
+%LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
+%LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
 
@@
 
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
-Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here.
+
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here.
 
@@
 
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
 Some conclusions here.
+
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here.
 

### 2023-04-25 article-cn/makefiles.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+#-> Get source FileName
+find . -maxdepth 1 -type f -name "*.tex" | while read FileName; do 
+#--- Process file.tex ---
+echo "$FileName"
+echo "${FileName%.tex}"
+#-> Compile the main file
+xelatex --synctex=-1 "$FileName"
+bibtex "${FileName%.tex}"
+xelatex --synctex=-1 "$FileName"
+xelatex --synctex=-1 "$FileName"
+#-> Clear aux files
+rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
+done

### 2023-04-26 article-en/article-temp-header.tex
update

--- 2023-04-14 article-en/article-temp2.tex
@@
 
-\documentclass[10pt,reqno,final]{article}
+\documentclass[10pt,twoside,reqno,final]{article}
 %\documentclass[10pt,reqno,draft]{article}
@@
 
+\makeatletter
+\newcommand\@shorttitle{}
+\newcommand\shorttitle[1]{\def\@shorttitle{#1}}
+\newcommand\@shortauthor{}
+\newcommand\shortauthor[1]{\def\@shortauthor{#1}}
+\makeatother
+
 % headers and footers setting
@@
 
-%\fancyhead[CO]{\uppercase{Title of Paper}}
-%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
-%\fancyhead[RO]{\thepage}
-%\fancyhead[LE]{\thepage}
+\makeatletter
+\pagestyle{fancy}
+\fancyhf{}
+\fancyhead[CO]{\@shorttitle}
+\fancyhead[CE]{\@shortauthor}
+\fancyhead[RO]{\thepage}
+\fancyhead[LE]{\thepage}
+\makeatother
 
@@
 %\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
-\captionsetup{font={small},labelformat={default},labelsep=period}
-\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
-\captionsetup[table]{position=top,skip={2pt},name={Table}}
+\captionsetup{labelformat={default},labelsep=period}
+\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
+\captionsetup[table]{position=top,skip={4pt},name={Table}}
 %\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
@@
 
+% redefine maketitle environment
+\makeatletter
+\def\@maketitle{%
+  \newpage
+  \null
+  %\vspace{-1.5em}%
+  \begin{center}%
+    \let \footnote \thanks
+    {\Large \bfseries \@title \par}%
+    \vskip 1.5em%
+    {\large
+      \lineskip 0.5em%
+      \begin{tabular}[t]{c}%
+        \@author
+      \end{tabular}\par}%
+    \vskip 0.5em%
+    {\large \@date}%
+  \end{center}%
+  \par
+  \vskip 1em
+}
+\makeatother
+
 % redefine abstract environment
@@
     \quotation
-    \fi}
-    {\if@twocolumn\else\endquotation\fi}
+  \fi}{
+  \if@twocolumn\else\endquotation\fi
+}
 \makeatother
@@
 
+\shorttitle{Short Title of Article}
+\shortauthor{Author A, Author B, and Author C}
+
 \author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
@@
 %\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
-\affil[1]{Department of Mathematics, \LaTeX\ University.}
+\affil[1]{Department of Mathematics, \LaTeX\ University}
 \affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

### 2023-04-26 article-en/article-temp2.tex
update

@@
 \usepackage{algpseudocode}
-% package for author and affiliation style
-\usepackage[affil-it]{authblk}
 % package for using box and verbatim
 \usepackage{fancybox}
-% package for page headers and footers
-\usepackage{fancyhdr}
-
-% package for section etc.
-\usepackage{titlesec}
-\titleformat{\section}{\large\bfseries}{\thesection.}{1.2ex}{}
-\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
-\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}
 
@@
 %\setlength{\evensidemargin}{0.5cm}
-
-% headers and footers setting
-%\pagestyle{fancy}
-%\fancyhf{}
-%\fancyhead[CO]{\uppercase{Title of Paper}}
-%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
-%\fancyfoot[C]{\thepage}
-%\renewcommand{\headrulewidth}{0pt}
-
-%\fancyhead[C]{\uppercase{Title of Paper}}
-%\fancyfoot[C]{\thepage}
-%\renewcommand{\headrulewidth}{0pt}
-
-%\fancyhead[CO]{\uppercase{Title of Paper}}
-%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
-%\fancyhead[RO]{\thepage}
-%\fancyhead[LE]{\thepage}
 
@@
 \theoremstyle{remark}
-\newtheorem{remark}[theorem]{Remark}
+\newtheorem{remark}{Remark}[section]
 
 % caption setting
-%\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
-\captionsetup{font={small},labelformat={default},labelsep=period}
-\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
-\captionsetup[table]{position=top,skip={2pt},name={Table}}
+%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
+\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
+\captionsetup[table]{position=top,skip={4pt},name={Table}}
 %\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
@@
 \numberwithin{table}{section}
-
-% redefine abstract environment
-\makeatletter
-\renewenvironment{abstract}{%
-    \if@twocolumn
-      \section*{\abstractname}%
-    \else %% <- here removed \small
-      \begin{center}%
-        {\bfseries \large\abstractname\vspace{\z@}} %% <- here added \large
-      \end{center}%
-      \quotation
-    \fi}
-    {\if@twocolumn\else\endquotation\fi}
-\makeatother
 
@@
 
-\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
-\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
-\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
-%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
-\affil[1]{Department of Mathematics, \LaTeX\ University.}
-\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
+%\author{Author A, Author B, and J. E. Smith\thanks{Corresponding author (\textit{E-mail address:} \texttt{xyz@math.univ.edu}).} }
 
-\date{Date: \today}
+\author{
+  Author A \\
+  {\itshape Department of Computer Science, \LaTeX\ University} \\
+  \and
+  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
+  {\itshape Department of Mathematics, \LaTeX\ University} \\
+  \and
+  Author C\thanks{This author was supported in part by NSF Grant No. 12345678.} \\
+  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
+}
+
+\date{\today}
 
@@
 
-We interleave text filler with some example theorems and theorem-like
-items.
+We interleave text filler with some example theorems and theorem-like items.
 
@@
 
-LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
-LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
+%LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
+%LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
 
@@
 
-Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here.
 
-Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here.
 
@@
 
-Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here.
 
-Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here.
 

### 2023-04-26 article-en/article-temp3.tex
update

@@
 \usepackage{algpseudocode}
+% package for author and affiliation style
+\usepackage[affil-it]{authblk}
 % package for using box and verbatim
 \usepackage{fancybox}
+% package for page headers and footers
+\usepackage{fancyhdr}
+
+% package for section etc.
+\usepackage{titlesec}
+\titleformat{\section}{\large\bfseries}{\thesection.}{1.2ex}{}
+\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
+\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}
 
@@
 %\setlength{\evensidemargin}{0.5cm}
+
+% headers and footers setting
+%\pagestyle{fancy}
+%\fancyhf{}
+%\fancyhead[CO]{\uppercase{Title of Paper}}
+%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
+%\fancyfoot[C]{\thepage}
+%\renewcommand{\headrulewidth}{0pt}
+
+%\fancyhead[C]{\uppercase{Title of Paper}}
+%\fancyfoot[C]{\thepage}
+%\renewcommand{\headrulewidth}{0pt}
+
+%\fancyhead[CO]{\uppercase{Title of Paper}}
+%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
+%\fancyhead[RO]{\thepage}
+%\fancyhead[LE]{\thepage}
 
@@
 \theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
+\newtheorem{remark}[theorem]{Remark}
 
 % caption setting
-%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
-\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
-\captionsetup[table]{position=top,skip={2pt},name={Table}}
+%\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
+\captionsetup{labelformat={default},labelsep=period}
+\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
+\captionsetup[table]{position=top,skip={4pt},name={Table}}
 %\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
@@
 \numberwithin{table}{section}
+
+% redefine maketitle environment
+\makeatletter
+\def\@maketitle{%
+  \newpage
+  \null
+  %\vspace{-1.5em}%
+  \begin{center}%
+    \let \footnote \thanks
+    {\Large \bfseries \@title \par}%
+    \vskip 1.5em%
+    {\large
+      \lineskip 0.5em%
+      \begin{tabular}[t]{c}%
+        \@author
+      \end{tabular}\par}%
+    \vskip 0.5em%
+    {\large \@date}%
+  \end{center}%
+  \par
+  \vskip 1em
+}
+\makeatother
+
+% redefine abstract environment
+\makeatletter
+\renewenvironment{abstract}{%
+  \if@twocolumn
+    \section*{\abstractname}%
+  \else %% <- here removed \small
+    \begin{center}%
+      {\bfseries \large\abstractname\vspace{\z@}} %% <- here added \large
+    \end{center}%
+    \quotation
+  \fi}{
+  \if@twocolumn\else\endquotation\fi
+}
+\makeatother
 
@@
 
-%\author{Author A, Author B, and J. E. Smith\thanks{Corresponding author (\textit{E-mail address:} \texttt{xyz@math.univ.edu}).} }
+\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
+\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
+\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
+%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
+\affil[1]{Department of Mathematics, \LaTeX\ University}
+\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
 
-\author{
-  Author A \\
-  {\itshape Department of Computer Science, \LaTeX\ University} \\
-  \and
-  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
-  {\itshape Department of Mathematics, \LaTeX\ University} \\
-  \and
-  Author C\thanks{This author was supported in part by NSF Grant No. 12345678.} \\
-  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
-}
-
-\date{\today}
+\date{Date: \today}
 
@@
   \item item two
-  %\item item three
 \end{itemize}
@@
   \item item two
-  %\item item three
 \end{enumerate}
@@
 
-We interleave text filler with some example theorems and theorem-like items.
+We interleave text filler with some example theorems and theorem-like
+items.
 
@@
 
-%LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
-%LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
+LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
+LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
 
@@
 
-Some discussions here. Some discussions here. Some discussions here.
-Some discussions here. Some discussions here. Some discussions here.
-Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
 
-Some discussions here. Some discussions here. Some discussions here.
-Some discussions here. Some discussions here. Some discussions here.
-Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
 
@@
 
-Some conclusions here. Some conclusions here. Some conclusions here.
-Some conclusions here. Some conclusions here. Some conclusions here.
-Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
 
-Some conclusions here. Some conclusions here. Some conclusions here.
-Some conclusions here. Some conclusions here. Some conclusions here.
-Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
 

### 2023-05-09 response-letter/Review-Report.tex
update

% Review report

\documentclass{article}
\usepackage{amsthm,amsmath,amssymb}
\usepackage{bm,mathrsfs}
\usepackage{graphicx}
\usepackage{color,xcolor}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{geometry}
\geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}

\renewcommand{\baselinestretch}{1.5}
\pagenumbering{gobble}
%\pagestyle{plain}

% information of paper
\title{Review Report on \\
``This is the title of the journal article"
}
\author{by Reviewer}
\date{}

\begin{document}

\maketitle

This article is devoted to developing a new method for the model equation.
This manuscript aims to give upper and lower bounds for the posterior error estimate.
The goal of this manuscript is to provide comprehensive information on the topic.
The results obtained in this manuscript are very meaningful, providing valuable insights into the development of the XXX method for the model equation.
The main contributions of this paper are: (1) The first innovation of the paper; (2) The second innovation of the paper.

The reviewer has the following comments.

\begin{enumerate}[label={\arabic*.}]
\item Page 2, Line 12: ``Expression A" should be ``Expression B";
\item Page 3, Line 5: The notation ``$u(t)$" should be ``$\tilde{u}(t)$";
\item Page 5, Line 8: The value ranges for the parameter $C$ in equation (2.1) is not clear, please give a little more detail about it.
\item Page 8, Line 4: It should be added a comma.
\item Page 10, Line $-2$:  The function $f(x)=b$ contradicts with the definition of $f(x)=a$.
\end{enumerate}

\end{document}

### 2023-05-26 article-en/article-temp-header.tex
update

@@
 \titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
-\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}
+\titleformat{\subsubsection}{\normalfont\itshape}{\normalfont\thesubsubsection.}{1.2ex}{}
+
+% hyperlink setting
+\hypersetup{
+  colorlinks = true,
+  linkcolor = magenta,
+  citecolor = blue,
+  filecolor = blue,
+  urlcolor = blue,
+}
 
@@
 %\fancyhf{}
-%\fancyhead[CO]{\uppercase{Title of Paper}}
-%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
-%\fancyfoot[C]{\thepage}
+%\fancyhead[CO]{\footnotesize\uppercase{Title of Paper}}
+%\fancyhead[CE]{\footnotesize\uppercase{Author A, Author B \& Author C}}
+%\fancyfoot[C]{\footnotesize\thepage}
 %\renewcommand{\headrulewidth}{0pt}
 
-%\fancyhead[C]{\uppercase{Title of Paper}}
-%\fancyfoot[C]{\thepage}
+%\fancyhead[C]{\footnotesize\uppercase{Title of Paper}}
+%\fancyfoot[C]{\footnotesize\thepage}
 %\renewcommand{\headrulewidth}{0pt}
@@
 \fancyhf{}
-\fancyhead[CO]{\@shorttitle}
-\fancyhead[CE]{\@shortauthor}
-\fancyhead[RO]{\thepage}
-\fancyhead[LE]{\thepage}
+\fancyhead[CO]{\footnotesize\MakeUppercase{\@shorttitle}}
+\fancyhead[CE]{\footnotesize\MakeUppercase{\@shortauthor}}
+\fancyhead[RO]{\footnotesize\thepage}
+\fancyhead[LE]{\footnotesize\thepage}
+\renewcommand{\headrulewidth}{0pt}
 \makeatother
@@
 
-\shorttitle{Short Title of Article}
-\shortauthor{Author A, Author B, and Author C}
+% Short title for running heads:
+\shorttitle{A posteriori error analysis for CG methods for PDDEs}
 
-\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
-\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
-\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
-%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
+\author[1]{Author A}
+\author[2]{Author B}
+\author[1]{Author C\thanks{Email address: \texttt{xyz@math.univ.edu}; Corresponding author.}}
 \affil[1]{Department of Mathematics, \LaTeX\ University}
 \affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
+
+% Short list of authors for running heads:
+\shortauthor{Author A, Author B, and Author C}
 
@@
 
+% References
 \bibliographystyle{plain}
@@
 
+\phantomsection
+\addcontentsline{toc}{section}{\refname}
 \bibliography{reference}

### 2023-06-06 article-en/article-temp-info.tex
update

--- 2023-05-26 article-en/article-temp-header.tex
@@
 \hypersetup{
-  colorlinks = true,
-  linkcolor = magenta,
-  citecolor = blue,
-  filecolor = blue,
-  urlcolor = blue,
+  colorlinks=true,
+  linkcolor=magenta,
+  citecolor=blue,
+  filecolor=blue,
+  urlcolor=blue
 }
@@
 \geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}
+\setlength{\headheight}{18pt}
+\setlength{\headsep}{18pt}
+\setlength{\footskip}{25pt}
 %\setlength{\textwidth}{15cm}
@@
 
+% define some new commands
 \makeatletter
-\newcommand\@shorttitle{}
+\newcommand\cortext[1]{\def\@cortext{#1}}
 \newcommand\shorttitle[1]{\def\@shorttitle{#1}}
-\newcommand\@shortauthor{}
 \newcommand\shortauthor[1]{\def\@shortauthor{#1}}
@@
 
+\newcommand\cormark{\raisebox{-1.6pt}{*}}
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  %\addtocounter{footnote}{-1}%
+  \endgroup
+}
+
 % headers and footers setting
-%\pagestyle{fancy}
-%\fancyhf{}
-%\fancyhead[CO]{\footnotesize\uppercase{Title of Paper}}
-%\fancyhead[CE]{\footnotesize\uppercase{Author A, Author B \& Author C}}
-%\fancyfoot[C]{\footnotesize\thepage}
-%\renewcommand{\headrulewidth}{0pt}
-
-%\fancyhead[C]{\footnotesize\uppercase{Title of Paper}}
-%\fancyfoot[C]{\footnotesize\thepage}
-%\renewcommand{\headrulewidth}{0pt}
-
 \makeatletter
@@
 \fancyhf{}
-\fancyhead[CO]{\footnotesize\MakeUppercase{\@shorttitle}}
-\fancyhead[CE]{\footnotesize\MakeUppercase{\@shortauthor}}
+\fancyhead[CO]{\footnotesize\MakeUppercase{\ifx\@shorttitle\undefined{}\else\@shorttitle\fi}}
+\fancyhead[CE]{\footnotesize\MakeUppercase{\ifx\@shortauthor\undefined{}\else\@shortauthor\fi}}
 \fancyhead[RO]{\footnotesize\thepage}
@@
     \let \footnote \thanks
-    {\Large \bfseries \@title \par}%
+    {\Large \bfseries \@title \ifx\@cortext\undefined{}\else\blfootnote{\@cortext}\fi \par}%
     \vskip 1.5em%
@@
 % Short title for running heads:
-\shorttitle{A posteriori error analysis for CG methods for PDDEs}
+\shorttitle{Short Title of the Article}
 
@@
 \author[2]{Author B}
-\author[1]{Author C\thanks{Email address: \texttt{xyz@math.univ.edu}; Corresponding author.}}
+\author[1,\cormark]{Author C}
 \affil[1]{Department of Mathematics, \LaTeX\ University}
 \affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
+\cortext{Corresponding author. Email address: \texttt{xyz@math.univ.edu}}
 

### 2023-06-12 note-temp/compile-pdflatex-en.sh
update

@@ -1,16 +1,0 @@
-#!/bin/bash
-
-#-> Get source filename
-find . -maxdepth 1 -type f -name "*en.tex" | while read FileName; do 
-#--- Process FileName.tex ---
-echo "$FileName"
-echo "${FileName%.tex}"
-#-> Compile the main file
-pdflatex --synctex=-1 "$FileName"
-bibtex "${FileName%.tex}"
-pdflatex --synctex=-1 "$FileName"
-pdflatex --synctex=-1 "$FileName"
-#-> Clear aux files
-rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
-done
-

### 2023-06-12 note-temp/compile-xelatex-cn.sh

@@ -1,17 +1,0 @@
-#!/bin/bash
-
-#-> Get source filename
-find . -maxdepth 1 -type f -name "*cn.tex" | while read FileName;
-do 
-#--- Process FileName.tex ---
-echo "$FileName"
-echo "${FileName%.tex}"
-#-> Compile the main file
-xelatex --synctex=-1 "$FileName"
-bibtex "${FileName%.tex}"
-xelatex --synctex=-1 "$FileName"
-xelatex --synctex=-1 "$FileName"
-#-> Clear aux files
-rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
-done
-

### 2023-09-02 article-en/article-temp.tex
update

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage{subfig}
 % package for hyperlink
@@
 \geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}
+%\setlength{\headheight}{18pt}
+%\setlength{\headsep}{18pt}
+\setlength{\footskip}{25pt}
 %\setlength{\textwidth}{15cm}
@@
   \medskip
-  \noindent{\bf Keywords}: Example, \LaTeX, numerical methods
+  \noindent{\bfseries Keywords}: Example, \LaTeX, numerical methods
 
   \medskip
-  \noindent{\bf 2000 Mathematics Subject Classification: } 65L60, 65L05, 65L70.
+  \noindent{\bfseries Mathematics Subject Classification:}  65M60, 65M12.
 \end{abstract}
@@
   \centering
-  \includegraphics[width=0.48\linewidth]{fig1}
+  \includegraphics[width=0.46\linewidth]{fig1}
   \caption{Example figure using external image files.}
@@
   \includegraphics[width=0.45\linewidth]{fig1}
-  \hfill
+  \qquad
   \includegraphics[width=0.45\linewidth]{fig2}
@@
 \Xhline{2\arrayrulewidth}
-N  & A       & B    & C       & D      & E     \\
+$N$  & A       & B    & C       & D      & E     \\
 \Xhline{2\arrayrulewidth}
@@
 Use \texttt{minipage} package to set images side-by-side, each with its own title, as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
+
 \begin{figure}[htp!]
@@
 
+Use \texttt{subfig} package to set subfigure, each with its subcaption, as shown in Figure~\ref{fig:twosubfig}.
+
+\begin{figure}[htp!]
+\centering
+\subfloat[Subcaption A]{\includegraphics[width=0.46\linewidth]{fig1}}
+\qquad
+\subfloat[Subcaption B]{\includegraphics[width=0.46\linewidth]{fig2}}
+\caption{Two subfigures}
+\label{fig:twosubfig}
+\end{figure}
+
 Additional results are available in the supplement in Table~\ref{tab:foo}.
@@
 \hline
-   &  1/128    & 9.18E-06    &2.02    & 7.70E-03  &1.01       & 6.46E-07    &2.02   \\
-1  &  1/256    & 2.29E-06    &2.01    & 1.92E-03  &1.00       & 1.61E-07    &2.01   \\
-   &  1/512    & 5.70E-07    &2.00    & 9.56E-04  &1.00       & 4.01E-08    &2.00   \\
+  & 1/128 & 9.18E-06 & 2.02 & 7.70E-03 & 1.01 & 6.46E-07 & 2.02 \\
+1 & 1/256 & 2.29E-06 & 2.01 & 1.92E-03 & 1.00 & 1.61E-07 & 2.01 \\
+  & 1/512 & 5.70E-07 & 2.00 & 9.56E-04 & 1.00 & 4.01E-08 & 2.00 \\
 \hline  % \cline{1-8}
-   &  1/128    & 1.39E-08    &3.01    & 1.15E-05  &2.01       & 3.48E-12   &4.02    \\
-2  &  1/256    & 1.73E-09    &3.01    & 2.88E-06  &2.01       & 3.27E-13   &3.94    \\
-   &  1/512    & 2.17E-10    &3.00    & 7.24E-06  &2.00       & 6.66E-13   &1.55    \\
+  & 1/128 & 1.39E-08 & 3.01 & 1.15E-05 & 2.01 & 3.48E-12 & 4.02 \\
+2 & 1/256 & 1.73E-09 & 3.01 & 2.88E-06 & 2.01 & 3.27E-13 & 3.94 \\
+  & 1/512 & 2.17E-10 & 3.00 & 7.24E-06 & 2.00 & 6.66E-13 & 1.55 \\
 \hline  % \cline{1-8}
-   &  1/32     & 2.28E-09    &4.05    & 6.92E-07  &3.04       & 1.45E-15   &8.21    \\
-3  &  1/64     & 1.42E-10    &4.03    & 8.65E-08  &3.02       & 2.06E-14   &3.85    \\
-   &  1/128    & 8.91E-12    &4.01    & 1.08E-08  &3.01       & 3.86E-14   &0.91    \\
+  & 1/32  & 2.28E-09 & 4.05 & 6.92E-07 & 3.04 & 1.45E-15 & 8.21 \\
+3 & 1/64  & 1.42E-10 & 4.03 & 8.65E-08 & 3.02 & 2.06E-14 & 3.85 \\
+  & 1/128 & 8.91E-12 & 4.01 & 1.08E-08 & 3.01 & 3.86E-14 & 0.91 \\
 \hline
@@
 
-Some discussions here. Some discussions here. Some discussions here.
-Some discussions here. Some discussions here. Some discussions here.
-Some discussions here. Some discussions here.
-
 \section{Conclusions}
@@
 Some conclusions here.
-
-Some conclusions here. Some conclusions here. Some conclusions here.
-Some conclusions here. Some conclusions here. Some conclusions here.
-Some conclusions here. Some conclusions here.
 
@@
 
-\bibliographystyle{plain}
-%\bibliographystyle{abbrv}
+%\bibliographystyle{plain}
+\bibliographystyle{abbrv}
 

### 2023-10-08 cover-letter/Cover-Letter2.tex
update

--- 2022-10-27 cover-letter/cover_letter2.tex
@@
-% LaTeX Cover Letter Template
+% LaTeX cover letter template
 
-\documentclass[a4paper]{article}
+\documentclass[11pt]{article}
 
+% all kinds of packages needed
 \usepackage[utf8]{inputenc}
-\usepackage{fullpage}
-%\usepackage{geometry}
-%\geometry{margin=1.25in}
-%showframe  % Uncomment to show frames around the margins
-
-% Default font family: sans serif
-%\usepackage{helvet}
-%\renewcommand{\familydefault}{\sfdefault}
-
-\pagenumbering{gobble} % No page numbering
-
 \usepackage{amsmath,amsthm,amssymb}
-\usepackage{amsfonts,bm,version}
-\usepackage{graphicx,fancybox,mathrsfs}
+\usepackage{bm,mathrsfs}
+\usepackage{graphicx}
 \usepackage{color,xcolor}
 \usepackage{mathtools}
-\usepackage{enumerate}
+\usepackage{enumitem}
 \usepackage{caption}
-\allowdisplaybreaks
+\usepackage{geometry}
+\geometry{left=1.25in,right=1.25in,top=1in,bottom=1in}
 
@@
 
-\usepackage{fancyhdr}       % Required for customizing headers and footers
+% allow page breaks between multiline formulas
+\allowdisplaybreaks
 
-\fancypagestyle{main}{%
-	\fancyhf{} % Clear default headers/footers
-	\renewcommand{\headrulewidth}{0pt} % No header rule
-	\renewcommand{\footrulewidth}{0.5pt} % Footer rule thickness
-}
-%\pagestyle{main}
+% command for line spacing
+\renewcommand{\baselinestretch}{1.1}
 
@@
 
-%----------------------------------------------------------------------------------------
+% package for header and footer
+\usepackage{fancyhdr}
+
+\fancypagestyle{firstpage}{%
+	\fancyhf{} % Clear default headers/footers
+	\renewcommand{\headrulewidth}{0pt} % No header rule
+	\renewcommand{\footrulewidth}{1pt} % Footer rule thickness
+}
+
+\fancypagestyle{subsequentpages}{%
+	\fancyhf{} % Clear default headers/footers
+	\renewcommand{\headrulewidth}{1pt} % Header rule thickness
+	\renewcommand{\footrulewidth}{1pt} % Footer rule thickness
+}
+
+\AtBeginDocument{\thispagestyle{firstpage}} % Use the first page headers/footers style on the first page
+\pagestyle{subsequentpages} % Use the subsequent pages headers/footers style on subsequent pages
+
+%-----------------------------------------------------
 
@@
 
-%----------------------------------------------------------------------------------------
+%-----------------------------------------------------
 %	First page header
-%----------------------------------------------------------------------------------------
+%-----------------------------------------------------
 
@@
 
-\vspace{-1em}
+\vspace{-1em} % Pull the rule closer to the logo
 
-\rule{\linewidth}{0.5pt} % Horizontal rule
+\rule{\linewidth}{1pt} % Horizontal rule
 
-\vskip2.5em
+\vspace{1.5em} % Vertical whitespace
 
-%----------------------------------------------------------------------------------------
-%	Your information
-%----------------------------------------------------------------------------------------
+%-----------------------------------------------------
+%	YOUR NAME AND CONTACT INFORMATION
+%-----------------------------------------------------
 
@@
 \begin{tabular}{l @{}}
-	\textbf{XX research group} \\
-    \textbf{Department of Mathematics} \\
-    University of XXXX \\
-    XX Building, XX Road \\
-	City 200123, P. R. China. \\[10pt] % Address
-    \textbf{Dr. Who} \\
-	Email: xxx@univ.edu.cn \bigskip \\
-    \today \\ % Date
+	\today \bigskip\\ % Date
+	XXX \\
+	Address 1 \\ % Address
+	Address 2 \\
+	Phone: +86 123-4567 \\
+	Email: xxx@univ.edu.cn
 \end{tabular}
@@
 
-\bigskip
+%-----------------------------------------------------
+%	ADDRESSEE AND GREETING
+%-----------------------------------------------------
 
-%Dear Mrs.\ XXX,
-Dear Editor,
+\begin{tabular}{@{} l}
+	Mr.\ XXX \\
+	Recruitment Officer \\
+	The Corporation \\
+	123 Pleasant Lane \\
+	City, State 12345
+\end{tabular}
 
@@
 
-%----------------------------------------------------------------------------------------
-%	Letter body
-%----------------------------------------------------------------------------------------
+Dear Mrs.\ XXX,
 
-Please find attached the manuscript ``PAPER TITLE" by Author A and Author B for consideration as a Research Article in XX.
+\bigskip
 
-Our work builds on the considerable interest of the scientific community in XXX [cite]. This  is more impressing especially since the XX were recently experimentally demonstrated [cite].
+%-----------------------------------------------------
+%	LETTER CONTENT
+%-----------------------------------------------------
 
-Hitherto, XX have increasingly been investigated [cite]. However, the ``missing component" has  been XXX. XXX will enable future XXX.
+PARAGRAPH ONE: State the reason for the letter, name the position or type of work you are applying for and identify the source from which you learned of the opening (i.e.
+career development center, newspaper, employment service, personal contact).
 
-In this paper, we XXX.
+PARAGRAPH TWO: Indicate why you are interested in the position, the company, its products, services - above all, stress what you can do for the employer.
+If you are a recent graduate, explain how your academic background makes you a qualified candidate for the position.
+If you have practical work experience, point out specific achievements or unique qualifications.
+Try not to repeat the same information the reader will find in the resume.
+Refer the reader to the enclosed resume or application which summarizes your qualifications, training, and experiences.
+The purpose of this section is to strengthen your resume by providing details which bring your experiences to life.
 
-We are convinced that this work will have implications for XXX.
-As such, the research should  appeal to a broad audience interested in XXX.
-We thus believe that the manuscript is  appropriate for the readership of XX.
+PARAGRAPH THREE: Request a personal interview and indicate your flexibility as to the time and place.
+Repeat your phone number in the letter and offer assistance to help in a speedy response.
+For example, state that you will be in the city where the company is located on a certain date and would like to set up an interview.
+Alternatively, state that you will call on a certain date to set up an interview.
+End the letter by thanking the employer for taking time to consider your credentials.
 
-We remain at your disposal for any further questions.
+PARAGRAPH FOUR: Enclosed, please find my resume, which provides a comprehensive overview of my qualifications, academic background, and professional experiences.
+I believe my achievements in [mention a significant accomplishment or role relevant to the position] demonstrate my ability to [mention a key skill or competency needed for the job].
+Rather than repeating the details found in my resume, I invite you to review it for a more in-depth understanding of my qualifications.
 
-\bigskip %
+\bigskip
 
@@
 
-%\vspace{25pt} %
+%\medskip
 

### 2023-10-16 amsart-en/amsart-temp.tex
update

@@
 
-\subjclass[2000]{65L60, 65L05, 65L70}
+\subjclass[2000]{65M60, 65M12}
 
@@
 The introduction introduces the context and summarizes the manuscript.
-It is importantly to clearly state the contributions of this piece of work.
+It is important to clearly state the contributions of this piece of work.
 
@@
 The two figures are placed side by side, sharing one title, as shown in \autoref{fig:twofigs}.
+
 \begin{figure}[htp!]
@@
 12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
+%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
 %16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
@@
 
+Some description and explanation about figures and tables.
+
 Use \texttt{minipage} package to set images side-by-side, each with its own title,
 as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
+
 \begin{figure}[htp!]

### 2023-10-16 amsart-en/amsart-temp2.tex
update

@@
 
-\author{author A$^1$ and author B$^{1,*}$}
-\address{$^1$common address of authors A and B}
+\author[Author A]{Author A$^{1}$}
+\author[Author B]{Author B$^{2}$}
+\author[Author C]{Author C$^{1,*}$}
+\address{$^{1}$Common address of authors A and B}
+\address{$^{2}$author C address}
 
-\author{author C$^{2}$}
-\address{$^2$author C address}
+%\author[Author A, Author B]{Author A$^{1}$, Author B$^{1,*}$}
+%\address{$^{1}$common address of authors A and B}
+%\author[Author C]{Author C$^{2}$}
+%\address{$^{2}$author C address}
 
@@
 
-\thanks{${}^{*}$Corresponding author.}
-\thanks{The first author was supported in part by NSF Grant \#000000.}
+\thanks{${}^{*}$Corresponding author}
+\thanks{The first author was supported in part by NSFC Grant \#000000.}
 \thanks{Support information for the second author.}
@@
 
+\clearpage
 \textbf{Some figures and tables here.}
@@
 
+Some description and explanation of pictures and tables
+
 Use \texttt{minipage} package to set images side-by-side, each with its own title,
 as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
+
 \begin{figure}[htp!]
@@
 %\bibliographystyle{abbrv}
+%\bibliographystyle{amsplain}
 

### 2023-10-16 article-en/article-temp.tex
update

@@
 % Information for title and author
-\title{An Example Article\thanks{The work is supported in part by NSF Grant No. 12345678 and ...}}
+\title{An Example Article\thanks{The work is supported in part by NSFC Grant No. 12345678 and ...}}
 
@@
 The introduction introduces the context and summarizes the
-manuscript. It is importantly to clearly state the contributions of
+manuscript. It is important to clearly state the contributions of
 this piece of work.

### 2023-10-16 article-en/article-temp2.tex
update

@@
   \and
-  Author C\thanks{This author was supported in part by NSF Grant No. 12345678.} \\
+  Author C\thanks{This author was supported in part by NSFC Grant No. 12345678.} \\
   {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
@@
 
-Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here.Some experimental results here.
+Some experimental results here. %Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here.Some experimental results here.
 
@@
 6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
+%8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
+%10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
+%12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
 %14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\

### 2023-10-16 article-en/article-temp3.tex
update

@@
 \titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
-\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}
+\titleformat{\subsubsection}{\normalfont\itshape}{\normalfont\thesubsubsection.}{1.2ex}{}
 
@@
 %\fancyhf{}
-%\fancyhead[CO]{\uppercase{Title of Paper}}
-%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
-%\fancyfoot[C]{\thepage}
+%\fancyhead[CO]{\footnotesize\uppercase{Title of Paper}}
+%\fancyhead[CE]{\footnotesize\uppercase{Author A, Author B \& Author C}}
+%\fancyfoot[C]{\footnotesize\thepage}
 %\renewcommand{\headrulewidth}{0pt}
 
-%\fancyhead[C]{\uppercase{Title of Paper}}
-%\fancyfoot[C]{\thepage}
+%\fancyhead[C]{\footnotesize\uppercase{Title of Paper}}
+%\fancyfoot[C]{\footnotesize\thepage}
 %\renewcommand{\headrulewidth}{0pt}
 
-%\fancyhead[CO]{\uppercase{Title of Paper}}
-%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
-%\fancyhead[RO]{\thepage}
-%\fancyhead[LE]{\thepage}
+%\fancyhead[CO]{\footnotesize\uppercase{Title of Paper}}
+%\fancyhead[CE]{\footnotesize\uppercase{Author A, Author B \& Author C}}
+%\fancyhead[RO]{\footnotesize\thepage}
+%\fancyhead[LE]{\footnotesize\thepage}
 
@@
 
-\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
+\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}}}
 \author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
-\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
+\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}; Corresponding author.}}
 %\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
@@
   \medskip
-  \noindent{\bf Keywords}: Example, \LaTeX, numerical methods
+  \noindent{\bfseries Keywords}: Example, \LaTeX, numerical methods
 
   \medskip
-  \noindent{\bf 2000 Mathematics Subject Classification: } 65L60, 65L05, 65L70.
+  \noindent{\bfseries Mathematics Subject Classification:} 65M60, 65M12.
 \end{abstract}
@@
 
-Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
-
-Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here. Some discussions here.
+Some discussions here. Some discussions here.
 
@@
 
-Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
-
-Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here. Some conclusions here. Some conclusions here.
+Some conclusions here.
 

### 2024-01-09 amsart-en/amsart-temp.tex
update

@@
 % package for bibliography support
-\usepackage[numbers,sort&compress]{natbib}
+\usepackage{cite}
+%\usepackage[numbers,sort&compress]{natbib}
 
@@
 \begin{abstract}
-  This is an example \LaTeX\ article. This can be used as a
-  template for new articles.  Abstracts must be able to stand alone
-  and so cannot contain citations to the paper's references,
-  equations, etc.  An abstract must consist of a single paragraph and
-  be concise. Because of online formatting, abstracts must appear as
-  plain as possible. Any equations should be inline.
+This is an example \LaTeX\ article. This can be used as a template for new articles.
+Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
+An abstract must consist of a single paragraph and be concise.
+Because of online formatting, abstracts must appear as plain as possible.
+Any equations should be inline.
 \end{abstract}
@@
 \section{Introduction}
+
 The introduction introduces the context and summarizes the manuscript.
@@
 
-The paper is organized as follows. Our main results are in
-\ref{sec:main}, our new algorithm is in \ref{sec:alg}, experimental
-results are in \ref{sec:experiments}, discussion is in \ref{sec:discussion}
-and the conclusions follow in \ref{sec:conclusions}.
+The paper is organized as follows. Our main results are in \ref{sec:main},
+our new algorithm is in \ref{sec:alg}, experimental results are in \ref{sec:experiments},
+discussion is in \ref{sec:discussion} and the conclusions follow in \ref{sec:conclusions}.
 
@@
 
-This is a citation example \cite{Adams2003}. This statement requires
-citation \cite{Shen1994,Tadmor2012,TreWei2014}.
+This is a citation example \cite{Adams2003,TreWei2014}.
+This statement requires citations \cite{Shen1994,Tadmor2012,TreWei2014}.
 
@@
 \begin{corollary}\label{cor:a}
-  Let $f(x)$ be continuous and differentiable everywhere. If $f(x)$
-  has at least two roots, then $f'(x)$ must have at least one root.
+  Let $f(x)$ be continuous and differentiable everywhere.
+  If $f(x)$ has at least two roots, then $f'(x)$ must have at least one root.
 \end{corollary}
@@
 \section*{Acknowledgments}
-We would like to acknowledge the assistance of volunteers in putting
-together this example manuscript and supplement.
+
+We would like to acknowledge the assistance of volunteers in putting together this example manuscript and supplement.
 

### 2024-01-09 amsart-en/amsart-temp2.tex
update

@@
 
+% hyperlink setting
+%\hypersetup{
+%  colorlinks=true,
+%  linkcolor=magenta,
+%  citecolor=blue,
+%  filecolor=blue,
+%  urlcolor=blue
+%}
+
 % package for bibliography support
-\usepackage[numbers,sort&compress]{natbib}
+\usepackage{cite}
+%\usepackage[numbers,sort&compress]{natbib}
 
@@
 \address{$^{1}$Common address of authors A and B}
-\address{$^{2}$author C address}
+\address{$^{2}$Author C address}
 
 %\author[Author A, Author B]{Author A$^{1}$, Author B$^{1,*}$}
-%\address{$^{1}$common address of authors A and B}
+%\address{$^{1}$Common address of authors A and B}
 %\author[Author C]{Author C$^{2}$}
-%\address{$^{2}$author C address}
+%\address{$^{2}$Author C address}
 
@@
 \begin{theorem}[$LDL^T$ Factorization \cite{GoVa2013}]\label{thm:bigthm}
-  If $A \in \mathbb{R}^{n \times n}$ is symmetric and the principal
-  submatrix $A(1:k,1:k)$ is nonsingular for $k=1:n-1$, then there
+  If $A \in \mathbb{R}^{n \times n}$ is symmetric and the principal submatrix $A(1:k,1:k)$ is nonsingular for $k=1:n-1$, then there
   exists a unit lower triangular matrix $L$ and a diagonal matrix
@@
 \begin{theorem}[Mean Value Theorem]\label{thm:mvt}
-  Suppose $f$ is a function that is continuous on the closed interval
-  $[a,b]$.  and differentiable on the open interval $(a,b)$.
+  Suppose $f$ is a function that is continuous on the closed interval $[a,b]$ and differentiable on the open interval $(a,b)$.
   Then there exists a number $c$ such that $a < c < b$ and
@@
 
-Some description and explanation of pictures and tables
+Some description and explanation of pictures and tables.
 

### 2024-01-09 article-en/article-temp-info.tex
update

@@
   \endgroup
+}
+\newcommand{\tfootnote}[1]{%
+  \textsuperscript{$\star$}%
+  {\renewcommand{\thefootnote}{$\star$}%
+  \footnotetext{#1}}
 }
@@
 % Information for title and author
-\title{An Example Article}
+\title{An Example Article\tfootnote{This is a title footnote}}
 
@@
 \begin{abstract}
-  This is an example \LaTeX\ article. This can be used as a
-  template for new articles.  Abstracts must be able to stand alone
-  and so cannot contain citations to the paper's references,
-  equations, etc.  An abstract must consist of a single paragraph and
-  be concise. Because of online formatting, abstracts must appear as
-  plain as possible. Any equations should be inline.
+This is an example \LaTeX\ article. This can be used as a template for new articles.
+Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
+An abstract must consist of a single paragraph and be concise.
+Because of online formatting, abstracts must appear as plain as possible.
+Any equations should be inline.
 
 \medskip
-  \noindent{\bf Keywords}: Example, \LaTeX, numerical methods
+\noindent{\bfseries Keywords}: Example, \LaTeX, numerical methods
 
 \medskip
-  \noindent{\bf 2000 Mathematics Subject Classification: } 65L60, 65L05, 65L70.
+\noindent{\bfseries Mathematics Subject Classification:} 65M60, 65M12.
 \end{abstract}
@@
 \section{Introduction}
-The introduction introduces the context and summarizes the
-manuscript. It is importantly to clearly state the contributions of
-this piece of work.
+
+The introduction introduces the context and summarizes the manuscript.
+It is important to clearly state the contributions of this piece of work.
 
@@
 
-The paper is organized as follows. Our main results are in
-\ref{sec:main}, our new algorithm is in \ref{sec:alg}, experimental
-results are in \ref{sec:experiments}, discussion is in \ref{sec:discussion} and the conclusions follow in
-\ref{sec:conclusions}.
+The paper is organized as follows. Our main results are in \ref{sec:main},
+our new algorithm is in \ref{sec:alg}, experimental results are in \ref{sec:experiments},
+discussion is in \ref{sec:discussion} and the conclusions follow in \ref{sec:conclusions}.
 
@@
 
-This is a citation example \cite{Adams2003}. This statement requires citation \cite{Shen1994,Tadmor2012,TreWei2014}.
+This is a citation example \cite{Adams2003,TreWei2014}.
+This statement requires citations \cite{Shen1994,Tadmor2012,TreWei2014}.
 
@@
 \begin{equation}\label{eq:matrices}
-S=\begin{bmatrix}1&0\\0&0\end{bmatrix}
+S=\begin{bmatrix}
+1 & 0 \\
+0 & 0
+\end{bmatrix}
 \quad\text{and}\quad
-C=\begin{pmatrix}1&1&0\\1&1&0\\0&0&0\end{pmatrix}.
+C=\begin{pmatrix}
+1 & 1 & 0 \\
+1 & 1 & 0 \\
+0 & 0 & 0
+\end{pmatrix}.
 \end{equation}
@@
 
-Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here.Some experimental results here.
+Some experimental results here. Some experimental results here.
+Some experimental results here. Some experimental results here.
+Some experimental results here.Some experimental results here.
 
@@
 \section*{Acknowledgments}
-We would like to acknowledge the assistance of volunteers in putting
-together this example manuscript and supplement.
+
+We would like to acknowledge the assistance of volunteers in putting together this example manuscript and supplement.
 
 % References
-\bibliographystyle{plain}
-%\bibliographystyle{abbrv}
+%\bibliographystyle{plain}
+\bibliographystyle{abbrv}
 

### 2024-01-09 article-en/article-temp.tex
update

@@
 \begin{abstract}
-  This is an example \LaTeX\ article. This can be used as a
-  template for new articles.  Abstracts must be able to stand alone
-  and so cannot contain citations to the paper's references,
-  equations, etc.  An abstract must consist of a single paragraph and
-  be concise. Because of online formatting, abstracts must appear as
-  plain as possible. Any equations should be inline.
+This is an example \LaTeX\ article. This can be used as a template for new articles.
+Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
+An abstract must consist of a single paragraph and be concise.
+Because of online formatting, abstracts must appear as plain as possible.
+Any equations should be inline.
 
@@
 \section{Introduction}
-The introduction introduces the context and summarizes the
-manuscript. It is important to clearly state the contributions of
-this piece of work.
+
+The introduction introduces the context and summarizes the manuscript.
+It is important to clearly state the contributions of this piece of work.
 

### 2024-01-09 article-en/article-temp2.tex
update

@@
 
-Some experimental results here. %Some experimental results here. Some experimental results here. Some experimental results here. Some experimental results here.Some experimental results here.
+Some experimental results here. Some experimental results here.
+%Some experimental results here. Some experimental results here.
+%Some experimental results here.Some experimental results here.
 

### 2024-04-03 response-letter/Response-Letter3.tex
update

% LaTeX response letter template

\documentclass[11pt]{article}

% all kinds of packages needed
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{bm,mathrsfs}
\usepackage{graphicx}
\usepackage{color,xcolor}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{geometry}
\geometry{left=1.25in,right=1.25in,top=1in,bottom=1in}

% allow page breaks between multiline formulas
\allowdisplaybreaks

% command for listsep
\setlist{nolistsep}
\setlist[itemize]{itemsep=3pt}
\setlist[enumerate]{itemsep=3pt}

% command for line spacing
\renewcommand{\baselinestretch}{1.2}

% define counters for reviewers and their points
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% package for section etc.
%\usepackage{titlesec}
%\titleformat{\section}{\large\bfseries}{\thesection}{}{}
%\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection}{}{}

% command declarations for reviewer comments and our responses
\newcommand{\reviewersection}{%
\stepcounter{reviewer}\vskip 16pt \hrule height 0.6pt%
\section*{Reviewer~\thereviewer}%
}

% define color
\definecolor{lightred}{RGB}{216,144,144}
\definecolor{slightred}{RGB}{251,243,243}
\definecolor{slightgreen}{RGB}{243,248,243}

% Referee Comments
\usepackage[most]{tcolorbox}
\tcbuselibrary{breakable,skins}
%\newtcolorbox{commentbox}{
%  blanker, breakable, left=1em,
%  top=0.5em, bottom=0.5em,
%  borderline west={2pt}{0pt}{gray!75!white},
%  colback = {lightred}
%}
\newtcolorbox{commentbox}{
  enhanced, frame hidden, breakable, sharp corners,%
  leftrule=0pt, rightrule=0pt, toprule=0pt, bottomrule=0pt,%
  boxsep=2pt, top=0.5em, bottom=0.5em, left=0.5em, right=0.5em,%
  before skip=1.0em, after skip=1.0em,
  borderline west={2pt}{0pt}{lightred}, %gray!75!white
  colframe=gray, colback = {slightred}
}

\newtcolorbox{changebox}{
  enhanced, frame hidden, breakable, sharp corners,%
  leftrule=0pt, rightrule=0pt, toprule=0pt, bottomrule=0pt,%
  boxsep=2pt, top=0.5em, bottom=0.5em, left=0.5em, right=0.5em,%
  before skip=0.75em, after skip=0.75em,
  colframe=gray, colback = {slightgreen}
}

% define the point environment
\newenvironment{point}[1][Comment]{%
  \refstepcounter{point}%
  \noindent\textbf{#1~\arabic{point}}%
  \begin{commentbox}
  %\color{gray!40!black}
}{%
  \end{commentbox}
}

% define the block environment
\newenvironment{block}[1][]{%
  \noindent\textbf{#1}%
  \begin{commentbox}
  %\color{gray!40!black}
}{%
  \end{commentbox}
}

% package for underlining
\usepackage[normalem]{ulem}
\newcommand{\deleted}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\added}[1]{\textcolor{blue}{\uwave{#1}}}

% define maketitle environment
\makeatletter
\def\@maketitle{%
  \newpage
  \null
  \vskip 0.5em%
  \leftline{Reply to the review report on}
  \vskip 1.5em%
  \begin{center}%
  \let \footnote \thanks
    {\Large \bfseries \@title \par}%
    \vskip 1.5em%
    {\large
      \lineskip .5em%
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 1em%
    {\large \@date}%
  \end{center}%
  \par
  \vskip 1.0em}
\makeatother

% graphical path
\graphicspath{{./figures/}}

% differential operator
\newcommand{\dif}{\mathop{}\!\mathrm{d}}

% new command
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
\newcommand{\ii}{\mathrm{i}\mkern1mu}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}

% information for title and author
\title{Journal-001: The full title of the submitted paper}
\author{by \quad Author A ~ and ~ Author B}
\date{\today}

\begin{document}

\maketitle

% Simple title
%\begin{center}
%{\bfseries\LARGE Response to Reviewers}
%\end{center}
%\section*{Response to Reviewer Comments}

% General intro text goes here
The authors thank the reviewers for their critical assessment of our work.
In the following we address their concerns point by point.

% New reviewer section
\reviewersection

% Comments to the authors
\begin{block}[Comments to the authors]
This is comments of Reviewer \thereviewer. With some more words foo bar foo bar ...
\begin{enumerate}
  \item Point one
  \item Point two
  %\item Point three
\end{enumerate}
Suggestion: it's better to test a case with ...
\end{block}

% Our reply
\noindent\textbf{Author response}
\par\smallskip%

We agree with the reviewer on this point. This is what we did to fix it.
\begin{enumerate}
  \item Reply one
  \item Reply two
  %\item Reply three
\end{enumerate}
\begin{equation}\label{eq:abc}
  a^2+b^2=c^2.
\end{equation}
Please see Page 5 line 10 of the revised version.

\medskip

\noindent\textbf{Changes}

\begin{changebox}
Changes made in the manuscript. Overkill if you also add track changes. To add a track-changes version of the two manuscripts, run \texttt{latexdiff} on the original + revised paper. Goolge latexdiff tutorial to see how that works. Once you do that, you can copy-paste code from the file highlighting difference directly in here. For instance:

\begin{quotation}
Our results indicate that \added{increasing} \deleted{decreasing} the temperature leads to a \added{significant} \deleted{negligible} increase in the growth rate of \added{E. coli} \deleted{bacteria}.
\end{quotation}

\end{changebox}

\clearpage

% New reviewer section
\reviewersection

% comment 1
\begin{point}[Comment]
This is comment 1 of Reviewer \thereviewer.
\end{point}

\noindent\textbf{Reply:} \\[3pt]
Our reply to This is comment 1 of Reviewer \thereviewer.

\medskip

\noindent\textbf{Changes:}

\begin{changebox}
Lots of very important changes
\end{changebox}

\medskip

% comment 2
\begin{point}[Comment]
This is comment 2 of Reviewer \thereviewer. With some more words foo bar foo bar ...
\end{point}

\noindent\textbf{Reply:} \\[3pt]
Our reply to it with reference to one of our points above using the {\LaTeX}'s label/ref system (see also \ref{eq:abc}).

\medskip

\noindent\textbf{Changes:}

\begin{changebox}
So we did not change absolutely anything on this point.
\end{changebox}

% New reviewer section
% \reviewersection

\end{document}

### 2024-08-22 amsart-en/amsart-journal.tex
update

--- 2024-01-09 amsart-en/amsart-temp2.tex
@@
 \usepackage{algpseudocode}
+% refinements for typographical perfection
+\usepackage{microtype}
 % package for using box and verbatim
-\usepackage{fancybox}
-% package for address
-\usepackage[foot]{amsaddr}
+%\usepackage{fancybox}
 
@@
 
-\author[Author A]{Author A$^{1}$}
-\author[Author B]{Author B$^{2}$}
-\author[Author C]{Author C$^{1,*}$}
-\address{$^{1}$Common address of authors A and B}
-\address{$^{2}$Author C address}
+\author[Author A]{Author A}
+\address{Address of author A}
+\curraddr{Current address of author A}
+\email{xyz@math.university.edu}
 
-%\author[Author A, Author B]{Author A$^{1}$, Author B$^{1,*}$}
-%\address{$^{1}$Common address of authors A and B}
-%\author[Author C]{Author C$^{2}$}
-%\address{$^{2}$Author C address}
+\author[Author B]{Author B}
+\address{Address of author B}
+\curraddr{Current address of author B}
+\email{two@math.univ.edu}
 
-\email{list of emails}
+\author[Author C]{Author C}
+\address{Address of author C}
+\curraddr{Current address of author C}
+\email{three@univ.edu.com}
 
-\thanks{${}^{*}$Corresponding author}
 \thanks{The first author was supported in part by NSFC Grant \#000000.}
@@
 \thanks{Support information for the third author.}
+\thanks{The third author is the corresponding author.}
+%\thanks{${}^{*}$Corresponding author}
 
@@
 \date{\today}
+
+\dedicatory{This paper is dedicated to our advisors.}
 
@@
   \item item two
-  %\item item three
+  \item item three
 \end{itemize}
@@
   \item item two
-  %\item item three
+  \item item three
 \end{enumerate}
@@
 \begin{algorithm}[H]
-\caption{Euclid’s algorithm}
+\caption{Euclid's algorithm}
 \label{alg:euclid}
@@
 
-Use the \texttt{tabularx} environment to generate \autoref{tab:error}.
+Use the \texttt{tabular} environment to generate \autoref{tab:foo}.
+The commands \verb|\tabcolsep| and \verb|\tabcolsep| control the spacing between columns and the vertical space between rows, respectively.
 
@@
 \centering
-\newcolumntype{L}{X}
-\newcolumntype{C}{>{\centering \arraybackslash}X}
-\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
-\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
-\renewcommand\arraystretch{1.2}
-\caption{Table description}
-\label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
-\Xhline{2\arrayrulewidth}
-N  & A       & B    & C       & D      & E     \\
-\Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
-%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
+\setlength{\tabcolsep}{12pt}  % 6pt standard
+\renewcommand{\arraystretch}{1.2}
+\caption{Event Schedule}
+\label{tab:foo}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Date} & \textbf{Location}  & \textbf{Event Name}  & \textbf{Remarks}  \\ \hline
+2023-02  & New York & Academic Symposium     & Topic: Artificial Intelligence \\ \hline
+2023-05  & London   & Academic Exchange      & Focus: Mathematical Modeling   \\ \hline
+2023-09  & Shanghai & Technology Exhibition  & Display of New Chips           \\ \hline
+2024-02  & Tokyo   & Research Workshop      & Subject: Quantum Computing     \\ \hline
+2024-06  & Paris   & International Conference & Theme: Climate Change        \\ \hline
+\end{tabular}
 \end{table}
@@
 
-Additional results are available in the supplement in Table~\ref{tab:foo}.
+Use the \texttt{tabularx} environment to generate \autoref{tab:heightweight}.
+%The defined column type \texttt{P} also works for \texttt{tabular} environment.
 
@@
 \centering
-\renewcommand\arraystretch{1.2} % line spacing
+\newcolumntype{L}{X}
+\newcolumntype{C}{>{\centering \arraybackslash}X}
+\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
+\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
+\caption{Height and weight sample of students from a school}
+\label{tab:heightweight}
+\begin{tabularx}{0.9\textwidth}{P{1.5cm}CCC}
+\toprule
+Serial No. & Age & Height (cm) & Weight (kg) \\
+\midrule
+001 & 15 & 156 & 42 \\
+002 & 16 & 158 & 45 \\
+003 & 14 & 162 & 48 \\
+004 & 15 & 163 & 50 \\
+\cmidrule{2-4}
+Average & 15 & 159.75 & 46.25 \\
+\bottomrule
+\end{tabularx}
+\end{table}
+
+Additional results are available in the supplement in Table~\ref{tab:error}.
+
+\begin{table}[!htp]
+\centering
+\setlength{\tabcolsep}{8pt}
+\renewcommand\arraystretch{1.2}
 \caption{Numerical error}
-\label{tab:foo}
+\label{tab:error}
 \begin{tabular}{c|c|cc|cc|cc}
-\hline
+\Xhline{2\arrayrulewidth}
 degree & step-size~$h$ & $L^2$-errors & order & $H^1$-errors & order & $L^\infty$-errors & order \\
 \hline
+\multirow{3}{*}{1}
   & 1/128 & 9.18E-06 & 2.02 & 7.70E-03 & 1.01 & 6.46E-07 & 2.02 \\
-1 & 1/256 & 2.29E-06 & 2.01 & 1.92E-03 & 1.00 & 1.61E-07 & 2.01 \\
+  & 1/256 & 2.29E-06 & 2.01 & 1.92E-03 & 1.00 & 1.61E-07 & 2.01 \\
   & 1/512 & 5.70E-07 & 2.00 & 9.56E-04 & 1.00 & 4.01E-08 & 2.00 \\
 \hline  % \cline{1-8}
+\multirow{3}{*}{2}
   & 1/128 & 1.39E-08 & 3.01 & 1.15E-05 & 2.01 & 3.48E-12 & 4.02 \\
-2 & 1/256 & 1.73E-09 & 3.01 & 2.88E-06 & 2.01 & 3.27E-13 & 3.94 \\
+  & 1/256 & 1.73E-09 & 3.01 & 2.88E-06 & 2.01 & 3.27E-13 & 3.94 \\
   & 1/512 & 2.17E-10 & 3.00 & 7.24E-06 & 2.00 & 6.66E-13 & 1.55 \\
 \hline  % \cline{1-8}
+\multirow{3}{*}{3}
   & 1/32  & 2.28E-09 & 4.05 & 6.92E-07 & 3.04 & 1.45E-15 & 8.21 \\
-3 & 1/64  & 1.42E-10 & 4.03 & 8.65E-08 & 3.02 & 2.06E-14 & 3.85 \\
+  & 1/64  & 1.42E-10 & 4.03 & 8.65E-08 & 3.02 & 2.06E-14 & 3.85 \\
   & 1/128 & 8.91E-12 & 4.01 & 1.08E-08 & 3.01 & 3.86E-14 & 0.91 \\
-\hline
+\Xhline{2\arrayrulewidth}
 \end{tabular}
@@
 Some discussions here. Some discussions here. Some discussions here.
-Some discussions here. Some discussions here.
-
-Some discussions here. Some discussions here. Some discussions here.
 Some discussions here. Some discussions here. Some discussions here.
@@
 Some conclusions here. Some conclusions here. Some conclusions here.
-Some conclusions here.
-
-Some conclusions here. Some conclusions here. Some conclusions here.
 Some conclusions here. Some conclusions here. Some conclusions here.
@@
 
+% Appendix
 \appendix
@@
 % References
-\bibliographystyle{plain}
+%\bibliographystyle{plain}
 %\bibliographystyle{abbrv}
-%\bibliographystyle{amsplain}
+\bibliographystyle{amsplain}
 

### 2024-08-22 amsart-en/amsart-temp.tex
update

@@
 \usepackage{algpseudocode}
+% refinements for typographical perfection
+\usepackage{microtype}
 % package for using box and verbatim
@@
 \centering
-\newcolumntype{L}{X}
-\newcolumntype{C}{>{\centering \arraybackslash}X}
-\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
-\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
-\renewcommand\arraystretch{1.2}
-\caption{Table description}
-\label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
-\Xhline{2\arrayrulewidth}
-N  & A       & B    & C       & D      & E     \\
-\Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
-%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
+\setlength{\tabcolsep}{12pt}  % 6pt standard
+\renewcommand{\arraystretch}{1.2}
+\caption{Event Schedule}
+\label{tab:foo}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Date} & \textbf{Location}  & \textbf{Event Name}  & \textbf{Remarks}  \\ \hline
+2023-02  & New York & Academic Symposium     & Topic: Artificial Intelligence \\ \hline
+2023-05  & London   & Academic Exchange      & Focus: Mathematical Modeling   \\ \hline
+2023-09  & Shanghai & Technology Exhibition  & Display of New Chips           \\ \hline
+2024-02  & Tokyo   & Research Workshop      & Subject: Quantum Computing     \\ \hline
+2024-06  & Paris   & International Conference & Theme: Climate Change        \\ \hline
+\end{tabular}
 \end{table}
 
-Some description and explanation about figures and tables.
+Some description and explanation of pictures and tables.
 

### 2024-08-22 article-en/article-temp-info.tex
update

@@
 \usepackage{fancyhdr}
+% refinements for typographical perfection
+\usepackage{microtype}
 
@@
 \theoremstyle{remark}
-\newtheorem{remark}[theorem]{Remark}
+\newtheorem{remark}{Remark}[section]
 
@@
 \centering
-\newcolumntype{L}{X}
-\newcolumntype{C}{>{\centering \arraybackslash}X}
-\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
-\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
-\renewcommand\arraystretch{1.2}
-\caption{Table description}
-\label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
-\Xhline{2\arrayrulewidth}
-$N$  & A       & B    & C       & D      & E     \\
-\Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
-%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
+\setlength{\tabcolsep}{12pt}  % 6pt standard
+\renewcommand{\arraystretch}{1.2}
+\caption{Event Schedule}
+\label{tab:foo}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Date} & \textbf{Location}  & \textbf{Event Name}  & \textbf{Remarks}  \\ \hline
+2023-02  & New York & Academic Symposium     & Topic: Artificial Intelligence \\ \hline
+2023-05  & London   & Academic Exchange      & Focus: Mathematical Modeling   \\ \hline
+2023-09  & Shanghai & Technology Exhibition  & Display of New Chips           \\ \hline
+2024-02  & Tokyo   & Research Workshop      & Subject: Quantum Computing     \\ \hline
+2024-06  & Paris   & International Conference & Theme: Climate Change        \\ \hline
+\end{tabular}
 \end{table}
@@
 
-Additional results are available in the supplement in Table~\ref{tab:foo}.
+Use the \texttt{tabularx} environment to generate \autoref{tab:heightweight}.
+%The defined column type \texttt{P} also works for \texttt{tabular} environment.
 
-\begin{table}[!htp]
+\begin{table}[htp!]
 \centering
-\renewcommand\arraystretch{1.2} % line spacing
+\newcolumntype{L}{X}
+\newcolumntype{C}{>{\centering \arraybackslash}X}
+\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
+\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
+\caption{Height and weight sample of students from a school}
+\label{tab:heightweight}
+\begin{tabularx}{0.9\textwidth}{P{1.5cm}CCC}
+\toprule
+Serial No. & Age & Height (cm) & Weight (kg) \\
+\midrule
+001 & 15 & 156 & 42 \\
+002 & 16 & 158 & 45 \\
+003 & 14 & 162 & 48 \\
+004 & 15 & 163 & 50 \\
+\cmidrule{2-4}
+Average & 15 & 159.75 & 46.25 \\
+\bottomrule
+\end{tabularx}
+\end{table}
+
+Additional results are available in the supplement in Table~\ref{tab:error}.
+
+\begin{table}[htp!]
+\centering
+\setlength{\tabcolsep}{8pt}
+\renewcommand\arraystretch{1.2}
 \caption{Numerical error}
-\label{tab:foo}
+\label{tab:error}
 \begin{tabular}{c|c|cc|cc|cc}
-\hline
+\Xhline{2\arrayrulewidth}
 degree & step-size~$h$ & $L^2$-errors & order & $H^1$-errors & order & $L^\infty$-errors & order \\
 \hline
+\multirow{3}{*}{1}
   & 1/128 & 9.18E-06 & 2.02 & 7.70E-03 & 1.01 & 6.46E-07 & 2.02 \\
-1 & 1/256 & 2.29E-06 & 2.01 & 1.92E-03 & 1.00 & 1.61E-07 & 2.01 \\
+  & 1/256 & 2.29E-06 & 2.01 & 1.92E-03 & 1.00 & 1.61E-07 & 2.01 \\
   & 1/512 & 5.70E-07 & 2.00 & 9.56E-04 & 1.00 & 4.01E-08 & 2.00 \\
 \hline  % \cline{1-8}
+\multirow{3}{*}{2}
   & 1/128 & 1.39E-08 & 3.01 & 1.15E-05 & 2.01 & 3.48E-12 & 4.02 \\
-2 & 1/256 & 1.73E-09 & 3.01 & 2.88E-06 & 2.01 & 3.27E-13 & 3.94 \\
+  & 1/256 & 1.73E-09 & 3.01 & 2.88E-06 & 2.01 & 3.27E-13 & 3.94 \\
   & 1/512 & 2.17E-10 & 3.00 & 7.24E-06 & 2.00 & 6.66E-13 & 1.55 \\
 \hline  % \cline{1-8}
+\multirow{3}{*}{3}
   & 1/32  & 2.28E-09 & 4.05 & 6.92E-07 & 3.04 & 1.45E-15 & 8.21 \\
-3 & 1/64  & 1.42E-10 & 4.03 & 8.65E-08 & 3.02 & 2.06E-14 & 3.85 \\
+  & 1/64  & 1.42E-10 & 4.03 & 8.65E-08 & 3.02 & 2.06E-14 & 3.85 \\
   & 1/128 & 8.91E-12 & 4.01 & 1.08E-08 & 3.01 & 3.86E-14 & 0.91 \\
-\hline
+\Xhline{2\arrayrulewidth}
 \end{tabular}

### 2024-08-22 article-en/article-temp.tex
update

@@
 \usepackage{fancybox}
+% refinements for typographical perfection
+\usepackage{microtype}
 

### 2024-08-22 article-en/article-temp2.tex
update

@@
 \centering
-\newcolumntype{L}{X}
-\newcolumntype{C}{>{\centering \arraybackslash}X}
-\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
-\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
-\renewcommand\arraystretch{1.2}
-\caption{Table description}
-\label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
-\Xhline{2\arrayrulewidth}
-$N$  & A       & B    & C       & D      & E     \\
-\Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-%8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-%10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-%12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
-%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
+\setlength{\tabcolsep}{12pt}  % 6pt standard
+\renewcommand{\arraystretch}{1.2}
+\caption{Event Schedule}
+\label{tab:foo}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Date} & \textbf{Location}  & \textbf{Event Name}  & \textbf{Remarks}  \\ \hline
+2023-02  & New York & Academic Symposium     & Topic: Artificial Intelligence \\ \hline
+2023-05  & London   & Academic Exchange      & Focus: Mathematical Modeling   \\ \hline
+2023-09  & Shanghai & Technology Exhibition  & Display of New Chips           \\ \hline
+2024-02  & Tokyo   & Research Workshop      & Subject: Quantum Computing     \\ \hline
+2024-06  & Paris   & International Conference & Theme: Climate Change        \\ \hline
+\end{tabular}
 \end{table}

### 2024-08-22 book-en/book-en.tex
update

@@
 \usepackage{amsmath,amsthm,amssymb}
-\usepackage{mathrsfs,bm}
+\usepackage{mathrsfs}
 %\usepackage[notcite,notref]{showkeys}
-\usepackage{geometry}
-\geometry{left=2.5cm,right=2.5cm,top=3.0cm,bottom=3.0cm}
-%\geometry{left=1in,right=1in,top=1in,bottom=1in}
-%\geometry{left=2.5cm,right=2.1cm,top=1.7cm,bottom=2cm,includehead,includefoot}
-%\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
-
 \usepackage[english]{babel}
@@
 \usepackage{bookmark}
+\usepackage{microtype}
+\usepackage{geometry}
+\geometry{left=2.5cm,right=2.5cm,top=3.0cm,bottom=3.0cm}
+%\geometry{left=1in,right=1in,top=1in,bottom=1in}
+%\geometry{left=2.5cm,right=2.1cm,top=1.7cm,bottom=2cm,includehead,includefoot}
+%\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
+\setlength{\headheight}{18pt}
+\setlength{\headsep}{18pt}
+\setlength{\footskip}{25pt}
 
@@
 
+%----- make index -----
 \makeindex
-%\bibliographystyle{plain}
+
+%----- bibliography style -----
+\bibliographystyle{plain}
 
@@
 
-\usepackage[cleardoublepage=plain]{scrextend}
+%---- cleardoublepage -----
+%\usepackage[cleardoublepage=plain]{scrextend}
+\makeatletter
+\renewcommand{\cleardoublepage}{\clearpage
+  \clearpage\if@twoside\ifodd\c@page\else%
+  \thispagestyle{empty}%
+  \hbox{}\newpage\if@twocolumn\hbox{}\newpage\fi\fi\fi%
+}
+\makeatother
 
+%----- header and footer -----
 \usepackage{fancyhdr,fancyref}
@@
 \fancyhf{}  % remove the original style
-\fancyhead[RO,LE]{~\thepage~}
+\fancyhead[RO,LE]{\thepage}
 \fancyhead[LO]{\rmfamily \rightmark}
@@
 
-\setlength{\headheight}{15pt}
+\renewcommand{\baselinestretch}{1.2}
 %\setlength{\parskip}{3pt plus1pt minus1pt}
-
-\renewcommand{\baselinestretch}{1.2}
 
@@
 \newtheorem{corollary}{Corollary}[chapter]
-\newtheorem{remark}{Remarks}[chapter]
+\newtheorem{remark}{Remark}[chapter]
 \newtheorem{exercise}{Exercise}[chapter]
@@
 
+% graphic path
+\graphicspath{{./figure/}{./figures/}{./image/}{./images/}}
+
+% differential operator
+\newcommand{\dif}{\mathop{}\!\mathrm{d}}
+
 % define new command
@@
 \newcommand{\norm}[1]{\lVert#1\rVert}
-\newcommand{\dif}{\mathop{}\!\mathrm{d}}
 \newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
@@
 \newcommand{\plogo}{\fbox{$\mathcal{PL}$}} % Generic dummy publisher logo
-
-\graphicspath{{./figure/}{./figures/}{./image/}{./images/}}
 
@@
 
-\chapter{Preface}
+\addcontentsline{toc}{chapter}{Preface}
+\markboth{Preface}{}
+\chapter*{Preface}
 
@@
 
-\clearpage
 Adjust the width of the algorithm environment
@@
 
-Additional results are available in the supplement in Table \ref{tab:foo}.
+Use the \texttt{tabular} environment to generate \autoref{tab:foo}.
+The commands \verb|\tabcolsep| and \verb|\tabcolsep| control the spacing between columns and the vertical space between rows, respectively.
 
-\begin{table}[!htp]
+\begin{table}[htp!]
 \centering
-\renewcommand\arraystretch{1.2} % line spacing
-\caption{Numerical error}
+\setlength{\tabcolsep}{10pt}  % 6pt standard
+\renewcommand{\arraystretch}{1.2}
+\caption{Event Schedule}
 \label{tab:foo}
-\begin{tabular}{c|c|cc|cc|cc}
+\begin{tabular}{|c|c|c|c|}
 \hline
-degree &  step-size~$h$  & $L^2$-errors  &  order  & $H^1$-errors & order & $L^\infty$-errors  &  order \\
-\hline
-   &  1/128    & 9.18E-06    &2.02    & 7.70E-03  &1.01       & 6.46E-07    &2.02   \\
-1  &  1/256    & 2.29E-06    &2.01    & 1.92E-03  &1.00       & 1.61E-07    &2.01   \\
-   &  1/512    & 5.70E-07    &2.00    & 9.56E-04  &1.00       & 4.01E-08    &2.00   \\
-\hline  % \cline{1-8}
-   &  1/128    & 1.39E-08    &3.01    & 1.15E-05  &2.01       & 3.48E-12   &4.02    \\
-2  &  1/256    & 1.73E-09    &3.01    & 2.88E-06  &2.01       & 3.27E-13   &3.94    \\
-   &  1/512    & 2.17E-10    &3.00    & 7.24E-06  &2.00       & 6.66E-13   &1.55    \\
-\hline  % \cline{1-8}
-   &  1/32     & 2.28E-09    &4.05    & 6.92E-07  &3.04       & 1.45E-15   &8.21    \\
-3  &  1/64     & 1.42E-10    &4.03    & 8.65E-08  &3.02       & 2.06E-14   &3.85    \\
-   &  1/128    & 8.91E-12    &4.01    & 1.08E-08  &3.01       & 3.86E-14   &0.91    \\
-\hline
+\textbf{Date} & \textbf{Location}  & \textbf{Event Name}  & \textbf{Remarks}  \\ \hline
+2023-02  & New York & Academic Symposium     & Topic: Artificial Intelligence \\ \hline
+2023-05  & London   & Academic Exchange      & Focus: Mathematical Modeling   \\ \hline
+2023-09  & Shanghai & Technology Exhibition  & Display of New Chips           \\ \hline
+2024-02  & Tokyo   & Research Workshop      & Subject: Quantum Computing     \\ \hline
+2024-06  & Paris   & International Conference & Theme: Climate Change        \\ \hline
 \end{tabular}
@@
 
-Use the \texttt{tabularx} environment to generate \autoref{tab:error}.
+\clearpage
+Use the \texttt{tabularx} environment to generate \autoref{tab:heightweight}.
+%The defined column type \texttt{P} also works for \texttt{tabular} environment.
 
@@
 \centering
+\caption{Height and weight sample of students from a school}
+\label{tab:heightweight}
+\begin{tabularx}{0.9\textwidth}{P{1.5cm}CCC}
+\toprule
+Serial No. & Age & Height (cm) & Weight (kg) \\
+\midrule
+001 & 15 & 156 & 42 \\
+002 & 16 & 158 & 45 \\
+003 & 14 & 162 & 48 \\
+004 & 15 & 163 & 50 \\
+\cmidrule{2-4}
+Average & 15 & 159.75 & 46.25 \\
+\bottomrule
+\end{tabularx}
+\end{table}
+
+Additional results are available in the supplement in Table~\ref{tab:error}.
+
+\begin{table}[htp!]
+\centering
+\setlength{\tabcolsep}{8pt}
 \renewcommand\arraystretch{1.2}
-\caption{Table description}
+\caption{Numerical error}
 \label{tab:error}
-\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
+\begin{tabular}{c|c|cc|cc|cc}
 \Xhline{2\arrayrulewidth}
-N  & A       & B    & C       & D      & E     \\
+degree & step-size~$h$ & $L^2$-errors & order & $H^1$-errors & order & $L^\infty$-errors & order \\
+\hline
+\multirow{3}{*}{1}
+  & 1/128 & 9.18E-06 & 2.02 & 7.70E-03 & 1.01 & 6.46E-07 & 2.02 \\
+  & 1/256 & 2.29E-06 & 2.01 & 1.92E-03 & 1.00 & 1.61E-07 & 2.01 \\
+  & 1/512 & 5.70E-07 & 2.00 & 9.56E-04 & 1.00 & 4.01E-08 & 2.00 \\
+\hline  % \cline{1-8}
+\multirow{3}{*}{2}
+  & 1/128 & 1.39E-08 & 3.01 & 1.15E-05 & 2.01 & 3.48E-12 & 4.02 \\
+  & 1/256 & 1.73E-09 & 3.01 & 2.88E-06 & 2.01 & 3.27E-13 & 3.94 \\
+  & 1/512 & 2.17E-10 & 3.00 & 7.24E-06 & 2.00 & 6.66E-13 & 1.55 \\
+\hline  % \cline{1-8}
+\multirow{3}{*}{3}
+  & 1/32  & 2.28E-09 & 4.05 & 6.92E-07 & 3.04 & 1.45E-15 & 8.21 \\
+  & 1/64  & 1.42E-10 & 4.03 & 8.65E-08 & 3.02 & 2.06E-14 & 3.85 \\
+  & 1/128 & 8.91E-12 & 4.01 & 1.08E-08 & 3.01 & 3.86E-14 & 0.91 \\
 \Xhline{2\arrayrulewidth}
-2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
-4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
-6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
-8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
-10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
-12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
-\Xhline{2\arrayrulewidth}
-\end{tabularx}
+\end{tabular}
 \end{table}
@@
 
+\clearpage
 \section{Figure Environment}
@@
 
-\clearpage
 The two figures are placed side by side, sharing the one title, as shown in Figure~\ref{fig:twofigs}.
@@
 
+\clearpage
 Use \texttt{minipage} package to set images side-by-side, each with its own title, as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
@@
 
-The following table: Table~\ref{tab2:heightweight}. Use \verb|autoref|: \autoref{tab2:heightweight}.
+The following table: Table~\ref{tab:heightweight2}.
 
@@
 \caption{A sample of the height and weight of students.}
-\label{tab2:heightweight}
-% PLCR is defined in the preamble
-\begin{tabularx}{0.8\textwidth}{lCCC}
-   \toprule %\Xhline{2\arrayrulewidth}
-	Number &  Age & Height & Weight\\
+\label{tab:heightweight2}
+\begin{tabularx}{0.9\textwidth}{P{1.5cm}CCC}
+\toprule
+Serial No. & Age & Height (cm) & Weight (kg) \\
 \midrule
-	1&14&156&42\\
-	2&16&158&45\\
-	3&14&162&48\\
-	4&15&163&50\\
+001 & 15 & 156 & 42 \\
+002 & 16 & 158 & 45 \\
+003 & 14 & 162 & 48 \\
+004 & 15 & 163 & 50 \\
 \cmidrule{2-4}
-	Mean &15&159.75&46.25\\
+Average & 15 & 159.75 & 46.25 \\
 \bottomrule
@@
 
-\bibliographystyle{plain}
 \bibliography{reference}

### 2024-08-22 book-en/book-temp-en.tex
update

--- 2023-04-14 book-en/book-cover-en.tex
@@
 %\usepackage[notcite,notref]{showkeys}
-\usepackage{geometry}
-\geometry{left=2.5cm,right=2.5cm,top=3.0cm,bottom=3.0cm}
-%\geometry{left=1in,right=1in,top=1in,bottom=1in}
-%\geometry{left=2.5cm,right=2.1cm,top=1.7cm,bottom=2cm,includehead,includefoot}
-%\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
-
 \usepackage[english]{babel}
@@
 \usepackage{algpseudocode}
-\usepackage{xstring}
+%\usepackage{xstring}
 %\usepackage[english]{babel}
@@
 \usepackage{anyfontsize}
+\usepackage{microtype}
+\usepackage{geometry}
+\geometry{left=2.5cm,right=2.5cm,top=3.0cm,bottom=3.0cm}
+%\geometry{left=1in,right=1in,top=1in,bottom=1in}
+%\geometry{left=2.5cm,right=2.1cm,top=1.7cm,bottom=2cm,includehead,includefoot}
+%\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
+\setlength{\headheight}{18pt}
+\setlength{\headsep}{18pt}
+\setlength{\footskip}{25pt}
 
@@
 %\def\bibfont{\small}  % bib font size
-%\setlength{\bibsep}{8pt}  % vertical space of bib
+%\setlength{\bibsep}{7pt plus 3pt minus 3pt}  % vertical space of bib
 
@@
 
-\usepackage[cleardoublepage=plain]{scrextend}
+%---- cleardoublepage -----
+%\usepackage[cleardoublepage=plain]{scrextend}
+\makeatletter
+\renewcommand{\cleardoublepage}{\clearpage
+  \clearpage\if@twoside\ifodd\c@page\else%
+  \thispagestyle{empty}%
+  \hbox{}\newpage\if@twocolumn\hbox{}\newpage\fi\fi\fi%
+}
+\makeatother
 
@@
 \pagestyle{fancy}
-%\renewcommand{\chaptermark}[1]{\markboth{\thechapter ~ #1}{}}
-%\renewcommand{\sectionmark}[1]{\markright{\thesection ~ #1}{}}
 \fancyhf{}  % remove the original style
@@
 
-\setlength{\headheight}{15pt}
+%----- linespread -----
+\renewcommand{\baselinestretch}{1.2}
 %\setlength{\parskip}{3pt plus1pt minus1pt}
 
-\usepackage{tocloft,calc}
-\renewcommand{\cftchappresnum}{\chaptername\space}
-\renewcommand{\cftchapaftersnumb}{\hspace{-12pt}}
-\setlength{\cftchapnumwidth}{\widthof{\textbf{Appendix~999~}}}
-\makeatletter
-\g@addto@macro\appendix{%
-  \addtocontents{toc}{%
-    \protect\renewcommand{\protect\cftchappresnum}{\appendixname\space}%
-    \protect\renewcommand{\protect\cftchapaftersnumb}{\hspace{0pt}}
-  }%
-  \renewcommand{\chaptermark}[1]{\markboth{\appendixname~\thechapter. ~ #1}{}}
-}
-
-\renewcommand{\baselinestretch}{1.2}
+%----- table of contents -----
+\usepackage{tocloft}
+\renewcommand{\cftaftertoctitle}{\hfill}
+%\setlength{\cftbeforetoctitleskip}{12pt}
+%\setlength{\cftaftertoctitleskip}{24pt}
+%\setlength{\cftbeforechapskip}{12pt plus 2pt minus 2pt}
+%\setlength{\cftbeforesecskip}{3pt}
+\renewcommand{\cftdot}{$\cdot$}
+\renewcommand{\cftdotsep}{3}
+\renewcommand{\cftchapdotsep}{\cftdotsep}
+\renewcommand\cftchapleader{\cftdotfill{\cftchapdotsep}}
+\renewcommand{\cftsecdotsep}{\cftdotsep}
 
@@
 
+% graphic path
+\graphicspath{{./figure/}{./figures/}{./image/}{./images/}}
+
 % differential operator
@@
 \begin{titlepage} % Suppresses headers and footers on the title page
-
+  \makeatletter
   \pdfbookmark[0]{Cover}{cover} % book cover
@@
 
-	\scshape % Use small caps for all text on the title page
+  % \scshape % Use small caps for all text on the title page
 
@@
 
-    \makeatletter
-
-	{\LARGE\bfseries \@title \\} % Title
+  {\LARGE\bfseries \@title } % Title
 
@@
 
-	{\scshape\Large \@author \\} % Editor list
+  {\scshape\Large \@author} % Editor list
 
@@
 
+  \makeatother
+
   \vfill % Whitespace between editor names and publisher logo
-
-    \makeatletter
 
@@
 
-\chapter{Preface}
+\addcontentsline{toc}{chapter}{Preface}
+\markboth{Preface}{}
+\chapter*{Preface}
+
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
+The quick brown fox jumps over the lazy dog.
 

### 2024-08-31 book-en/book-en.tex
update

@@
 \author{Edited by Andy}
-\date{February 2023}
+\date{\today}
 
@@
 
-\section{The first section}\label{my label}
+\section{The first section}\label{sec:firstsec}
 LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
@@
 For example consider this document:
-\begin{equation}\label{eqn:trifun}
+\begin{equation}\label{eq:trifun}
 \sin^2{\theta}+\cos^2{\theta}=1.
@@
 This is a lemma environment
-\begin{enumerate}[label=\rm (\roman*)]
+\begin{enumerate}[label={\upshape(\roman*)}]
   \item item A

### 2024-08-31 book-en/book-temp-en.tex
update

@@
 
-\title{THE BOOK \\[8pt] \LaTeX ~TEMPLATES}
+\title{THE BOOK \\[8pt] \LaTeX{} TEMPLATES}
 \author{Edited by Andy}

### 2024-09-30 book-en/book-temp-en.tex
update

@@
 
-\title{THE BOOK \\[8pt] \LaTeX{} TEMPLATES}
-\author{Edited by Andy}
+\title{THE BOOK \\[12pt] \LaTeX{} TEMPLATES}
+\author{Andy}
 \date{\today}

### 2024-09-30 book-en/makefiles.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+#-> Get source filename
+find . -maxdepth 1 -type f -name "*.tex" | while read FileName; do 
+#--- Process FileName.tex ---
+echo "$FileName"
+echo "${FileName%.tex}"
+#-> Compile the main file
+pdflatex --synctex=-1 "$FileName"
+bibtex "${FileName%.tex}"
+pdflatex --synctex=-1 "$FileName"
+pdflatex --synctex=-1 "$FileName"
+#clear aux files
+rm -r *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb 
+done

### 2024-09-30 faq/cleaner.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+# Delete files with the specified extensions
+rm -f *.aux *.bbl *.blg *.log *.out *.toc *.bcf *.xml *.synctex *.nlo *.nls *.bak *.ind *.idx *.ilg *.lof *.lot *.ent-x *.tmp *.ltx *.los *.lol *.loc *.listing *.gz *.userbak *.nav *.snm *.vrb *.synctex\(busy\)
+
+rm -f *.fls *.xdv *.fdb_latexmk

### 2024-10-10 amsart-en/amsart-journal.tex
update

@@
 
-\keywords{Keyword 1, keyword 2, error analysis}
+\keywords{Academic article, example, \LaTeX{} template}
 
@@
 \begin{abstract}
-This is an example \LaTeX\ article. This can be used as a template for new articles.
-Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
+This is an example \LaTeX{} article. This can be used as a template for new articles.
+Abstracts must be able to stand alone and so cannot contain citations to the paper's references, equations, etc.
 An abstract must consist of a single paragraph and be concise.
@@
 
-In this paper we present a new method for solving the model equation
+In this paper, we present a new method for solving the model equation
 \begin{equation}\label{eq:mulequ}
@@
   & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
-  &\, u(x,y,t) = g(t), \quad \text{on } ~ \partial \Omega, \\
-  &\, u(x,y,0)=\varphi(x, y), \quad \text{on } ~\Omega.
+  & u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega \times \mathcal{T},, \\
+  & u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega,
 \end{aligned}\right.
@@
 
-This is an example of quoting an equation \eqref{eq:mulequ}.
+This is an example of referencing the equation \eqref{eq:mulequ}.
 
@@
 
-This is a equation in appendix.
+This is an equation in the appendix.
 \begin{equation}\label{eq:abc}

### 2024-10-10 article-en/article-temp-info.tex
update

@@
 
+% package for line number
+%\usepackage[pagewise,mathlines]{lineno}
+%\linenumbers
+%\modulolinenumbers[5]
+
 % differential operator
@@
 
-% Information for title and author
-\title{An Example Article\tfootnote{This is a title footnote}}
+% Full Title of the paper
+\title{Academic Article Template for Manuscript or Preprint\tfootnote{This is a title footnote}}
 
@@
 
+% Authors and their affiliations
 \author[1]{Author A}
@@
 \author[1,\cormark]{Author C}
-\affil[1]{Department of Mathematics, \LaTeX\ University}
-\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
+\affil[1]{Department of Mathematics, \LaTeX{} University}
+\affil[2]{Department of Mechanical Engineering, \LaTeX{} University}
 \cortext{Corresponding author. Email address: \texttt{xyz@math.univ.edu}}
@@
 
+% Date is editable
 \date{Date: \today}
@@
 \medskip
-\noindent{\bfseries Keywords}: Example, \LaTeX, numerical methods
+\noindent{\bfseries Keywords}: Academic article, Example, \LaTeX{} template
 
@@
 \end{abstract}
+
+%%%%%%%%%% main body %%%%%%%%%%
 
@@
   & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
-  &\, u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega, \\
-  &\, u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega.
+  & u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega \times \mathcal{T},, \\
+  & u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega,
 \end{aligned}\right.
@@
 
-This is a equation in appendix.
+This is an equation in the appendix.
 \begin{equation}\label{eq:A1}

### 2024-10-10 article-en/article-temp.tex
update

@@
 \author{
-  Author A\thanks{Department of Computer Science, \LaTeX\ University}~,
-  Author B\thanks{Department of Mathematics, \LaTeX\ University}~,
+  Author A\thanks{Department of Computer Science, \LaTeX{} University}~,
+  Author B\thanks{Department of Mathematics, \LaTeX{} University}~,
   and
-  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
+  Author C\thanks{Department of Mechanical Engineering, \LaTeX{} University}
 }

### 2024-10-10 article-en/article-temp2.tex
update

@@
   Author A \\
-  {\itshape Department of Computer Science, \LaTeX\ University} \\
+  {\itshape Department of Computer Science, \LaTeX{} University} \\
   \and
   Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
-  {\itshape Department of Mathematics, \LaTeX\ University} \\
+  {\itshape Department of Mathematics, \LaTeX{} University} \\
   \and
   Author C\thanks{This author was supported in part by NSFC Grant No. 12345678.} \\
-  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
+  {\itshape Department of Mechanical Engineering, \LaTeX{} University} \\
 }

### 2024-10-10 article-en/article-temp3.tex
update

@@
 %\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
-\affil[1]{Department of Mathematics, \LaTeX\ University}
-\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
+\affil[1]{Department of Mathematics, \LaTeX{} University}
+\affil[2]{Department of Mechanical Engineering, \LaTeX{} University}
 
